---
subtitle: |
  Code Notebook Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr etc
  "here", # to never worry about directories
  "ggpubr", # theme_pubr()
  "janitor", # tabyl()
  "knitr", # for kable()
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load Data

Full dataset (and pre-processing pipeline) is available at [GitHub](https://github.com/LS-Konig/eu25games2019). We can directly fetch the data from there (by now also compressed, so only ca 30 MB). `read_rds()` can decompress the file directly.

```{r}
#| label: load-data
# URL of raw data
raw_url <- "https://raw.githubusercontent.com/LS-Konig/eu25games2019/main/data/03_final/eu25games2019.rds?cache_bust=1"

# Create temporary file path
tmp <- tempfile(fileext = ".rds")

# Download binary file locally
download.file(raw_url, tmp, mode = "wb")

# Read data into R (takes a couple seconds as it decompresses the file)
eu25games2019 <- read_rds(tmp)

# Clean up variables
rm(raw_url, tmp)
```

`eu25games2019` contains data in wide format, i.e., one row corresponds one survey response. So far I have not excluded incompletes or anything. This is just a quick starter for Tuesday's presentation.

To analyze outcomes, the data need to be transformed to long (tidy) format, with one row equal to one observation, in this case one row should be one game played.

```{r}
#| label: game-outcomes-to-long
# select relevant variables
eu25_games_long <- eu25games2019 |>
  # wave, country and respondent identifiers
  select(
    meta_wave,
    meta_country,
    meta_pid,
    # dictator game vars
    contains("cj_dict"),
    # trust game vars
    contains("cj_trust")
  ) |>
  # to long format
  pivot_longer(
    cols = -c(meta_wave, meta_country, meta_pid),
    names_to = c("game_type", "round", ".value"),
    names_pattern = "^(cj_dict|cj_trust)(\\d+)_(.+)$"
  ) |>
  # keep cj_ prefix for experimental vars
  rename_with(
    ~ paste0("cj_", .),
    -c(meta_wave, meta_country, meta_pid, game_type, round)
  ) |>
  # filter observations with valid outcomes
  filter(!is.na(cj_pl2))
```

# Preliminary Tables and Figures

```{r}
#| label: tbl-n-outcomes-per-country
#| tbl-cap: "Number of valid game observations per country"
eu25_games_long |>
  filter(!is.na(cj_pl2)) |>
  tabyl(meta_country)
```

```{r}
#| label: tbl-n-resp-per-country
#| tbl-cap: "Number of unique respondents per country"
eu25_games_long |>
  filter(!is.na(cj_pl2)) |>
  group_by(meta_country) |>
  summarise(n_resp = n_distinct(meta_pid))
```

```{r}
#| label: fig-randomization
#| fig-cap: "Number of observations (one row = one game played) per drawn religion attribute, separately for the dictator and trust game."
#| fig-dpi: 300
#| fig-width: 6
#| fig-height: 3
#| out-width: "60%"
eu25_games_long |>
  filter(!is.na(cj_rel)) |>
  ggplot(aes(x = cj_rel)) +
  geom_bar(,
    color = "black",
    fill = "white",
    width = 0.5
  ) +
  labs(
    title = "Randomization Check: Religion Attribute",
    x = "Religion attribute",
    y = "Number of observations"
  ) +
  theme_pubr(base_size = 8) +
  facet_wrap(~game_type)
```

```{r}
#| label: fig-tokens-to-muslim-profiles
#| fig-cap: "Mean tokens allocated to Player 2 by religion attribute, in the Dictator and Trust games. Bar height corresponds to group means."
#| dpi: 300
#| fig-height: 3
#| fig-width: 6
# summary stats
rel_summ <- eu25_games_long |>
  group_by(game_type, cj_rel) |>
  summarise(
    mean_toks = mean(cj_pl2),
    sd_toks = sd(cj_pl2),
    .groups = "drop"
  ) |>
  filter(!is.na(cj_rel)) |>
  mutate(cj_rel = fct_reorder(cj_rel, mean_toks))

# detect Muslim category label from factor levels
muslim_key <- levels(rel_summ$cj_rel)[
  grepl("uslim", levels(rel_summ$cj_rel), ignore.case = TRUE)
]

# pairwise t-tests: each non-Muslim group vs Muslim
rel_clean <- eu25_games_long |>
  filter(!is.na(cj_rel), !is.na(cj_pl2))

ttest_annot <- rel_clean |>
  group_by(game_type) |>
  group_modify(
    ~ {
      d <- .x
      others <- setdiff(unique(d$cj_rel), muslim_key)
      purrr::map_dfr(others, function(grp) {
        tt <- t.test(
          d$cj_pl2[d$cj_rel == muslim_key],
          d$cj_pl2[d$cj_rel == grp]
        )
        tibble(
          cj_rel = grp,
          label = sprintf(
            "vs. Muslim\nt = %.2f, p = %.3f",
            tt$statistic,
            tt$p.value
          )
        )
      })
    }
  ) |>
  ungroup() |>
  left_join(
    rel_summ |> select(game_type, cj_rel, mean_toks),
    by = c("game_type", "cj_rel")
  ) |>
  mutate(cj_rel = factor(cj_rel, levels = levels(rel_summ$cj_rel)))

ggplot(rel_summ, aes(x = cj_rel, y = mean_toks)) +
  geom_col(colour = "black", fill = "white", width = 0.5) +
  geom_text(
    aes(label = round(mean_toks, 2)),
    vjust = -0.5,
    size = 3
  ) +
  # geom_text(
  #   data = ttest_annot,
  #   aes(x = cj_rel, y = mean_toks * 0, label = label),
  #   size = 2.5,
  #   colour = "grey40",
  #   lineheight = 0.9
  # ) +
  labs(
    title = "Mean Tokens by Religion of Player 2",
    x = NULL,
    y = "Mean tokens allocated"
  ) +
  theme_pubr(base_size = 8) +
  facet_wrap(~game_type)
```


# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
