---
subtitle: |
  Code Notebook Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false

# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr etc
  "here", # to never worry about directories
  "ggpubr", # theme_pubr()
  "knitr", # for kable()
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load Data

Note to others: at this point, I have only recoded the religion attribute variables, the rest is yet to be done. Variables with `_raw` suffix contain original survey responses which vary across countries / languages, I plan to construct a respective harmonized variable for each `_raw` in the data, however I keep this in a seperate repo as it's just a super messy dataset. I will add appropriate documentation of the variable naming schemes etc. asap.

```{r}
#| label: load-data

eu25games2019 <- read_rds(
  here(
    "data",
    "01_raw",
    "eu25games2019.rds"
  )
)
```

`eu25games2019` contains data in wide format, i.e., one row corresponds one survey response. So far I have not excluded incompletes or anything. This is just a quick starter for Tuesday's presentation.

To analyze outcomes, the data need to be transformed to long (tidy) format, with one row equal to one observation, in this case one row should be one game played.

```{r}
#| label: game-outcomes-to-long

# select relevant variables
eu25_games_long <- eu25games2019 |>
  # wave, country and respondent identifiers
  select(
    meta_wave,
    meta_country,
    meta_pid,
    # dictator game vars
    contains("cj_dict"),
    # trust game vars
    contains("cj_trust")
  ) |>
  # to long format
  pivot_longer(
    cols = -c(meta_wave, meta_country, meta_pid),
    names_to = c("game_type", "round", ".value"),
    names_pattern = "^(cj_dict|cj_trust)(\\d+)_(.+)$"
  ) |>
  # keep cj_ prefix for experimental vars
  rename_with(
    ~ paste0("cj_", .),
    -c(meta_wave, meta_country, meta_pid, game_type, round)
  ) |>
  # filter observations with valid outcomes
  filter(!is.na(cj_pl2))

```

# Preliminary Figure

```{r}
#| label: fig-tokens-to-muslim-profiles
#| fig-cap: "Mean tokens allocated to profiles displayed as Muslim in the Dictator and Trust games. Heigth of bars correspond to means, segment show standard deviations."

eu25_games_long |>
  group_by(game_type, cj_rel) |>
  summarise(
    mean_toks = mean(cj_pl2),
    sd_toks = sd(cj_pl2)
  ) |>
  filter(!is.na(cj_rel)) |>
  ggplot() +
  geom_col(
    aes(
      x = fct_reorder(cj_rel, mean_toks),
      y = mean_toks
    ),
    color = "black",
    fill = "white",
    width = 0.5
  ) +
  geom_segment(
    aes(
      x = fct_reorder(cj_rel, mean_toks),
      y = mean_toks - sd_toks,
      yend = mean_toks + sd_toks
    )
  ) +
  theme_pubr() +
  facet_wrap(~game_type)
```


# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true

end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
