---
subtitle: |
  Data Preparation for Analyses
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

Goal: create long format analysis tibble with outcome, predictors, respondent and country IDs.

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr etc
  "here", # to never worry about directories
  "ggpubr", # theme_pubr()
  "janitor", # tabyl()
  "knitr", # for kable()
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load Data

Full dataset (and pre-processing pipeline) is available at [GitHub](https://github.com/LS-Konig/eu25games2019). We can directly fetch the data from there (by now also compressed, so only ca 30 MB). `read_rds()` can decompress the file directly.

```{r}
#| label: load-data
# URL of raw data
raw_url <- "https://raw.githubusercontent.com/LS-Konig/eu25games2019/main/data/03_final/eu25games2019.rds?cache_bust=1"

# Create temporary file path
tmp <- tempfile(fileext = ".rds")

# Download binary file locally
download.file(raw_url, tmp, mode = "wb")

# Read data into R (takes a couple seconds as it decompresses the file)
eu25games2019 <- read_rds(tmp)

# Clean up variables
rm(raw_url, tmp)
```


# Filter out wave 1 only respondets

Data comes in three waves with partial panel structure.

```{r}
#| label: explore-partial-panel
# count obs per wave
cat("Raw observations per wave:\n")
eu25games2019 |>
  count(meta_wave)

# total obs (raw)
cat("\nRaw observations total:\n")
eu25games2019 |>
  nrow()

# missing IDs --- would distort every duplicate count below, so check first ----
cat("\nMissing values in ID variables:\n")
eu25games2019 |>
  summarise(
    na_responseid = sum(is.na(meta_responseid)),
    na_psid = sum(is.na(meta_psid)),
    na_pid = sum(is.na(meta_pid))
  )

# distinct ID values -----------------------------------------------------------
cat("\nDistinct `meta_responseid` values:\n")
eu25games2019 |>
  distinct(meta_responseid) |>
  nrow()

cat("\nDistinct `meta_psid` values:\n")
eu25games2019 |>
  distinct(meta_psid) |>
  nrow()

cat("\nDistinct `meta_pid` values:\n")
eu25games2019 |>
  distinct(meta_pid) |>
  nrow()

# row-key integrity: meta_responseid (expected: none) --------------------------
# anything > 0 here is a data-integrity issue, not respondent behaviour
cat("\n`meta_responseid` duplication (expected: none):\n")
eu25games2019 |>
  count(meta_responseid) |>
  filter(n > 1) |>
  summarise(duplicated_ids = n(), excess_rows = sum(n - 1))

# meta_psid duplication --------------------------------------------------------
# psid = sample-instance ID; collisions are usually partial+complete / re-entries
cat("\n`meta_psid` duplication (overall):\n")
eu25games2019 |>
  count(meta_psid) |>
  filter(n > 1) |>
  summarise(duplicated_psids = n(), excess_rows = sum(n - 1))

cat("\n`meta_psid` duplicate rows per wave:\n")
eu25games2019 |>
  count(meta_wave, meta_psid) |>
  filter(n > 1) |>
  summarise(
    duplicated_psids = n(),
    excess_rows = sum(n - 1),
    .by = meta_wave
  ) |>
  arrange(meta_wave)

# does any psid leak across waves? (it shouldn't, if it's per-assignment)
cat("\n`meta_psid` values spanning more than one wave:\n")
eu25games2019 |>
  distinct(meta_psid, meta_wave) |>
  count(meta_psid) |>
  filter(n > 1) |>
  nrow()

# meta_pid WITHIN-wave duplication --- the suspect case ------------------------
# same panelist appearing >1x in a single wave (re-entry / partial+complete)
cat("\n`meta_pid` within-wave duplication, per wave:\n")
eu25games2019 |>
  count(meta_wave, meta_pid) |>
  filter(n > 1) |>
  summarise(duplicated_pids = n(), excess_rows = sum(n - 1), .by = meta_wave) |>
  arrange(meta_wave)

cat("\n`meta_pid` within-wave duplication (total across waves):\n")
eu25games2019 |>
  count(meta_wave, meta_pid) |>
  filter(n > 1) |>
  summarise(duplicated_pids = n(), excess_rows = sum(n - 1))

# cross-wave participation --- EXPECTED panel overlap, NOT duplication ---------
cat("\nPanelists by number of distinct waves participated:\n")
eu25games2019 |>
  distinct(meta_pid, meta_wave) |>
  count(meta_pid, name = "n_waves") |>
  count(n_waves, name = "n_panelists") |>
  arrange(n_waves)

cat("\nPanelists appearing in 2+ waves:\n")
eu25games2019 |>
  distinct(meta_pid, meta_wave) |>
  count(meta_pid, name = "n_waves") |>
  filter(n_waves > 1) |>
  nrow()
```

# Filter our respondents who did not participate in games (w2 and w3 only)

```{r}
#| label: filter-out-nongame-respondents
# pids of anyone who participated in at least one of w2 / w3
pids_in_games <- eu25games2019 |>
  filter(meta_wave %in% c(2, 3)) |>
  distinct(meta_pid) |>
  pull(meta_pid)

# keep all w2 + w3 rows; from w1 keep only pids that reappear in w2 or w3
eu25games2019 <- eu25games2019 |>
  filter(meta_wave %in% c(2, 3) | meta_pid %in% pids_in_games)

cat("Observations remaining:\n")
nrow(eu25games2019)

cat("\nObservations per wave:\n")
eu25games2019 |>
  count(meta_wave)

cat("\nDistinct panelists remaining:\n")
eu25games2019 |>
  distinct(meta_pid) |>
  nrow()
```

# Select clean covariate candidates

```{r}
#| label: select-cleaned-vars
eu25games2019 |>
  select(-contains("_raw")) |>
  select(contains("q_")) |>
  glimpse()
```

# Reshape to long format data for analyses

`eu25games2019` contains data in wide format, i.e., one row corresponds one survey response. To analyze outcomes, the data need to be transformed to long (tidy) format, with one row equal to one observation, in this case one row should be one game played.

```{r}
#| label: game-outcomes-to-long
# select relevant variables
eu25_games_long <- eu25games2019 |>
  # wave, country and respondent identifiers
  select(
    meta_wave,
    meta_country,
    meta_pid,
    # dictator game vars
    contains("cj_dict"),
    # trust game vars
    contains("cj_trust")
  ) |>
  # to long format
  pivot_longer(
    cols = -c(meta_wave, meta_country, meta_pid),
    names_to = c("game_type", "round", ".value"),
    names_pattern = "^(cj_dict|cj_trust)(\\d+)_(.+)$"
  ) |>
  # keep cj_ prefix for experimental vars
  rename_with(
    ~ paste0("cj_", .),
    -c(meta_wave, meta_country, meta_pid, game_type, round)
  ) |>
  # filter observations with valid outcomes
  filter(!is.na(cj_pl2))
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
