---
subtitle: |
  Nested Random Intercepts in `multibart` — Mechanism Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
  cache: true
---

# Purpose {#sec-purpose}

This notebook is a **scaffold**, not a finished analysis.
Its job is to test the nested-random-intercept extension added to the local `multibart` package (functions `nested_random_intercepts()` and `get_nested_random_intercepts_posteriors()` in `code/multibart/R/groups.R`).

The goals, in priority order, are:

1. **Verify the modified `multibart` works in principle.**
   On *synthetic* two-level data with known variance components we confirm the new helper builds a valid random-effects design, that both fitting paths (`bcf_continuous_linear` and `bcf_binary`) accept it and run, and that the posterior extractor returns correctly-shaped, correctly-labelled output that recovers the planted structure.
2. **See what the output looks like and how to process it downstream.**
   We fit on a small subsample of the real data (when it exists) and walk the posterior objects through to the tidy summaries and figures the manuscript will need.

::: callout-note
## Why nesting fits the existing sampler

The C++ MCMC sampler is already general over an arbitrary number of variance components `K` and an arbitrary random-effects design matrix `W` — it reads the dimensions off its inputs at runtime.
A nested respondent-within-country intercept model is just `W = [D_country | D_resp]` with a block-structured `q × 2` component-assignment matrix `Q` giving each grouping factor its own variance component.
Because respondent ids are globally unique, this dummy coding *is* nesting (each respondent dummy belongs to exactly one country).
This is the same `q × 2` mechanism `random_intercepts_slopes()` already uses for intercept + slope; we only swap the two blocks for two grouping factors.
:::

::: callout-warning
## The real risk is cost, not correctness

`W` is `n × (C + R)`.
At full scale that is roughly `112,500 × (25 + 37,500)`, and the sampler forms `WtW` (≈ 37.5k²) densely and solves a system of that order every iteration.
The correctness story is solid; the open question is whether the **dense** sampler runs in acceptable time and memory.
That is exactly why this notebook smoke-tests on synthetic data and then on a *few-country* subsample first.
If the dense fit proves prohibitive, the documented fallback (CLAUDE.md Open Question #1) is country random intercepts only, with respondent dependence handled by cluster-bootstrapped uncertainty.
:::

# Setup {#sec-setup}

The setup chunk loads the usual project packages plus `pkgload`, which lets us load the **local source** copy of `multibart` (compiling its C++ as needed) without installing it.
We point `load_all()` at `code/multibart` so we are testing the freshly edited package, not a stale installed one.

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # multi-panel figure
  "pkgload", # load local multibart source
  "sessioninfo", # session docs

  # for multibart dependencies -------------------------------------------------
  "Rcereal",
  "fastDummies"
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)

# local package
pkgload::load_all(here::here("code", "multibart"))
```

# Synthetic mechanism check {#sec-synthetic}

This is the primary test.
We generate data from a known additive two-level model so that we control the truth and can check the machinery end-to-end.

## Simulate two-level data {#sec-simulate}

The design mirrors the real structure: respondents nested in countries, several conjoint tasks per respondent.
Treatment `z` is randomized with a known propensity of 0.5 (as in the conjoint design), so no propensity model is needed.
Country and respondent intercepts are drawn from normals with **distinct** variances (`sigma_country` clearly larger than `sigma_resp`); recovering that separation is the key thing we want to see.
We keep the dimensions small so the dense `WtW` solve is trivial.

In plain language, the chunk below builds a fake dataset where we already know every answer, so we can check whether the model can rediscover it.
The pieces are:

- **The nesting structure** (`country_id`, `resp_id`): 8 countries, 25 respondents each, 3 tasks per respondent, for `n = 600` rows. Respondent ids are numbered globally (1…200), so each respondent belongs to exactly one country — that is what makes the structure *nested* rather than *crossed*.
- **The group offsets** (`b_country`, `b_resp`): each country gets its own baseline shift and each respondent gets a smaller one, drawn from normals whose SDs are the planted "variance components" we later try to recover. These stand in for the real-world fact that some countries (and some people) are simply more generous on average, for reasons we are not modelling and treat as nuisance.
- **The covariates** (`X`): four standard-normal columns `x1`–`x4`, the respondent/profile characteristics a real analysis would use to explain heterogeneity.
- **The prognostic surface** (`mu_x`): what the outcome looks like *before* any treatment, as a function of the covariates (here it rises with `x1` and falls with `x2`). In causal-forest language this is the "control" or confounding part — everything that drives the outcome but is not the treatment effect.
- **The true treatment effect** (`tau_x`): the quantity of substantive interest, and the thing BCF exists to estimate. It is deliberately *heterogeneous* — a step function that is `0.5` when `x3 <= 0` and `1.25` when `x3 > 0` — so we can later check that the model recovers not just an average effect but the way the effect *varies* across people.
- **The treatment** (`z`): a coin flip independent of everything else (propensity 0.5), exactly as a randomized conjoint attribute would be.
- **The outcome** (`y_cont`, `y_bin`): the linear predictor adds together the prognostic surface, the treatment effect applied only to treated units (`tau_x * z`), the country and respondent offsets, and noise. The continuous outcome is that sum directly; the binary outcome passes it through a probit link to produce 0/1 draws, mimicking the game-decision outcomes in the real data.

```{r}
#| label: simulate
set.seed(20260602)

# dimensions
n_country <- 8
n_resp_per_country <- 25
n_task <- 3

# nested ids
country_id <- factor(rep(
  seq_len(n_country),
  each = n_resp_per_country * n_task
))
resp_id <- factor(rep(seq_len(n_country * n_resp_per_country), each = n_task))
n <- length(resp_id)

# planted variance components
sigma_country <- 1.5
sigma_resp <- 0.5
b_country <- rnorm(n_country, 0, sigma_country)
b_resp <- rnorm(nlevels(resp_id), 0, sigma_resp)

# covariates, control function, heterogeneous tau
p <- 4
X <- matrix(rnorm(n * p), nrow = n)
colnames(X) <- paste0("x", seq_len(p))
mu_x <- 1.0 * X[, 1] - 0.5 * X[, 2]
tau_x <- 0.5 + 0.75 * (X[, 3] > 0)

# randomized treatment, known propensity 0.5
z <- rbinom(n, 1, 0.5)

# linear predictor with nested random intercepts on mu only
lin_pred <- mu_x +
  tau_x * z +
  b_country[as.integer(country_id)] +
  b_resp[as.integer(resp_id)]

# continuous and binary outcomes
y_cont <- lin_pred + rnorm(n, 0, 1)
y_bin <- rbinom(n, 1, pnorm(scale(lin_pred)[, 1]))
```

A quick `stopifnot()` guards the nesting invariant — every respondent must sit in exactly one country — and the basic dimensions.
Verification chunks like this are required after each data-prep step in this project.

```{r}
#| label: check-sim
# each respondent maps to exactly one country
resp_country_map <- tapply(as.integer(country_id), resp_id, function(v) {
  length(unique(v))
})
stopifnot(
  all(resp_country_map == 1),
  length(y_cont) == n,
  length(y_bin) == n,
  nrow(X) == n,
  all(sort(unique(z)) == c(0, 1))
)
```

## Build the nested random-effects design {#sec-build-re}

`nested_random_intercepts()` takes the two grouping factors (outer first, inner second) and returns the design `W`, the component-assignment matrix `Q`, the per-level dummies, and the block sizes used later by the extractor.
We assert the shape we expect: `W` is `n × (C + R)`, and `Q`'s columns sum to the two block sizes (so component 1 owns the country dummies and component 2 the respondent dummies).

```{r}
#| label: build-re
re <- nested_random_intercepts(country_id, resp_id)

C <- re$n_level1
R <- re$n_level2

stopifnot(
  nrow(re$randeff_design) == n,
  ncol(re$randeff_design) == C + R,
  ncol(re$randeff_variance_component_design) == 2,
  all(colSums(re$randeff_variance_component_design) == c(C, R)),
  all(rowSums(re$randeff_variance_component_design) == 1)
)
```

## Fit — continuous path {#sec-fit-cont}

`bcf_continuous_linear()` is the path for a continuous outcome.
The nested design is passed straight through the unchanged wrapper to the sampler.

Every argument in the call below, in order:

- **`y`** — the outcome vector (length `n`). The wrapper standardizes it internally (subtracts the mean, divides by SD) and back-transforms the posterior, so it is fine to pass on the raw scale.
- **`z`** — the binary treatment (0/1) whose effect `tau(x)` we want.
- **`x_control`** — the design matrix fed to the prognostic function `mu(x)` (the "control" part: covariates that explain the outcome absent treatment). Must be a numeric matrix.
- **`x_moderate`** — the design matrix fed to the treatment-effect function `tau(x)`; these are the candidate *moderators* the forest may split on to let the effect vary. We pass the same `X` for both, letting the model search the full covariate set for heterogeneity.
- **`zhat`** — the propensity `E(Z | X)`. Because treatment is randomized with known propensity 0.5, we pass the truth directly and skip any first-stage propensity model. (The binary path calls this argument `pihat`.)
- **`randeff_design`** — `W`, the `n x (C + R)` matrix of group dummies (country block then respondent block) built by `nested_random_intercepts()`. Each row places its observation in one country column and one respondent column.
- **`randeff_variance_component_design`** — `Q`, the `(C + R) x K` matrix telling the sampler which variance component governs each column of `W`. With `K = 2`, column 1 flags the country dummies and column 2 the respondent dummies, so the two levels shrink independently.
- **`randeff_scales`** — the prior scale for each of the `K` variance components; see the note below on why its *length* is what matters.
- **`randeff_df`** — degrees of freedom for the half-t prior on each random-intercept SD. Smaller values are heavier-tailed (more permissive of large group variance); `3` is the package default.
- **`nburn`** — burn-in iterations run and then discarded so the chain can reach its stationary distribution.
- **`nsim`** — post-burn-in iterations actually saved as posterior draws (the row dimension of every posterior matrix in the output).
- **`update_interval`** — how often (in iterations) the sampler prints a progress line; see the console note below.

Two call-site details deserve emphasis:

- **`randeff_scales` must be length `K = 2`.**
  The sampler indexes `randeff_scales(ii)` for each variance component, so a scalar default would be out of bounds with two components.
  We pass one scale per level.
  (A pre-existing quirk means the scale value currently cancels in the prior, so only its *length* matters today; we still pass sensible values for clarity and forward-compatibility.)
- **Short MCMC.** This is a smoke test, so `nburn`/`nsim` are small. Real fits use far longer chains.

::: callout-note
## What prints to the console while it runs

With `text_trace = TRUE` (set inside the wrapper), the sampler narrates itself.
First come one-off setup lines: `Using random effects.`, `Reading in y`, `Setting up designs` / `Setting up forests` (with a line per design reporting how many covariate columns were instantiated), and finally `Done.` followed by `Beginning MCMC:`.
If you do **not** see `Using random effects.`, the random-effects block was not detected — the nested design did not reach the sampler.

Then, every `update_interval` iterations, it prints a single progress line:

```
iteration: 450 sigma/SD(Y): 0.83
```

`iteration` counts through the full `nburn + nsim` run, so it is the live progress meter.
`sigma/SD(Y)` is the current residual SD expressed as a fraction of the outcome's SD (recall `y` is standardized internally): values well below 1 mean the model is explaining a good share of the outcome variance.
What you want to see is this number *wandering around a stable level* once burn-in is past — a value still drifting downward at the end of the run is a sign the chain has not converged and `nburn` was too short.
:::

```{r}
#| label: fit-cont
fit_cont <- bcf_continuous_linear(
  y = y_cont,
  z = z,
  x_control = X,
  x_moderate = X,
  zhat = rep(0.5, n), # known propensity
  randeff_design = re$randeff_design,
  randeff_variance_component_design = re$randeff_variance_component_design,
  randeff_scales = c(1, 1), # length K = 2
  randeff_df = 3,
  nburn = 2000,
  nsim = 2000,
  update_interval = 50
)
```

## Fit — binary path {#sec-fit-bin}

`bcf_binary()` is the path for a 0/1 outcome and carries the identical random-effects block, so the *same* `re` object works unchanged.
Every argument means exactly what it does in the continuous call (@sec-fit-cont), with one rename: the known propensity is passed as **`pihat`** rather than `zhat`.
Internally this path adds a probit data-augmentation step, so the model operates on a latent continuous scale underneath the binary outcome.
Here the recovered random-intercept scales live on that latent (probit-like) scale, so they will not numerically match the continuous-outcome truth — for the binary path the test is simply that it **accepts the nested design, runs, and returns correctly-shaped output**.

```{r}
#| label: fit-bin
fit_bin <- bcf_binary(
  y = y_bin,
  z = z,
  x_control = X,
  x_moderate = X,
  pihat = rep(0.5, n), # known propensity
  randeff_design = re$randeff_design,
  randeff_variance_component_design = re$randeff_variance_component_design,
  randeff_scales = c(1, 1), # length K = 2
  randeff_df = 3,
  nburn = 2000,
  nsim = 2000,
  update_interval = 50
)
```

## What the fitted object contains {#sec-fit-object}

Both paths return a list of class `bcf_fit` with the same backbone.
Knowing its slots is what makes the extraction and downstream steps below legible.
Every posterior matrix has `nsim` rows (one per saved draw); columns are observations or groups as noted.

- **`$sigma`** — length-`nsim` vector: the residual SD posterior, back-transformed to the original outcome scale.
- **`$yhat`** — `nsim x n` matrix: posterior of the fitted values (full prediction including random intercepts), on the original scale.
- **`$random_effects`** — `nsim x (C + R)` matrix: the random-intercept coefficient draws. Columns follow the design `W`, so the first `C` are the country intercepts and the next `R` are the respondent intercepts. This is what `get_nested_random_intercepts_posteriors()` slices and labels.
- **`$random_effects_sd`** — `nsim x K` matrix (here `K = 2`): the variance-component SD draws, column 1 for the country level and column 2 for the respondent level. These are the planted `sigma_country` / `sigma_resp` we try to recover.
- **`$control_fit`** — a list describing the fitted prognostic forest `mu(x)`: `tree_samples` (the live forest object), `str` (a serialized string of the same, which survives saving/reloading), and the `scale` / `shift` used to undo the internal standardization. Pass this to `get_forest_fit()` to read `mu(x)` back out.
- **`$moderate_fit`** — the same structure for the treatment-effect forest `tau(x)`; its `shift` is 0 because `tau` is a difference.
- **(binary path only)** `$mu_scale` and `$tau_scale` — length-`nsim` posterior draws of the global scale parameters for the two forests.

Note that `tau(x)` and `mu(x)` are **not** stored as ready-made `nsim x n` matrices on this object (the relevant lines are commented out in the wrapper); they are recovered on demand from `$moderate_fit` / `$control_fit` with `get_forest_fit()`, which is exactly what @sec-recovery does.

## Extract and verify the posteriors {#sec-extract}

`get_nested_random_intercepts_posteriors()` slices the fitted random coefficients into the country block (`1:C`) and respondent block (`(C+1):(C+R)`), labels each from the stored dummies, and pulls the two variance-component SD posteriors.
We run it on both fits and assert the output shapes; for the continuous fit we also check that the recovered posterior-mean SDs **separate** in the right direction (country SD clearly larger than respondent SD), matching the planted truth.

```{r}
#| label: extract
post_cont <- get_nested_random_intercepts_posteriors(fit_cont, re)
post_bin <- get_nested_random_intercepts_posteriors(fit_bin, re)

# shape checks: C + R coefficients, two SD columns
stopifnot(
  ncol(fit_cont$random_effects) == C + R,
  ncol(fit_cont$random_effects_sd) == 2,
  ncol(post_cont$level1_posterior) == C,
  ncol(post_cont$level2_posterior) == R,
  ncol(post_bin$level1_posterior) == C,
  ncol(post_bin$level2_posterior) == R
)

# posterior-mean variance components (continuous path)
sd_country_hat <- mean(post_cont$level1_sd)
sd_resp_hat <- mean(post_cont$level2_sd)

cat(
  "planted   sigma_country / sigma_resp:",
  sigma_country,
  "/",
  sigma_resp,
  "\n"
)
cat(
  "recovered sigma_country / sigma_resp:",
  round(sd_country_hat, 3),
  "/",
  round(sd_resp_hat, 3),
  "\n"
)

# the two components should separate in the right direction
stopifnot(sd_country_hat > sd_resp_hat)
```

If the planted and recovered scales are in the same ballpark and ordered correctly, the nested extension is working as intended.
Exact recovery is not expected from a 200-iteration smoke test on a small sample.

## True vs. recovered covariate effects {#sec-recovery}

The variance-component check above confirms the random-effects machinery, but the substantive payload of BCF is the two covariate functions: the prognostic surface $\mu(x)$ and the treatment-effect surface $\tau(x)$.
We pull per-observation posterior means of both straight from the fitted forests with `get_forest_fit()` — passing `Z = NULL` returns the leaf coefficients (here $\mu$ and $\tau$) rather than fitted values.
Because the prognostic function is identified only up to the global intercept and the random intercepts, we compare $\mu(x)$ in centred form; $\tau(x)$ is identified directly and is compared on its natural scale.

We do this for **both** fitted models, and present them as two separate figures, because they are read differently:

- The **continuous-outcome model** (@fig-recovery-cont) is the genuine numerical recovery check. The recovered effects and the planted truth are on the same scale, so the 45° identity line means "perfect recovery" and the points should hug it.
- The **binary-outcome model** (@fig-recovery-bin) recovers effects on the latent probit scale (see @sec-fit-bin), which is compressed relative to the continuous-scale truth. The 45° line therefore does **not** apply; what we look for instead is that recovered effects *rise* with the truth and that the two $\tau(x)$ groups separate in the right order. We mark a fitted linear trend rather than the identity.

```{r}
#| label: recover-effects
# per-observation posterior means of mu(x) and tau(x) from one fit
extract_recovery <- function(fit) {
  tau_draws <- get_forest_fit(fit$moderate_fit, X)
  mu_draws <- get_forest_fit(fit$control_fit, X)
  bind_rows(
    tibble(
      effect = "Treatment effect",
      truth = tau_x,
      estimate = colMeans(tau_draws)
    ),
    tibble(
      effect = "Prognostic effect",
      truth = mu_x - mean(mu_x),
      estimate = colMeans(mu_draws) - mean(colMeans(mu_draws))
    )
  )
}

recovery_cont <- extract_recovery(fit_cont)
recovery_bin <- extract_recovery(fit_bin)
```

Each figure plots recovered against true effect for the two surfaces.
For the continuous model the dashed line is the 45° identity (perfect recovery); for the binary model it is a fitted linear trend, since the latent scale rules the identity out.
$\tau(x)$ is a planted step function (two true values, low for `x3 <= 0` and high for `x3 > 0`), so its recovered cloud should sit higher at the larger true value — the expected partial-pooling shrinkage pulls the two clouds gently toward the centre.

```{r}
#| label: recovery-panel
# one scatter panel; reference layer is the identity line or a fitted trend
recovery_panel <- function(dat, ttl, reference = c("identity", "trend")) {
  reference <- match.arg(reference)
  ref_layer <- if (reference == "identity") {
    geom_abline(
      slope = 1,
      intercept = 0,
      linetype = "dashed",
      colour = "grey50"
    )
  } else {
    geom_smooth(
      method = "lm",
      se = FALSE,
      linetype = "dashed",
      colour = "grey50"
    )
  }
  dat |>
    ggplot(aes(x = truth, y = estimate)) +
    ref_layer +
    geom_point(alpha = 0.3, colour = "#0072B2") +
    labs(title = ttl, x = "True effect", y = "Posterior mean") +
    ggpubr::theme_pubr()
}
```

```{r}
#| label: fig-recovery-cont
#| fig-cap: "Continuous-outcome model. True (data-generating) covariate effects vs. recovered posterior means: prognostic mu(x) (centred) and treatment effect tau(x). Dashed line is the 45° identity (perfect recovery); points are individual observations. Smoke-test fit, small sample."
#| dpi: 500
p_mu_c <- recovery_cont |>
  filter(effect == "Prognostic effect") |>
  recovery_panel("Prognostic surface mu(x)", reference = "identity")
p_tau_c <- recovery_cont |>
  filter(effect == "Treatment effect") |>
  recovery_panel("Treatment effect tau(x)", reference = "identity")

(p_mu_c + p_tau_c) +
  patchwork::plot_annotation(
    title = "Continuous-outcome model: true vs. recovered effects"
  )
```

```{r}
#| label: fig-recovery-bin
#| fig-cap: "Binary-outcome model. Recovered effects are on the latent probit scale and so are compressed relative to the continuous-scale truth; the 45° identity does not apply, and the dashed line is a fitted linear trend. The check is that recovered effects rise with the truth and that the tau(x) clouds separate in the right order. Smoke-test fit, small sample."
#| dpi: 500
p_mu_b <- recovery_bin |>
  filter(effect == "Prognostic effect") |>
  recovery_panel("Prognostic surface mu(x)", reference = "trend")
p_tau_b <- recovery_bin |>
  filter(effect == "Treatment effect") |>
  recovery_panel("Treatment effect tau(x)", reference = "trend")

(p_mu_b + p_tau_b) +
  patchwork::plot_annotation(
    title = "Binary-outcome model: true vs. recovered effects (latent scale)"
  )
```

# Processing the output downstream {#sec-downstream}

This section shows the shape of what we get back and how to turn it into the tidy objects the manuscript figures consume.
The random-effects posteriors are `draws × group` matrices; we melt them to long form and summarize per group.

```{r}
#| label: tidy-re
# country-level intercept posterior -> long tidy summary
country_re_summary <- post_cont$level1_posterior |>
  as_tibble() |>
  mutate(.draw = row_number()) |>
  pivot_longer(-.draw, names_to = "country", values_to = "intercept") |>
  summarise(
    post_mean = mean(intercept),
    lower = quantile(intercept, 0.05),
    upper = quantile(intercept, 0.95),
    .by = country
  )

country_re_summary
```

A caterpillar plot of the country intercepts is the kind of appendix-only clustering diagnostic the analysis plan calls for (country structure is a nuisance, shown only to justify the RE specification).
The chunk below is a template following the project figure conventions; it is not rendered here.

```{r}
#| label: fig-country-re
#| fig-cap: "Posterior country-level random intercepts (synthetic smoke-test data), with 90% credible intervals. Diagnostic only."
#| dpi: 500
country_re_summary |>
  mutate(country = fct_reorder(country, post_mean)) |>
  ggplot(aes(x = post_mean, y = country)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper)) +
  labs(
    title = "Country-level random intercepts",
    x = "Posterior intercept",
    y = "Country"
  ) +
  ggpubr::theme_pubr()
```

The treatment-effect posterior — recovered from `fit_cont$moderate_fit` via `get_forest_fit()` as in @sec-recovery, not stored as a `$tau` slot — and the variance-component SD posteriors (`post_cont$level1_sd`, `post_cont$level2_sd`) are processed the same way: melt, summarize, plot.
The respondent block (`post_cont$level2_posterior`) is large (`R` columns) and is generally summarized in aggregate (e.g. the distribution of posterior-mean respondent intercepts) rather than plotted per respondent.

# Small-subsample fit on real data {#sec-subsample}

::: callout-important
The cells below are placeholders.
They depend on the prepared analysis tibble from `01_prep_hte`, which does **not exist yet**.
Once it does, point the read at the real file, choose the outcome (Dictator or Trust), and pick the fitting path that matches its coding.
:::

The intent: subset to a handful of countries, fit the nested model, and confirm the *real* data flows through the same machinery — and, critically, gauge the dense `WtW` cost before attempting the full ~37.5k-respondent fit.

```{r}
#| label: load-subsample
# TODO: replace with real 01_prep_hte output
# dat <- readRDS(here::here("data", "hte_dictator.rds"))

# few-country subsample to bound the dense WtW cost
# few_countries <- levels(factor(dat$country_id))[1:3]
# sub <- dat |> filter(country_id %in% few_countries) |>
#   mutate(across(c(country_id, respondent_id), fct_drop))
```

```{r}
#| label: fit-subsample
# re_sub <- nested_random_intercepts(sub$country_id, sub$respondent_id)
#
# fit_sub <- bcf_continuous_linear(   # or bcf_binary, per outcome coding
#   y = sub$y,
#   z = sub$z,
#   x_control = sub_X,                # numeric model matrix of moderators
#   x_moderate = sub_X,
#   zhat = rep(0.5, nrow(sub)),       # known conjoint propensity
#   randeff_design = re_sub$randeff_design,
#   randeff_variance_component_design = re_sub$randeff_variance_component_design,
#   randeff_scales = c(1, 1),         # length K = 2
#   randeff_df = 3,
#   nburn = 1000,
#   nsim = 1000
# )
#
# post_sub <- get_nested_random_intercepts_posteriors(fit_sub, re_sub)
```

Record the wall-clock time and peak memory of this subsample fit.
Extrapolating the dense solve from a few countries to all 25 (and from a few hundred respondents to ~37.5k) is what decides whether full nested REs are viable in the project window or whether the country-REs-only fallback is the pragmatic call.

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
