---
subtitle: |
  Nested Random Intercepts in `multibart` — Mechanism Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Purpose {#sec-purpose}

This notebook is a **scaffold**, not a finished analysis.
Its job is to test the nested-random-intercept extension added to the local `multibart` package (functions `nested_random_intercepts()` and `get_nested_random_intercepts_posteriors()` in `code/multibart/R/groups.R`).

The goals, in priority order, are:

1. **Verify the modified `multibart` works in principle.**
   On *synthetic* two-level data with known variance components we confirm the new helper builds a valid random-effects design, that the continuous fitting path (`bcf_continuous_linear`) accepts it and runs, and that the posterior extractor returns correctly-shaped, correctly-labelled output that recovers the planted structure.
2. **See what the output looks like and how to process it downstream.**
   We fit on a small subsample of the real data (when it exists) and walk the posterior objects through to the tidy summaries and figures the manuscript will need.

::: callout-note
## Why nesting fits the existing sampler

The C++ MCMC sampler is already general over an arbitrary number of variance components `K` and an arbitrary random-effects design matrix `W` — it reads the dimensions off its inputs at runtime.
A nested respondent-within-country intercept model is just `W = [D_country | D_resp]` with a block-structured `q × 2` component-assignment matrix `Q` giving each grouping factor its own variance component.
Because respondent ids are globally unique, this dummy coding *is* nesting (each respondent dummy belongs to exactly one country).
This is the same `q × 2` mechanism `random_intercepts_slopes()` already uses for intercept + slope; we only swap the two blocks for two grouping factors.
:::

::: callout-warning
## The real risk is cost, not correctness

`W` is `n × (C + R)`.
At full scale that is roughly `112,500 × (25 + 37,500)`, and the sampler forms `WtW` (≈ 37.5k²) densely and solves a system of that order every iteration.
The correctness story is solid; the open question is whether the **dense** sampler runs in acceptable time and memory.
That is exactly why this notebook smoke-tests on synthetic data and then on a *few-country* subsample first.
If the dense fit proves prohibitive, the documented fallback (CLAUDE.md Open Question #1) is country random intercepts only, with respondent dependence handled by cluster-bootstrapped uncertainty.
:::

# Setup {#sec-setup}

The setup chunk loads the usual project packages the normal way, including `multibart`'s own dependencies (`Rcpp`, `RcppArmadillo`, `Rcereal`, `fastDummies`), so they are installed and attached before the local package is touched.

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # multi-panel figure
  "sessioninfo", # session docs

  # multibart dependencies -----------------------------------------------------
  "Rcpp", # multibart Depends + LinkingTo
  "RcppArmadillo", # multibart Depends + LinkingTo
  "Rcereal", # multibart Depends + LinkingTo
  "fastDummies" # multibart helper dependency
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

## Local multibart package {#sec-multibart}

`multibart` lives only as source under `code/multibart`; it is not on CRAN.
Loading it with `pkgload::load_all()` puts it in memory but not on `.libPaths()` — fine interactively, but it breaks under `quarto render`, where instantiating its Rcpp module (`tree_samples`) calls `library("multibart")` and fails because no *installed* copy exists.
So we install the local source once (compiling its C++), then attach it with `library()` like any other package — robust for both interactive use and rendering.

```{r}
#| label: setup-multibart
#| include: false
# install local source on first use
if (!requireNamespace("multibart", quietly = TRUE)) {
  install.packages(
    here::here("code", "multibart"),
    repos = NULL,
    type = "source"
  )
}
# attach installed package
library(multibart)
```

::: callout-note
The chunk above only auto-installs when the package is *missing*, not when its source changes.
After editing `multibart`'s C++ or R code, reinstall to pick it up:
`install.packages(here::here("code", "multibart"), repos = NULL, type = "source")`.
:::

# Synthetic mechanism check {#sec-synthetic}

This is the primary test.
We generate data from a known additive two-level model so that we control the truth and can check the machinery end-to-end.

## Simulate two-level data {#sec-simulate}

The design mirrors the real structure: respondents nested in countries, several conjoint tasks each, with treatment randomized at a known propensity of 0.5 (the conjoint design) so no propensity model is needed.
The two random-intercept variances are deliberately distinct (`sigma_country` well above `sigma_resp`) — recovering that separation is the key check — and the dimensions are small so the dense `WtW` solve is trivial.
Per-quantity detail is in the chunk comments below.

A correct fit should recover a heterogeneous `tau(x)` stepping from ~`0.5` to ~`1.25` across `x3 = 0` (average ~`0.875`), the linear `mu(x)` shape in `x1`/`x2`, and two clearly separated variance components with `sigma_country` (1.5) above `sigma_resp` (0.5).

```{r}
#| label: simulate
set.seed(20260602)

# dimensions: 8 countries x 25 respondents x 3 tasks = 600 rows
n_country <- 8
n_resp_per_country <- 25
n_task <- 3

# nested ids; respondent ids are globally unique, so each sits in one country
# (dummy coding that is nesting, not crossing)
country_id <- factor(rep(
  seq_len(n_country),
  each = n_resp_per_country * n_task
))
resp_id <- factor(rep(seq_len(n_country * n_resp_per_country), each = n_task))
n <- length(resp_id)

# planted variance components, country spread deliberately >> respondent spread
sigma_country <- 1.5
sigma_resp <- 0.5
# group offsets: per-country and per-respondent baseline shifts (nuisance)
b_country <- rnorm(n_country, 0, sigma_country)
b_resp <- rnorm(nlevels(resp_id), 0, sigma_resp)

# covariates: candidate moderators a real analysis would split on
p <- 4
X <- matrix(rnorm(n * p), nrow = n)
colnames(X) <- paste0("x", seq_len(p))
# prognostic (control) surface: linear, flat in x3/x4
mu_x <- 1.0 * X[, 1] - 0.5 * X[, 2]
# heterogeneous treatment effect: step in x3, 0.5 -> 1.25 (average ~0.875)
tau_x <- 0.5 + 0.75 * (X[, 3] > 0)

# randomized treatment, known propensity 0.5
z <- rbinom(n, 1, 0.5)

# linear predictor: prognostic + effect-on-treated + nested intercepts (mu only)
lin_pred <- mu_x +
  tau_x * z +
  b_country[as.integer(country_id)] +
  b_resp[as.integer(resp_id)]

# continuous outcome: linear predictor + residual noise (SD 1)
y_cont <- lin_pred + rnorm(n, 0, 1)
```

A `stopifnot()` guards the nesting invariant — every respondent must sit in exactly one country — and the basic dimensions.

```{r}
#| label: check-sim
# each respondent maps to exactly one country
resp_country_map <- tapply(as.integer(country_id), resp_id, function(v) {
  length(unique(v))
})
stopifnot(
  all(resp_country_map == 1),
  length(y_cont) == n,
  nrow(X) == n,
  all(sort(unique(z)) == c(0, 1))
)
```

## Build the nested random-effects design {#sec-build-re}

`nested_random_intercepts()` takes the two grouping factors (outer first, inner second) and returns the design `W`, the component-assignment matrix `Q`, the per-level dummies, and the block sizes used later by the extractor.
We assert the shape we expect: `W` is `n × (C + R)`, and `Q`'s columns sum to the two block sizes (so component 1 owns the country dummies and component 2 the respondent dummies).

```{r}
#| label: build-re
re <- nested_random_intercepts(country_id, resp_id)

C <- re$n_level1
R <- re$n_level2

stopifnot(
  nrow(re$randeff_design) == n,
  ncol(re$randeff_design) == C + R,
  ncol(re$randeff_variance_component_design) == 2,
  all(colSums(re$randeff_variance_component_design) == c(C, R)),
  all(rowSums(re$randeff_variance_component_design) == 1)
)
```

## Fit — continuous path {#sec-fit-cont}

`bcf_continuous_linear()` is the continuous-outcome path; the nested design passes straight through the unchanged wrapper to the sampler.

Arguments, in call order:

- **`y`** — outcome vector (length `n`); the wrapper standardizes internally and back-transforms, so the raw scale is fine.
- **`z`** — binary treatment (0/1) whose effect `tau(x)` we want.
- **`x_control`** — numeric design for the prognostic function `mu(x)` (covariates explaining the outcome absent treatment).
- **`x_moderate`** — design for `tau(x)`: the candidate *moderators* the forest may split on. We pass the same `X` for both, searching the full set for heterogeneity.
- **`zhat`** — propensity `E(Z | X)`. Randomized at known 0.5, so we pass the truth and skip first-stage estimation.
- **`randeff_design`** — `W`, the `n x (C + R)` group-dummy matrix (country block then respondent block) from `nested_random_intercepts()`.
- **`randeff_variance_component_design`** — `Q`, the `(C + R) x K` map from each `W` column to its variance component; with `K = 2`, country and respondent levels shrink independently.
- **`randeff_scales`** — prior scale per variance component (must be length `K`; see below).
- **`randeff_df`** — half-t degrees of freedom for each random-intercept SD (`3`, the package default; smaller = heavier-tailed).
- **`nburn`, `nsim`** — burn-in (discarded) and saved draws; `nsim` is the row dimension of every posterior matrix.
- **`update_interval`** — iterations between progress lines (see console note).

Two call-site details matter:

- **`randeff_scales` must be length `K = 2`** — the sampler indexes one scale per component, so a scalar would be out of bounds. (A pre-existing quirk cancels the value in the prior, so only the length matters today; we pass sensible values anyway.)
- **Short MCMC** — this is a smoke test; real fits use far longer chains.

::: callout-note
## What healthy console output looks like

The wrapper first warns `All values of zhat are equal. zhat will not be included among covariates` — expected: a constant known propensity carries no information to split on, so the sampler drops it.

With `text_trace = TRUE`, the sampler then narrates setup.
The diagnostic line to look for is `Using random effects.`; without it, the nested design never reached the sampler.
The two BART designs (`design 0` = `mu(x)`, `design 1` = `tau(x)`) should each report four covariate columns.

Every `update_interval` iterations it prints a progress line, e.g. `iteration: 500 sigma/SD(Y): 0.542733`.
`sigma/SD(Y)` is the residual SD on the standardized-`y` scale; here it drops to ~`0.5` within 50 iterations and then holds in a stable `0.47–0.57` band — the model captures most of the variance and the chain has converged.
A value still drifting downward at the end would mean `nburn` was too short.
:::

```{r}
#| label: fit-cont
fit_cont <- bcf_continuous_linear(
  y = y_cont,
  z = z,
  x_control = X,
  x_moderate = X,
  zhat = rep(0.5, n), # known propensity
  randeff_design = re$randeff_design,
  randeff_variance_component_design = re$randeff_variance_component_design,
  randeff_scales = c(1, 1), # length K = 2
  randeff_df = 3,
  nburn = 2000,
  nsim = 2000,
  update_interval = 50
)
```

## What the fitted object contains {#sec-fit-object}

The fit returns a list of class `bcf_fit`; its slots drive the extraction and downstream steps below.
Every posterior matrix has `nsim` rows (one per saved draw); columns are observations or groups as noted.

- **`$sigma`** — length-`nsim` vector: the residual SD posterior, back-transformed to the original outcome scale.
- **`$yhat`** — `nsim x n` matrix: posterior of the fitted values (full prediction including random intercepts), on the original scale.
- **`$random_effects`** — `nsim x (C + R)` matrix: the random-intercept coefficient draws. Columns follow the design `W`, so the first `C` are the country intercepts and the next `R` are the respondent intercepts. This is what `get_nested_random_intercepts_posteriors()` slices and labels.
- **`$random_effects_sd`** — `nsim x K` matrix (here `K = 2`): the variance-component SD draws, column 1 for the country level and column 2 for the respondent level. These are the planted `sigma_country` / `sigma_resp` we try to recover.
- **`$control_fit`** — a list describing the fitted prognostic forest `mu(x)`: `tree_samples` (the live forest object), `str` (a serialized string of the same, which survives saving/reloading), and the `scale` / `shift` used to undo the internal standardization. Pass this to `get_forest_fit()` to read `mu(x)` back out.
- **`$moderate_fit`** — the same structure for the treatment-effect forest `tau(x)`; its `shift` is 0 because `tau` is a difference.

Note that `tau(x)` and `mu(x)` are **not** stored as ready-made `nsim x n` matrices on this object (the relevant lines are commented out in the wrapper); they are recovered on demand from `$moderate_fit` / `$control_fit` with `get_forest_fit()`, which is exactly what @sec-recovery does.

## Extract and verify the posteriors {#sec-extract}

`get_nested_random_intercepts_posteriors()` slices the fitted random coefficients into the country block (`1:C`) and respondent block (`(C+1):(C+R)`), labels each from the stored dummies, and pulls the two variance-component SD posteriors.
We run it on the fit and assert the output shapes; we also check that the recovered posterior-mean SDs **separate** in the right direction (country SD clearly larger than respondent SD), matching the planted truth.

```{r}
#| label: extract
post_cont <- get_nested_random_intercepts_posteriors(fit_cont, re)

# shape checks: C + R coefficients, two SD columns
stopifnot(
  ncol(fit_cont$random_effects) == C + R,
  ncol(fit_cont$random_effects_sd) == 2,
  ncol(post_cont$level1_posterior) == C,
  ncol(post_cont$level2_posterior) == R
)

# posterior-mean variance components (continuous path)
sd_country_hat <- mean(post_cont$level1_sd)
sd_resp_hat <- mean(post_cont$level2_sd)

cat(
  "planted   sigma_country / sigma_resp:",
  sigma_country,
  "/",
  sigma_resp,
  "\n"
)
cat(
  "recovered sigma_country / sigma_resp:",
  round(sd_country_hat, 3),
  "/",
  round(sd_resp_hat, 3),
  "\n"
)

# the two components should separate in the right direction
stopifnot(sd_country_hat > sd_resp_hat)
```

In the rendered fit the comparison reads `planted 1.5 / 0.5` against `recovered 1.072 / 0.384`: the right order (country above respondent), the right ballpark, and a ratio (≈2.8) close to the true 3.0, so the two levels are being shrunk separately — the property under test.
Both are biased *downward*, most visibly the country SD: with only `C = 8` level-1 groups there is little information to pin the between-country variance down, and the half-t prior pulls it toward zero.
That is expected partial pooling at this scale, not a defect — exact recovery is not the goal of a smoke test, and no formal coverage is claimed.
Scales in the same ballpark and correctly ordered mean the nested extension works.

## True vs. recovered covariate effects {#sec-recovery}

The variance-component check above confirms the random-effects machinery, but the substantive payload of BCF is the two covariate functions: the prognostic surface $\mu(x)$ and the treatment-effect surface $\tau(x)$.
We pull per-observation posterior means of both straight from the fitted forests with `get_forest_fit()` — passing `Z = NULL` returns the leaf coefficients (here $\mu$ and $\tau$) rather than fitted values.
Because the prognostic function is identified only up to the global intercept and the random intercepts, we compare $\mu(x)$ in centred form; $\tau(x)$ is identified directly and is compared on its natural scale.

This is the genuine numerical recovery check (@fig-recovery-cont): recovered effects and the planted truth are on the same scale, so the 45° identity line means "perfect recovery" and the points should hug it.

::: callout-note
## The planted truth we are checking against

From @sec-simulate, the data-generating values the figures below should reproduce:

- **$\tau(x)$** — a step function: $0.5$ when $x_3 \le 0$, $1.25$ when $x_3 > 0$ (average $\approx 0.875$).
- **$\mu(x)$** — linear, $1.0\,x_1 - 0.5\,x_2$, compared in centred form.
- **Variance components** — $\sigma_{\text{country}} = 1.5$, $\sigma_{\text{resp}} = 0.5$ (recovered and checked in @sec-extract).
:::

```{r}
#| label: recover-effects
# per-observation posterior means of mu(x) and tau(x); mu centred for identifiability
extract_recovery <- function(fit) {
  tau_draws <- get_forest_fit(fit$moderate_fit, X)
  mu_draws <- get_forest_fit(fit$control_fit, X)
  bind_rows(
    tibble(
      effect = "Treatment effect",
      truth = tau_x,
      estimate = colMeans(tau_draws)
    ),
    tibble(
      effect = "Prognostic effect",
      truth = mu_x - mean(mu_x),
      estimate = colMeans(mu_draws) - mean(colMeans(mu_draws))
    )
  )
}

recovery_cont <- extract_recovery(fit_cont)
```

The figure plots recovered against true effect, with the dashed 45° identity as the perfect-recovery reference.
$\tau(x)$ is a planted step function (low for `x3 <= 0`, high for `x3 > 0`), so its recovered cloud should sit higher at the larger true value — the expected partial-pooling shrinkage pulls the two clouds gently toward the centre.

```{r}
#| label: recovery-panel
# one scatter panel against the 45-degree identity reference
recovery_panel <- function(dat, ttl) {
  dat |>
    ggplot(aes(x = truth, y = estimate)) +
    geom_abline(
      slope = 1,
      intercept = 0,
      linetype = "dashed",
      colour = "grey50"
    ) +
    geom_point(alpha = 0.3, colour = "#0072B2") +
    labs(title = ttl, x = "True effect", y = "Posterior mean") +
    ggpubr::theme_pubr()
}
```

```{r}
#| label: fig-recovery-cont
#| fig-cap: "Continuous-outcome model. True (data-generating) covariate effects vs. recovered posterior means: prognostic mu(x) (centred) and treatment effect tau(x). Dashed line is the 45° identity (perfect recovery); points are individual observations. Smoke-test fit, small sample."
#| dpi: 500
p_mu_c <- recovery_cont |>
  filter(effect == "Prognostic effect") |>
  recovery_panel("Prognostic surface mu(x)")
p_tau_c <- recovery_cont |>
  filter(effect == "Treatment effect") |>
  recovery_panel("Treatment effect tau(x)")

(p_mu_c + p_tau_c) +
  patchwork::plot_annotation(
    title = "Continuous-outcome model: true vs. recovered effects",
    subtitle = "Dashed line: 45° identity (perfect recovery)"
  )
```

# Processing the output downstream {#sec-downstream}

The random-effects posteriors are `draws × group` matrices; we melt them to long form and summarize per group — the tidy shape the manuscript figures consume.

```{r}
#| label: tidy-re
# country-level intercept posterior -> long tidy summary
country_re_summary <- post_cont$level1_posterior |>
  as_tibble() |>
  mutate(.draw = row_number()) |>
  pivot_longer(-.draw, names_to = "country", values_to = "intercept") |>
  summarise(
    post_mean = mean(intercept),
    lower = quantile(intercept, 0.05),
    upper = quantile(intercept, 0.95),
    .by = country
  ) |>
  # planted country intercepts: column k of level1_posterior is country k
  left_join(
    tibble(country = colnames(post_cont$level1_posterior), truth = b_country),
    by = "country"
  )

country_re_summary
```

A caterpillar plot of the country intercepts is the appendix-only clustering diagnostic the analysis plan calls for: country structure is a nuisance, shown only to justify the RE specification.

```{r}
#| label: fig-country-re
#| fig-cap: "Posterior country-level random intercepts (synthetic smoke-test data), with 90% credible intervals. Orange crosses mark the planted true country intercepts. Diagnostic only."
#| dpi: 500
country_re_summary |>
  mutate(country = fct_reorder(country, post_mean)) |>
  ggplot(aes(y = country)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(x = post_mean, xmin = lower, xmax = upper)) +
  geom_point(
    aes(x = truth, colour = "Planted truth"),
    shape = 4,
    size = 3,
    stroke = 1.2
  ) +
  scale_colour_manual(values = c("Planted truth" = "#D55E00"), name = NULL) +
  labs(
    title = "Country-level random intercepts",
    x = "Posterior intercept",
    y = "Country"
  ) +
  ggpubr::theme_pubr()
```

The treatment-effect posterior — recovered from `fit_cont$moderate_fit` via `get_forest_fit()` as in @sec-recovery, not stored as a `$tau` slot — and the variance-component SD posteriors (`post_cont$level1_sd`, `post_cont$level2_sd`) are processed the same way: melt, summarize, plot.
The respondent block (`post_cont$level2_posterior`) is large (`R` columns) and is generally summarized in aggregate (e.g. the distribution of posterior-mean respondent intercepts) rather than plotted per respondent.

# Small-subsample fit on real data {#sec-subsample}

::: callout-important
The cells below are placeholders.
They depend on the prepared analysis tibble from `01_prep_hte`, which does **not exist yet**.
Once it does, point the read at the real file and choose the outcome (Dictator or Trust).
:::

The intent: subset to a handful of countries, fit the nested model, and confirm the *real* data flows through the same machinery — and, critically, gauge the dense `WtW` cost before attempting the full ~37.5k-respondent fit.

```{r}
#| label: load-subsample
# TODO: replace with real 01_prep_hte output
# dat <- readRDS(here::here("data", "hte_dictator.rds"))

# few-country subsample to bound the dense WtW cost
# few_countries <- levels(factor(dat$country_id))[1:3]
# sub <- dat |> filter(country_id %in% few_countries) |>
#   mutate(across(c(country_id, respondent_id), fct_drop))
```

```{r}
#| label: fit-subsample
# re_sub <- nested_random_intercepts(sub$country_id, sub$respondent_id)
#
# fit_sub <- bcf_continuous_linear(
#   y = sub$y,
#   z = sub$z,
#   x_control = sub_X,                # numeric model matrix of moderators
#   x_moderate = sub_X,
#   zhat = rep(0.5, nrow(sub)),       # known conjoint propensity
#   randeff_design = re_sub$randeff_design,
#   randeff_variance_component_design = re_sub$randeff_variance_component_design,
#   randeff_scales = c(1, 1),         # length K = 2
#   randeff_df = 3,
#   nburn = 1000,
#   nsim = 1000
# )
#
# post_sub <- get_nested_random_intercepts_posteriors(fit_sub, re_sub)
```

Record the wall-clock time and peak memory of this subsample fit.
Extrapolating the dense solve from a few countries to all 25 (and from a few hundred respondents to ~37.5k) is what decides whether full nested REs are viable in the project window or whether the country-REs-only fallback is the pragmatic call.

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
