---
subtitle: |
  Nested Structure in `grf` Causal Forests — Mechanism Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
  cache: true
---

# Purpose {#sec-purpose}

This notebook is a **scaffold**, not a finished analysis.
It is the `grf` counterpart to `03_multibart_nested_ri_test.qmd`: where that notebook tests the hierarchical-BCF primary method, this one tests the **Causal Random Forest robustness strategy** on the same synthetic data so the two are directly comparable.

The goals, in priority order, are:

1. **Verify the proposed `grf` strategy works in principle.**
   On *synthetic* two-level data with known effects we confirm that `grf::causal_forest()` with country fixed effects in `X`, respondent-level `clusters`, and the known conjoint propensity recovers the planted average and heterogeneous treatment effects.
2. **See what the output looks like and how to process it downstream.**
   We walk the forest output through the headline quantities the manuscript needs — cluster-robust ATE, individual `τ̂(x)`, and the best linear projection onto the pre-specified moderators — and produce the same true-vs-recovered figure as the BCF test.

::: callout-note
## How `grf` handles the nesting

The data are observations nested in respondents nested in countries.
The robustness strategy accounts for both levels without random effects:

- **Country** enters as **fixed effects** — one-hot dummy columns appended to the covariate matrix `X`. `grf` requires a numeric `X`, so we encode the factor explicitly rather than passing it raw.
- **Respondent** enters through `clusters = respondent_id`. This gives honest, cluster-aware subsampling (whole respondents are held out together) and cluster-robust variance for the ATE, absorbing the within-person dependence across the three conjoint tasks.

This is the frequentist analogue of the BCF random-intercept specification: the same nuisance structure, addressed by FE + clustering instead of partial pooling.
:::

::: callout-note
## Cost is not the concern here

Unlike the dense `WtW` solve in the nested-RE BCF fit, `grf` scales comfortably to the full ~112,500 observations and ~37,500 respondent clusters.
The synthetic check below is about **correctness of the strategy**, not feasibility; the small dimensions just keep the smoke test fast.
:::

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # multi-panel figure
  "fastDummies", # country fixed-effect dummies
  "grf", # causal_forest robustness method
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Synthetic mechanism check {#sec-synthetic}

This is the primary test.
We reuse the **exact data-generating process** from the BCF notebook (same seed), so the two methods are tested on identical data and their recovered effects can be compared one-to-one.

## Simulate two-level data {#sec-simulate}

Respondents nested in countries, several conjoint tasks per respondent.
Treatment `z` is randomized with a known propensity of 0.5, as in the conjoint design.
Country and respondent intercepts are drawn from normals with distinct variances; for `grf` these are pure nuisance — country is handled by fixed effects, respondent by clustering.

In plain language, the chunk below builds a fake dataset where we already know every answer, so we can check whether the causal forest rediscovers it.
This is the **same** data-generating process and seed as the BCF notebook, so the two methods see identical data.
The pieces are:

- **The nesting structure** (`country_id`, `resp_id`): 8 countries, 25 respondents each, 3 tasks per respondent, for `n = 600` rows. Respondent ids are numbered globally (1…200), so each respondent belongs to exactly one country — that is what makes the structure *nested* rather than *crossed*.
- **The group offsets** (`b_country`, `b_resp`): each country gets its own baseline shift and each respondent a smaller one, drawn from normals whose SDs are the planted variance components. Here they are pure nuisance — the things country fixed effects and respondent clustering are meant to absorb — not quantities `grf` reports.
- **The covariates** (`X_mod`): four standard-normal columns `x1`–`x4`, the respondent/profile characteristics a real analysis would use to explain heterogeneity. (These become the *moderator* matrix; country dummies are appended later in @sec-build.)
- **The prognostic surface** (`mu_x`): what the outcome looks like *before* any treatment, as a function of the covariates (rising with `x1`, falling with `x2`). `grf` does not report this directly — it is partialled out via `Y.hat` — but it still drives the outcome and so must be generated.
- **The true treatment effect** (`tau_x`): the quantity of interest, and the thing the causal forest estimates. It is deliberately *heterogeneous* — a step function that is `0.5` when `x3 <= 0` and `1.25` when `x3 > 0` — so we can check the forest recovers not just an average effect but the way it *varies*.
- **The treatment** (`z`): a coin flip independent of everything else (propensity 0.5), exactly as a randomized conjoint attribute would be.
- **The outcome** (`y`): the linear predictor sums the prognostic surface, the treatment effect applied only to treated units (`tau_x * z`), the country and respondent offsets, and noise. Only a continuous outcome is generated here (the binary path is exercised in the BCF notebook).

```{r}
#| label: simulate
set.seed(20260602)

# dimensions
n_country <- 8
n_resp_per_country <- 25
n_task <- 3

# nested ids
country_id <- factor(rep(
  seq_len(n_country),
  each = n_resp_per_country * n_task
))
resp_id <- factor(rep(seq_len(n_country * n_resp_per_country), each = n_task))
n <- length(resp_id)

# planted variance components (nuisance)
sigma_country <- 1.5
sigma_resp <- 0.5
b_country <- rnorm(n_country, 0, sigma_country)
b_resp <- rnorm(nlevels(resp_id), 0, sigma_resp)

# covariates, prognostic function, heterogeneous tau
p <- 4
X_mod <- matrix(rnorm(n * p), nrow = n)
colnames(X_mod) <- paste0("x", seq_len(p))
mu_x <- 1.0 * X_mod[, 1] - 0.5 * X_mod[, 2]
tau_x <- 0.5 + 0.75 * (X_mod[, 3] > 0)

# randomized treatment, known propensity 0.5
z <- rbinom(n, 1, 0.5)

# linear predictor with nested intercepts on the prognostic part only
lin_pred <- mu_x +
  tau_x * z +
  b_country[as.integer(country_id)] +
  b_resp[as.integer(resp_id)]

# continuous outcome
y <- lin_pred + rnorm(n, 0, 1)
```

A `stopifnot()` guards the nesting invariant — every respondent sits in exactly one country — and the basic dimensions.

```{r}
#| label: check-sim
# each respondent maps to exactly one country
resp_country_map <- tapply(as.integer(country_id), resp_id, function(v) {
  length(unique(v))
})
stopifnot(
  all(resp_country_map == 1),
  length(y) == n,
  nrow(X_mod) == n,
  all(sort(unique(z)) == c(0, 1))
)
```

## Build covariates and clustering {#sec-build}

Two pieces encode the nesting.
Country fixed effects become one-hot dummy columns (one dropped to avoid collinearity with the intercept `grf` fits internally) appended to the moderator matrix.
Respondent ids become an integer cluster vector.
We assert the assembled `X` has the expected width (`p` moderators + `C − 1` country dummies) and that the cluster vector is the right length.

```{r}
#| label: build
# country fixed effects as dummy columns
country_fe <- fastDummies::dummy_cols(
  data.frame(country = country_id),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
) |>
  as.matrix()

# moderators + country FE
X <- cbind(X_mod, country_fe)

# respondent-level clusters
clusters <- as.integer(resp_id)

stopifnot(
  nrow(X) == n,
  ncol(X) == p + (n_country - 1),
  length(clusters) == n,
  dplyr::n_distinct(clusters) == n_country * n_resp_per_country
)
```

## Fit the causal forest {#sec-fit}

`causal_forest()` takes the numeric `X`, outcome `y`, and treatment `z`.
Every argument in the call below:

- **`X`** — the numeric covariate matrix: the `p` moderators plus the `C − 1` country fixed-effect dummies assembled in @sec-build. `grf` requires a numeric matrix, which is why country was one-hot encoded rather than passed as a factor.
- **`Y`** — the outcome vector.
- **`W`** — the treatment (here binary 0/1, but `grf` also accepts continuous treatments).
- **`W.hat`** — the propensity `E(W | X)`. Passing the scalar `0.5` fixes it at the known conjoint propensity for every observation, so `grf` skips its internal propensity regression (the analogue of passing known `zhat`/`pihat` to BCF). Left `NULL`, `grf` would estimate it with a regression forest.
- **`clusters`** — an integer vector assigning each row to a respondent. This switches on cluster-aware *honest* subsampling (whole respondents are held out together, never split across the sample-fitting and estimation halves) and the cluster-robust variance that feeds the ATE standard error. It is how the within-person dependence across the three tasks is absorbed.
- **`num.trees`** — number of trees in the forest. More trees give more stable estimates and tighter variance estimation; `2000` is a smoke-test value, comfortably below a production setting.
- **`seed`** — RNG seed for reproducible subsampling and tree construction.

Two defaults left implicit are worth knowing:

- **`Y.hat = NULL`** (not passed) means `grf` fits its own regression forest of `Y` on `X` (which includes the country FE) and partials it out — the orthogonalization step at the heart of the R-learner. This is how the prognostic surface and country baselines are removed before estimating `tau(x)`.
- **`honesty = TRUE`** (the package default) splits each tree's data so the structure is learned on one half and the leaf effects estimated on the other, which is what makes the confidence intervals valid.

::: callout-note
## What prints to the console while it runs

Unlike the BCF sampler, `grf` is **silent** during fitting — there is no per-iteration trace, and a successful fit prints nothing at all.
That absence is normal, not a sign the call hung.
What you may see instead are *warnings*, and they are worth reading:

- a warning that the number of trees is too small for reliable variance estimates (raise `num.trees`);
- a warning about clusters being unbalanced or fewer clusters than expected (a sign the `clusters` vector was built wrong).

For a readable summary of the fitted object, call `print(cf)`, which reports the forest type, the number of trees, and the number of training samples and clusters — the quickest confirmation that the nesting was passed in as intended.
The substantive diagnostics all come *after* the fit, from the functions called in @sec-extract.
:::

```{r}
#| label: fit
cf <- grf::causal_forest(
  X = X,
  Y = y,
  W = z,
  W.hat = 0.5, # known conjoint propensity
  clusters = clusters, # respondent-level honest sampling + robust variance
  num.trees = 2000,
  seed = 20260602
)
```

## What the fitted object contains {#sec-fit-object}

`causal_forest()` returns a list of class `causal_forest`.
Unlike the BCF object, the treatment-effect estimates are already sitting on it — no forest needs to be replayed.
The components worth knowing:

- **`$predictions`** — a length-`n` vector of *out-of-bag* estimates of `tau(x)` for the training rows (each row predicted only by trees that did not see it, which is what keeps them honest). `predict(cf)` with no new data returns the same OOB predictions wrapped in a data frame.
- **`$variance.estimates`** — per-observation variance of those predictions (populated because the default `ci.group.size` is greater than 1); the basis for individual confidence intervals.
- **`$X.orig`, `$Y.orig`, `$W.orig`** — the data as passed in.
- **`$Y.hat`, `$W.hat`** — the fitted nuisance estimates that were partialled out: here `$W.hat` is the constant `0.5` we supplied, and `$Y.hat` is the internal regression-forest fit of `Y` on `X`.
- **`$clusters`** — the cluster assignment actually used, retained so downstream functions reproduce the cluster-robust variance.
- **`$tunable.params`, `$num.trees`** — the settings the forest was grown with.

The three headline quantities are read off with dedicated functions rather than from slots directly:

- **`predict(cf)$predictions`** — the individual `tau_hat`, as above.
- **`average_treatment_effect(cf, target.sample = "all")`** — a named numeric vector with `estimate` and `std.err` (the cluster-robust SE), i.e. the ATE.
- **`best_linear_projection(cf, X_mod)`** — a coefficient table (an `lmtest::coeftest` matrix) with one row per moderator plus an intercept and columns `Estimate`, `Std. Error`, `t value`, `Pr(>|t|)`. It is the linear summary of how `tau(x)` moves with each pre-specified moderator, and the direct counterpart to the BCF posterior projection.

## Extract and verify {#sec-extract}

We pull the three headline quantities.
The cluster-robust ATE should land near the planted average effect `mean(tau_x)`; the individual predictions should correlate with the true `τ(x)` and separate in the right direction across the `x3` moderator; the best linear projection onto the moderators should flag `x3` as the one with a clearly non-zero slope.

```{r}
#| label: extract
# cluster-robust average treatment effect
ate <- grf::average_treatment_effect(cf, target.sample = "all")

# individual treatment effects
tau_hat <- predict(cf)$predictions

# best linear projection onto the pre-specified moderators
blp <- grf::best_linear_projection(cf, X_mod)

cat("planted ATE:", round(mean(tau_x), 3), "\n")
cat(
  "recovered ATE:",
  round(ate["estimate"], 3),
  "(SE",
  round(ate["std.err"], 3),
  ")\n"
)
cat("cor(true tau, tau_hat):", round(cor(tau_x, tau_hat), 3), "\n")
cat(
  "tau_hat mean  x3<=0 / x3>0:",
  round(mean(tau_hat[X_mod[, 3] <= 0]), 3),
  "/",
  round(mean(tau_hat[X_mod[, 3] > 0]), 3),
  "\n"
)

# the two moderator groups should separate in the right direction
stopifnot(
  mean(tau_hat[X_mod[, 3] > 0]) > mean(tau_hat[X_mod[, 3] <= 0]),
  length(tau_hat) == n
)

print(round(blp[, 1:2], 3))
```

If the recovered ATE is within a couple of standard errors of the planted average, `τ̂(x)` orders correctly across `x3`, and the BLP isolates `x3`, the strategy is working as intended.
Exact recovery is not expected from a smoke-test forest on a small sample; partial pooling toward the grand mean (here, regularization toward the ATE) is expected.

## True vs. recovered covariate effects {#sec-recovery}

The analogue of the BCF notebook's recovery figure.
`grf` targets `τ(x)` directly and does not return a separate prognostic surface, so the figure focuses on the treatment effect.
We plot recovered against true `τ(x)` with a dashed 45° identity line, colouring points by the true moderator group: the planted step function takes two values (low for `x3 <= 0`, high for `x3 > 0`), so the two clouds should sit near their respective true values, shrunk gently toward the centre.

```{r}
#| label: recover-effects
recovery <- tibble(
  truth = tau_x,
  estimate = tau_hat,
  moderator = if_else(X_mod[, 3] > 0, "x3 > 0", "x3 <= 0")
)
```

```{r}
#| label: fig-recovery-grf
#| fig-cap: "True (data-generating) treatment effect tau(x) vs. recovered causal-forest estimates on synthetic data, coloured by the true moderator group. Dashed line is the 45° identity; points are individual observations. Smoke-test fit, small sample."
#| dpi: 500
recovery |>
  ggplot(aes(x = truth, y = estimate, colour = moderator)) +
  geom_abline(
    slope = 1,
    intercept = 0,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(alpha = 0.3) +
  scale_colour_manual(values = c("x3 <= 0" = "#0072B2", "x3 > 0" = "#D55E00")) +
  labs(
    title = "True vs. recovered treatment effect (synthetic smoke test)",
    x = "True effect",
    y = "Causal-forest estimate",
    colour = NULL
  ) +
  ggpubr::theme_pubr()
```

# Processing the output downstream {#sec-downstream}

This section shows how the forest output becomes the tidy objects the manuscript consumes.
The best linear projection is the headline summary for the BCF/CRF comparison table, so we tidy it into a coefficient frame.

```{r}
#| label: tidy-blp
blp_summary <- blp |>
  unclass() |>
  as.data.frame() |>
  tibble::rownames_to_column("term") |>
  as_tibble() |>
  rename(
    estimate = Estimate,
    std_error = `Std. Error`
  ) |>
  mutate(
    lower = estimate - 1.96 * std_error,
    upper = estimate + 1.96 * std_error
  )

blp_summary
```

The BLP coefficient frame plots as a standard coefficient figure — the same grammar used for the BCF posterior projection, which is what makes the two methods legible side by side in the manuscript.
The chunk below is a template following project figure conventions; the manuscript figure will overlay BCF and CRF coefficients on shared axes.

```{r}
#| label: fig-blp
#| fig-cap: "Best linear projection of the causal forest onto the pre-specified moderators (synthetic data), with 95% confidence intervals. Template for the BCF/CRF comparison figure."
#| dpi: 500
blp_summary |>
  filter(term != "(Intercept)") |>
  mutate(term = fct_reorder(term, estimate)) |>
  ggplot(aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper)) +
  labs(
    title = "Causal-forest best linear projection",
    x = "Projection coefficient",
    y = "Moderator"
  ) +
  ggpubr::theme_pubr()
```

# Small-subsample fit on real data {#sec-subsample}

::: callout-important
The cells below are placeholders.
They depend on the prepared analysis tibble from `01_prep_hte`, which does **not exist yet**.
Once it does, point the read at the real file, choose the outcome (Dictator or Trust), and assemble the moderator matrix.
:::

The intent: subset to a handful of countries, fit the causal forest with the real moderators, and confirm the *real* data flows through the same machinery before scaling to the full sample.

```{r}
#| label: load-subsample
# TODO: replace with real 01_prep_hte output
# dat <- readRDS(here::here("data", "hte_dictator.rds"))

# few-country subsample (grf scales fine; this just mirrors the BCF test)
# few_countries <- levels(factor(dat$country_id))[1:3]
# sub <- dat |> filter(country_id %in% few_countries) |>
#   mutate(across(c(country_id, respondent_id), fct_drop))
```

```{r}
#| label: fit-subsample
# country FE dummies + respondent clusters from the real data
# country_fe_sub <- fastDummies::dummy_cols(
#   data.frame(country = sub$country_id),
#   remove_first_dummy = TRUE, remove_selected_columns = TRUE
# ) |> as.matrix()
# X_sub <- cbind(sub_moderators, country_fe_sub)  # numeric moderator matrix + FE
#
# cf_sub <- grf::causal_forest(
#   X = X_sub,
#   Y = sub$y,
#   W = sub$z,
#   W.hat = 0.5,                       # known conjoint propensity
#   clusters = as.integer(factor(sub$respondent_id)),
#   num.trees = 2000
# )
#
# ate_sub <- grf::average_treatment_effect(cf_sub, target.sample = "all")
# blp_sub <- grf::best_linear_projection(cf_sub, sub_moderators)
```

Record the wall-clock time of this subsample fit, then scale to the full sample.
Because `grf` clusters cheaply, the full-sample CRF is expected to be the *less* costly of the two methods; the BCF nested-RE fit is the binding constraint on the project window.

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
