---
subtitle: |
  Nested Structure in `grf` Causal Forests — Mechanism Test
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: false
  message: true
---

# Purpose {#sec-purpose}

This notebook is a **scaffold**, not a finished analysis.
It is the `grf` counterpart to `03_multibart_nested_ri_test.qmd`: where that notebook tests the hierarchical-BCF primary method, this one tests the **Causal Random Forest robustness strategy** on the same synthetic data so the two are directly comparable.

The goals, in priority order, are:

1. **Verify the proposed `grf` strategy works in principle.**
   On *synthetic* two-level data with known effects we confirm that `grf::causal_forest()` with country fixed effects in `X`, respondent-level `clusters`, and the known conjoint propensity recovers the planted average and heterogeneous treatment effects.
2. **See what the output looks like and how to process it downstream.**
   We walk the forest output through the headline quantities the manuscript needs — cluster-robust ATE, individual `τ̂(x)`, and the best linear projection onto the pre-specified moderators — and produce the same true-vs-recovered figure as the BCF test.

::: callout-important
`eval: false` is set at the document level on purpose.
Nothing here is meant to run on render yet: the real data (`01_prep_hte` output) is not prepared.
The synthetic mechanism check in @sec-synthetic is self-contained and can be run on its own by flipping the relevant chunk to `eval: true`; the subsample section in @sec-subsample additionally requires the prepared data.
:::

::: callout-note
## How `grf` handles the nesting

The data are observations nested in respondents nested in countries.
The robustness strategy accounts for both levels without random effects:

- **Country** enters as **fixed effects** — one-hot dummy columns appended to the covariate matrix `X`. `grf` requires a numeric `X`, so we encode the factor explicitly rather than passing it raw.
- **Respondent** enters through `clusters = respondent_id`. This gives honest, cluster-aware subsampling (whole respondents are held out together) and cluster-robust variance for the ATE, absorbing the within-person dependence across the three conjoint tasks.

This is the frequentist analogue of the BCF random-intercept specification: the same nuisance structure, addressed by FE + clustering instead of partial pooling.
:::

::: callout-note
## Cost is not the concern here

Unlike the dense `WtW` solve in the nested-RE BCF fit, `grf` scales comfortably to the full ~112,500 observations and ~37,500 respondent clusters.
The synthetic check below is about **correctness of the strategy**, not feasibility; the small dimensions just keep the smoke test fast.
:::

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # multi-panel figure
  "fastDummies", # country fixed-effect dummies
  "grf", # causal_forest robustness method
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Synthetic mechanism check {#sec-synthetic}

This is the primary test.
We reuse the **exact data-generating process** from the BCF notebook (same seed), so the two methods are tested on identical data and their recovered effects can be compared one-to-one.

## Simulate two-level data {#sec-simulate}

Respondents nested in countries, several conjoint tasks per respondent.
Treatment `z` is randomized with a known propensity of 0.5, as in the conjoint design.
Country and respondent intercepts are drawn from normals with distinct variances; for `grf` these are pure nuisance — country is handled by fixed effects, respondent by clustering.

```{r}
#| label: simulate
set.seed(20260602)

# dimensions
n_country <- 8
n_resp_per_country <- 25
n_task <- 3

# nested ids
country_id <- factor(rep(
  seq_len(n_country),
  each = n_resp_per_country * n_task
))
resp_id <- factor(rep(seq_len(n_country * n_resp_per_country), each = n_task))
n <- length(resp_id)

# planted variance components (nuisance)
sigma_country <- 1.5
sigma_resp <- 0.5
b_country <- rnorm(n_country, 0, sigma_country)
b_resp <- rnorm(nlevels(resp_id), 0, sigma_resp)

# covariates, prognostic function, heterogeneous tau
p <- 4
X_mod <- matrix(rnorm(n * p), nrow = n)
colnames(X_mod) <- paste0("x", seq_len(p))
mu_x <- 1.0 * X_mod[, 1] - 0.5 * X_mod[, 2]
tau_x <- 0.5 + 0.75 * (X_mod[, 3] > 0)

# randomized treatment, known propensity 0.5
z <- rbinom(n, 1, 0.5)

# linear predictor with nested intercepts on the prognostic part only
lin_pred <- mu_x +
  tau_x * z +
  b_country[as.integer(country_id)] +
  b_resp[as.integer(resp_id)]

# continuous outcome
y <- lin_pred + rnorm(n, 0, 1)
```

A `stopifnot()` guards the nesting invariant — every respondent sits in exactly one country — and the basic dimensions.

```{r}
#| label: check-sim
# each respondent maps to exactly one country
resp_country_map <- tapply(as.integer(country_id), resp_id, function(v) {
  length(unique(v))
})
stopifnot(
  all(resp_country_map == 1),
  length(y) == n,
  nrow(X_mod) == n,
  all(sort(unique(z)) == c(0, 1))
)
```

## Build covariates and clustering {#sec-build}

Two pieces encode the nesting.
Country fixed effects become one-hot dummy columns (one dropped to avoid collinearity with the intercept `grf` fits internally) appended to the moderator matrix.
Respondent ids become an integer cluster vector.
We assert the assembled `X` has the expected width (`p` moderators + `C − 1` country dummies) and that the cluster vector is the right length.

```{r}
#| label: build
# country fixed effects as dummy columns
country_fe <- fastDummies::dummy_cols(
  data.frame(country = country_id),
  remove_first_dummy = TRUE,
  remove_selected_columns = TRUE
) |>
  as.matrix()

# moderators + country FE
X <- cbind(X_mod, country_fe)

# respondent-level clusters
clusters <- as.integer(resp_id)

stopifnot(
  nrow(X) == n,
  ncol(X) == p + (n_country - 1),
  length(clusters) == n,
  dplyr::n_distinct(clusters) == n_country * n_resp_per_country
)
```

## Fit the causal forest {#sec-fit}

`causal_forest()` takes the numeric `X`, outcome `y`, and treatment `z`.
Two strategy choices matter:

- **`W.hat = 0.5`** passes the known conjoint propensity directly, so no propensity is estimated (the analogue of passing known `zhat` to BCF).
- **`clusters = clusters`** switches on respondent-level honest sampling and cluster-robust variance.

`Y.hat` is left to `grf`'s internal regression forest on `X` (which includes the country FE), the standard partialling-out step.

```{r}
#| label: fit
cf <- grf::causal_forest(
  X = X,
  Y = y,
  W = z,
  W.hat = 0.5, # known conjoint propensity
  clusters = clusters, # respondent-level honest sampling + robust variance
  num.trees = 2000,
  seed = 20260602
)
```

## Extract and verify {#sec-extract}

We pull the three headline quantities.
The cluster-robust ATE should land near the planted average effect `mean(tau_x)`; the individual predictions should correlate with the true `τ(x)` and separate in the right direction across the `x3` moderator; the best linear projection onto the moderators should flag `x3` as the one with a clearly non-zero slope.

```{r}
#| label: extract
# cluster-robust average treatment effect
ate <- grf::average_treatment_effect(cf, target.sample = "all")

# individual treatment effects
tau_hat <- predict(cf)$predictions

# best linear projection onto the pre-specified moderators
blp <- grf::best_linear_projection(cf, X_mod)

cat("planted ATE:", round(mean(tau_x), 3), "\n")
cat(
  "recovered ATE:",
  round(ate["estimate"], 3),
  "(SE",
  round(ate["std.err"], 3),
  ")\n"
)
cat("cor(true tau, tau_hat):", round(cor(tau_x, tau_hat), 3), "\n")
cat(
  "tau_hat mean  x3<=0 / x3>0:",
  round(mean(tau_hat[X_mod[, 3] <= 0]), 3),
  "/",
  round(mean(tau_hat[X_mod[, 3] > 0]), 3),
  "\n"
)

# the two moderator groups should separate in the right direction
stopifnot(
  mean(tau_hat[X_mod[, 3] > 0]) > mean(tau_hat[X_mod[, 3] <= 0]),
  length(tau_hat) == n
)

print(round(blp[, 1:2], 3))
```

If the recovered ATE is within a couple of standard errors of the planted average, `τ̂(x)` orders correctly across `x3`, and the BLP isolates `x3`, the strategy is working as intended.
Exact recovery is not expected from a smoke-test forest on a small sample; partial pooling toward the grand mean (here, regularization toward the ATE) is expected.

## True vs. recovered covariate effects {#sec-recovery}

The analogue of the BCF notebook's recovery figure.
`grf` targets `τ(x)` directly and does not return a separate prognostic surface, so the figure focuses on the treatment effect.
We plot recovered against true `τ(x)` with a dashed 45° identity line, colouring points by the true moderator group: the planted step function takes two values (low for `x3 <= 0`, high for `x3 > 0`), so the two clouds should sit near their respective true values, shrunk gently toward the centre.

```{r}
#| label: recover-effects
recovery <- tibble(
  truth = tau_x,
  estimate = tau_hat,
  moderator = if_else(X_mod[, 3] > 0, "x3 > 0", "x3 <= 0")
)
```

```{r}
#| label: fig-recovery-grf
#| fig-cap: "True (data-generating) treatment effect tau(x) vs. recovered causal-forest estimates on synthetic data, coloured by the true moderator group. Dashed line is the 45° identity; points are individual observations. Smoke-test fit, small sample."
#| dpi: 500
recovery |>
  ggplot(aes(x = truth, y = estimate, colour = moderator)) +
  geom_abline(
    slope = 1,
    intercept = 0,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_point(alpha = 0.3) +
  scale_colour_manual(values = c("x3 <= 0" = "#0072B2", "x3 > 0" = "#D55E00")) +
  labs(
    title = "True vs. recovered treatment effect (synthetic smoke test)",
    x = "True effect",
    y = "Causal-forest posterior mean",
    colour = NULL
  ) +
  ggpubr::theme_pubr()
```

# Processing the output downstream {#sec-downstream}

This section shows how the forest output becomes the tidy objects the manuscript consumes.
The best linear projection is the headline summary for the BCF/CRF comparison table, so we tidy it into a coefficient frame.

```{r}
#| label: tidy-blp
blp_summary <- blp |>
  unclass() |>
  as.data.frame() |>
  tibble::rownames_to_column("term") |>
  as_tibble() |>
  rename(
    estimate = Estimate,
    std_error = `Std. Error`
  ) |>
  mutate(
    lower = estimate - 1.96 * std_error,
    upper = estimate + 1.96 * std_error
  )

blp_summary
```

The BLP coefficient frame plots as a standard coefficient figure — the same grammar used for the BCF posterior projection, which is what makes the two methods legible side by side in the manuscript.
The chunk below is a template following project figure conventions; the manuscript figure will overlay BCF and CRF coefficients on shared axes.

```{r}
#| label: fig-blp
#| fig-cap: "Best linear projection of the causal forest onto the pre-specified moderators (synthetic data), with 95% confidence intervals. Template for the BCF/CRF comparison figure."
#| dpi: 500
blp_summary |>
  filter(term != "(Intercept)") |>
  mutate(term = fct_reorder(term, estimate)) |>
  ggplot(aes(x = estimate, y = term)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper)) +
  labs(
    title = "Causal-forest best linear projection",
    x = "Projection coefficient",
    y = "Moderator"
  ) +
  ggpubr::theme_pubr()
```

# Small-subsample fit on real data {#sec-subsample}

::: callout-important
The cells below are placeholders.
They depend on the prepared analysis tibble from `01_prep_hte`, which does **not exist yet**.
Once it does, point the read at the real file, choose the outcome (Dictator or Trust), and assemble the moderator matrix.
:::

The intent: subset to a handful of countries, fit the causal forest with the real moderators, and confirm the *real* data flows through the same machinery before scaling to the full sample.

```{r}
#| label: load-subsample
# TODO: replace with real 01_prep_hte output
# dat <- readRDS(here::here("data", "hte_dictator.rds"))

# few-country subsample (grf scales fine; this just mirrors the BCF test)
# few_countries <- levels(factor(dat$country_id))[1:3]
# sub <- dat |> filter(country_id %in% few_countries) |>
#   mutate(across(c(country_id, respondent_id), fct_drop))
```

```{r}
#| label: fit-subsample
# country FE dummies + respondent clusters from the real data
# country_fe_sub <- fastDummies::dummy_cols(
#   data.frame(country = sub$country_id),
#   remove_first_dummy = TRUE, remove_selected_columns = TRUE
# ) |> as.matrix()
# X_sub <- cbind(sub_moderators, country_fe_sub)  # numeric moderator matrix + FE
#
# cf_sub <- grf::causal_forest(
#   X = X_sub,
#   Y = sub$y,
#   W = sub$z,
#   W.hat = 0.5,                       # known conjoint propensity
#   clusters = as.integer(factor(sub$respondent_id)),
#   num.trees = 2000
# )
#
# ate_sub <- grf::average_treatment_effect(cf_sub, target.sample = "all")
# blp_sub <- grf::best_linear_projection(cf_sub, sub_moderators)
```

Record the wall-clock time of this subsample fit, then scale to the full sample.
Because `grf` clusters cheaply, the full-sample CRF is expected to be the *less* costly of the two methods; the BCF nested-RE fit is the binding constraint on the project window.

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
