---
subtitle: |
  GRF Post-Processing — ATE, Heterogeneity Diagnostics, and CATE by Moderator (Dictator + Trust)
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Purpose {#sec-purpose}

This notebook post-processes the **primary** estimator — the saved `grf` causal forests
(`data/03_final/grf_{dictator,trust}.rds`) — following the canonical post-fit workflow from
the generalized-random-forest literature (`athey2019generalized`, `wager2018estimation`,
`athey2019estimating`).

It is written to be read **line by line**: every step is laid out sequentially, the two
games (Dictator, Trust) are done one after the other, and the headline CATE-by-moderator
figures are built **one explicit chunk per moderator** rather than through shared helper
functions.

For each game we run, in order:

1. **Average treatment effect (ATE) + SE** — `average_treatment_effect()`, the doubly-robust
   (AIPW) estimate with the cluster-robust standard error from the respondent clusters stored
   on the forest.
2. **Targeting Operator Characteristic (TOC) / RATE** — `rank_average_treatment_effect()`,
   the overall "is there targetable heterogeneity" summary (AUTOC ± SE plus the TOC curve).
3. **Best linear projection (BLP)** — `best_linear_projection()` of the CATE onto the
   moderator set, an appendix-style linear summary of effect modification.
4. **Variable importance** — `variable_importance()`, aggregated from the expanded dummy
   columns back up to the original moderators (construct level).
5. **CATE by moderator** — the headline figures: estimated CATE on the y-axis, the moderator
   on the x-axis, with an **honest 95% confidence interval at each level**. Per-level
   intervals come straight from `average_treatment_effect(cf, subset = ...)`, which is the
   documented `grf` way to get a doubly-robust, cluster-robust subset ATE.

Two moderator families, matching the research plan:

- **Conjoint round-level** moderators (`prof_mods`) — other attributes in the same profile.
- **Individual-level** moderators (`resp_mods`) — respondent pre-treatment items and indices.

The companion notebook `08_postprocess_bcf.qmd` runs the analogous workflow on the BCF fits.

::: callout-note
## A note on cost

Each per-level CI is a separate `average_treatment_effect()` call, so the CATE-by-moderator
sweep makes many calls (one per level, across 31 moderators, twice). This is slower than
computing the doubly-robust scores once and reusing them, but it is the most transparent
route and the user-requested one; Quarto `freeze: auto` caches the rendered result.
:::

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr, purrr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # later composition
  "grf", # causal_forest predictions, ATE, RATE, BLP
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load data and fits {#sec-load}

```{r}
#| label: load-data
eu25_long <- readRDS(here::here("data", "02_processed", "eu25_long.rds"))
cf_dict <- readRDS(here::here("data", "03_final", "grf_dictator.rds"))
cf_trust <- readRDS(here::here("data", "03_final", "grf_trust.rds"))
```

# Reconstruct the moderator designs {#sec-designs}

The frozen moderator list, copied verbatim from `06_grf_fit.qmd`.

```{r}
#| label: moderators
prof_mods <- c("cj_nat", "cj_eupos", "cj_age", "cj_sex", "cj_class")
resp_mods <- c(
  "q_gender",
  "q_age",
  "q_identity_country",
  "q_identity_eu",
  "q_identity_europe",
  "q_religion",
  "q_class",
  "q_eu_efficacy_understand",
  "q_pop_reps",
  "q_pop_goodevil",
  "q_pop_compromise",
  "q_dem_compromise",
  "q_dem_listen",
  "q_tech_experts",
  "q_tech_leaders",
  "q_party_harm",
  "q_people_incompetent",
  "q_eu_longterm",
  "q_eu_responsive",
  "q_eu_imp_nat_econ",
  "q_eu_imp_nat_cul",
  "q_eu_imp_nat_pol",
  "q_eu_abolish",
  "q_eu_satisfaction",
  "q_rural_urban",
  "q_edu_age_stop"
)
all_mods <- c(prof_mods, resp_mods)
```

For each game we filter `dat` to that game in its original order (the same order the forest
was fit on), keep the original moderator columns for plotting (`m_dict` / `m_trust`), and
build the numeric moderator matrix used by the projection and importance steps (`X_dict` /
`X_trust`) exactly as at fit time.
The `stopifnot()` confirms the reconstructed rows line up with the forest's training rows, so
each τ̂ aligns with its moderator value.

```{r}
#| label: designs
# dictator design (same row order as the fit)
sub_dict <- eu25_long |> filter(cj_game_type == "cj_dict")
m_dict <- sub_dict |>
  select(all_of(all_mods)) |>
  mutate(across(where(is.character), factor))
X_dict <- model.matrix(~ . - 1, data = m_dict)

# trust design (same row order as the fit)
sub_trust <- eu25_long |> filter(cj_game_type == "cj_trust")
m_trust <- sub_trust |>
  select(all_of(all_mods)) |>
  mutate(across(where(is.character), factor))
X_trust <- model.matrix(~ . - 1, data = m_trust)

stopifnot(
  length(cf_dict$Y.orig) == nrow(m_dict),
  length(cf_trust$Y.orig) == nrow(m_trust),
  !anyNA(X_dict),
  !anyNA(X_trust)
)
```

The y-axis label, shared by every CATE figure.

```{r}
#| label: ylab
yl <- "CATE (effect of Muslim profile)"
```

# Dictator game {#sec-dict}

## Average treatment effect {#sec-dict-ate}

The doubly-robust ATE with its cluster-robust SE (respondent clusters are stored on the
forest), and the implied 95% interval.

```{r}
#| label: ate-dict
ate_dict <- grf::average_treatment_effect(cf_dict, target.sample = "all")
cat(sprintf(
  "Dictator ATE: %.4f  (SE %.4f);  95%% CI [%.4f, %.4f]\n",
  ate_dict["estimate"],
  ate_dict["std.err"],
  ate_dict["estimate"] - 1.96 * ate_dict["std.err"],
  ate_dict["estimate"] + 1.96 * ate_dict["std.err"]
))
```

## Targeting Operator Characteristic (RATE) {#sec-dict-toc}

`rank_average_treatment_effect()` ranks observations by their out-of-bag predicted CATE and
traces the ATE among the top-`q` fraction against the overall ATE.
The area under this curve is the AUTOC; a curve and AUTOC clearly above zero is evidence of
targetable heterogeneity.
Priorities here are the forest's own out-of-bag predictions, which is acceptable because they
are honest (out-of-bag); a separate train/evaluate split would be the stricter alternative
but is out of scope.

```{r}
#| label: fig-grf-dict-toc
#| fig-cap: "GRF Targeting Operator Characteristic curve (Dictator game): ATE among the top-q fraction by predicted CATE minus the overall ATE, with 95% CI. AUTOC summarises the area under the curve."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
prio_dict <- predict(cf_dict)$predictions
rate_dict <- grf::rank_average_treatment_effect(cf_dict, prio_dict)
print(rate_dict)

toc_dict <- rate_dict$TOC |>
  mutate(lower = estimate - 1.96 * std.err, upper = estimate + 1.96 * std.err)

ggplot(toc_dict, aes(x = q, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(colour = "#0072B2", linewidth = 0.8) +
  labs(
    title = sprintf(
      "TOC (Dictator): AUTOC = %.3f (SE %.3f)",
      rate_dict$estimate,
      rate_dict$std.err
    ),
    x = "Treated fraction q (highest predicted CATE first)",
    y = "ATE(top q) - ATE(all)"
  ) +
  ggpubr::theme_pubr()
```

## Best linear projection {#sec-dict-blp}

The best linear projection of the CATE onto the moderator matrix: a linear summary of which
moderators shift the treatment effect.
This is an appendix/robustness summary, not a headline.

```{r}
#| label: fig-grf-dict-blp
#| fig-cap: "GRF best linear projection of the CATE onto the moderator set (Dictator game), with 95% CIs. Appendix-style linear summary of effect modification."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 9
blp_dict <- grf::best_linear_projection(cf_dict, X_dict)
blp_dict_df <- blp_dict |>
  unclass() |>
  as.data.frame() |>
  tibble::rownames_to_column("term") |>
  as_tibble() |>
  rename(estimate = Estimate, std_error = `Std. Error`) |>
  mutate(
    lower = estimate - 1.96 * std_error,
    upper = estimate + 1.96 * std_error
  ) |>
  filter(term != "(Intercept)")

ggplot(blp_dict_df, aes(x = estimate, y = fct_reorder(term, estimate))) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper), colour = "#0072B2") +
  labs(
    title = "Best linear projection of the CATE (Dictator)",
    x = "Projection coefficient",
    y = NULL
  ) +
  ggpubr::theme_pubr()
```

## Variable importance {#sec-dict-vi}

`variable_importance()` returns one value per design column (the expanded moderator dummies
plus the country fixed-effect dummies).
We map each column back to its source moderator by longest-prefix match and sum, giving a
construct-level ranking; country fixed-effect columns match no moderator and are dropped.

```{r}
#| label: fig-grf-dict-vi
#| fig-cap: "GRF variable importance (Dictator game), aggregated to the original moderators. Profile-level and respondent-level moderators distinguished by colour. Country fixed-effect columns excluded."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 7
vi_dict <- grf::variable_importance(cf_dict)
vi_dict_df <- tibble(
  column = colnames(cf_dict$X.orig),
  importance = as.numeric(vi_dict)
) |>
  mutate(
    moderator = map_chr(column, function(cn) {
      hit <- all_mods[startsWith(cn, all_mods)]
      if (length(hit) == 0) NA_character_ else hit[which.max(nchar(hit))]
    })
  ) |>
  filter(!is.na(moderator)) |>
  summarise(importance = sum(importance), .by = moderator) |>
  mutate(
    family = if_else(
      moderator %in% prof_mods,
      "Profile-level",
      "Respondent-level"
    ),
    moderator = fct_reorder(moderator, importance)
  )

ggplot(vi_dict_df, aes(x = importance, y = moderator, fill = family)) +
  geom_col() +
  scale_fill_manual(
    values = c("Profile-level" = "#D55E00", "Respondent-level" = "#0072B2")
  ) +
  labs(
    title = "Variable importance (Dictator)",
    x = "Importance (depth-weighted split frequency)",
    y = NULL,
    fill = NULL
  ) +
  ggpubr::theme_pubr()
```

## CATE by moderator — conjoint round-level {#sec-dict-prof}

For each discrete moderator we loop over its levels, compute the subset ATE with its honest
cluster-robust SE, form the 95% interval as estimate ± 1.96·SE, and plot the per-level
estimate (blue) over grey per-level count bars.

### cj_nat {#sec-dict-cj-nat}

```{r}
#| label: fig-grf-dict-cj-nat
#| fig-cap: "GRF CATE of the Muslim profile by cj_nat (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_nat"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_eupos {#sec-dict-cj-eupos}

```{r}
#| label: fig-grf-dict-cj-eupos
#| fig-cap: "GRF CATE of the Muslim profile by cj_eupos (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_eupos"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_age {#sec-dict-cj-age}

```{r}
#| label: fig-grf-dict-cj-age
#| fig-cap: "GRF CATE of the Muslim profile by cj_age (Dictator): connected per-level subset ATE with honest cluster-robust 95% CI ribbon (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_age"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    value = as.numeric(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(lower = estimate - 1.96 * se, upper = estimate + 1.96 * se)
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = value)) +
  geom_segment(
    aes(xend = value, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(aes(y = estimate), colour = "#0072B2", linewidth = 0.8) +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr()
```

### cj_sex {#sec-dict-cj-sex}

```{r}
#| label: fig-grf-dict-cj-sex
#| fig-cap: "GRF CATE of the Muslim profile by cj_sex (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_sex"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_class {#sec-dict-cj-class}

```{r}
#| label: fig-grf-dict-cj-class
#| fig-cap: "GRF CATE of the Muslim profile by cj_class (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_class"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

## CATE by moderator — respondent-level {#sec-dict-resp}

Same per-level construction for the respondent moderators.
The two genuinely continuous moderators — `q_age` and `q_edu_age_stop` — are instead split
into ten quantile bins and drawn as a ribbon-and-line with a covariate rug.

### q_gender {#sec-dict-q-gender}

```{r}
#| label: fig-grf-dict-q-gender
#| fig-cap: "GRF CATE of the Muslim profile by q_gender (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_gender"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_age {#sec-dict-q-age}

```{r}
#| label: fig-grf-dict-q-age
#| fig-cap: "GRF CATE of the Muslim profile across deciles of q_age (Dictator): per-bin subset ATE with honest cluster-robust 95% CI (ribbon); grey histogram shows the covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_age"
col <- m_dict[[mod]]
bin <- ntile(col, 10)
rows <- list()
for (k in sort(unique(bin))) {
  sel <- bin == k
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(k)]] <- tibble(
    bin = k,
    x_pos = mean(col[sel]),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(lower = estimate - 1.96 * se, upper = estimate + 1.96 * se)
# distribution band
yr <- range(c(cate$lower, cate$upper))
pad <- 0.12 * diff(yr)
floor_y <- yr[1] - pad
span <- 0.20 * diff(yr)
h <- hist(col[!is.na(col)], breaks = 30, plot = FALSE)
hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
  mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
ggplot(cate, aes(x = x_pos)) +
  geom_rect(
    data = hd,
    aes(xmin = mid - w / 2, xmax = mid + w / 2, ymin = floor_y, ymax = bar_top),
    fill = "grey80",
    inherit.aes = FALSE
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(aes(y = estimate), colour = "#0072B2", linewidth = 0.8) +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 1.5) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr()
```

### q_identity_country {#sec-dict-q-identity-country}

```{r}
#| label: fig-grf-dict-q-identity-country
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_country (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_country"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_identity_eu {#sec-dict-q-identity-eu}

```{r}
#| label: fig-grf-dict-q-identity-eu
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_eu (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_eu"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_identity_europe {#sec-dict-q-identity-europe}

```{r}
#| label: fig-grf-dict-q-identity-europe
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_europe (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_europe"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_religion {#sec-dict-q-religion}

```{r}
#| label: fig-grf-dict-q-religion
#| fig-cap: "GRF CATE of the Muslim profile by q_religion (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts. Rare categories give wide CIs."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_religion"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_class {#sec-dict-q-class}

```{r}
#| label: fig-grf-dict-q-class
#| fig-cap: "GRF CATE of the Muslim profile by q_class (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_class"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_efficacy_understand {#sec-dict-q-eu-efficacy-understand}

```{r}
#| label: fig-grf-dict-q-eu-efficacy-understand
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_efficacy_understand (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_efficacy_understand"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_reps {#sec-dict-q-pop-reps}

```{r}
#| label: fig-grf-dict-q-pop-reps
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_reps (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_reps"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_goodevil {#sec-dict-q-pop-goodevil}

```{r}
#| label: fig-grf-dict-q-pop-goodevil
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_goodevil (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_goodevil"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_compromise {#sec-dict-q-pop-compromise}

```{r}
#| label: fig-grf-dict-q-pop-compromise
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_compromise (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_compromise"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_dem_compromise {#sec-dict-q-dem-compromise}

```{r}
#| label: fig-grf-dict-q-dem-compromise
#| fig-cap: "GRF CATE of the Muslim profile by q_dem_compromise (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_dem_compromise"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_dem_listen {#sec-dict-q-dem-listen}

```{r}
#| label: fig-grf-dict-q-dem-listen
#| fig-cap: "GRF CATE of the Muslim profile by q_dem_listen (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_dem_listen"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_tech_experts {#sec-dict-q-tech-experts}

```{r}
#| label: fig-grf-dict-q-tech-experts
#| fig-cap: "GRF CATE of the Muslim profile by q_tech_experts (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_tech_experts"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_tech_leaders {#sec-dict-q-tech-leaders}

```{r}
#| label: fig-grf-dict-q-tech-leaders
#| fig-cap: "GRF CATE of the Muslim profile by q_tech_leaders (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_tech_leaders"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_party_harm {#sec-dict-q-party-harm}

```{r}
#| label: fig-grf-dict-q-party-harm
#| fig-cap: "GRF CATE of the Muslim profile by q_party_harm (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_party_harm"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_people_incompetent {#sec-dict-q-people-incompetent}

```{r}
#| label: fig-grf-dict-q-people-incompetent
#| fig-cap: "GRF CATE of the Muslim profile by q_people_incompetent (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_people_incompetent"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_longterm {#sec-dict-q-eu-longterm}

```{r}
#| label: fig-grf-dict-q-eu-longterm
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_longterm (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_longterm"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_responsive {#sec-dict-q-eu-responsive}

```{r}
#| label: fig-grf-dict-q-eu-responsive
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_responsive (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_responsive"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_econ {#sec-dict-q-eu-imp-nat-econ}

```{r}
#| label: fig-grf-dict-q-eu-imp-nat-econ
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_econ (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_econ"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_cul {#sec-dict-q-eu-imp-nat-cul}

```{r}
#| label: fig-grf-dict-q-eu-imp-nat-cul
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_cul (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_cul"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_pol {#sec-dict-q-eu-imp-nat-pol}

```{r}
#| label: fig-grf-dict-q-eu-imp-nat-pol
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_pol (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_pol"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_abolish {#sec-dict-q-eu-abolish}

```{r}
#| label: fig-grf-dict-q-eu-abolish
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_abolish (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_abolish"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_satisfaction {#sec-dict-q-eu-satisfaction}

```{r}
#| label: fig-grf-dict-q-eu-satisfaction
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_satisfaction (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_satisfaction"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_rural_urban {#sec-dict-q-rural-urban}

```{r}
#| label: fig-grf-dict-q-rural-urban
#| fig-cap: "GRF CATE of the Muslim profile by q_rural_urban (Dictator): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_rural_urban"
levs <- sort(unique(m_dict[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_dict[[mod]] == lev
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_edu_age_stop {#sec-dict-q-edu-age-stop}

```{r}
#| label: fig-grf-dict-q-edu-age-stop
#| fig-cap: "GRF CATE of the Muslim profile across deciles of q_edu_age_stop (Dictator): per-bin subset ATE with honest cluster-robust 95% CI (ribbon); grey histogram shows the covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_edu_age_stop"
col <- m_dict[[mod]]
bin <- ntile(col, 10)
rows <- list()
for (k in sort(unique(bin))) {
  sel <- bin == k
  a <- grf::average_treatment_effect(cf_dict, subset = sel)
  rows[[as.character(k)]] <- tibble(
    bin = k,
    x_pos = mean(col[sel]),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(lower = estimate - 1.96 * se, upper = estimate + 1.96 * se)
# distribution band
yr <- range(c(cate$lower, cate$upper))
pad <- 0.12 * diff(yr)
floor_y <- yr[1] - pad
span <- 0.20 * diff(yr)
h <- hist(col[!is.na(col)], breaks = 30, plot = FALSE)
hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
  mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
ggplot(cate, aes(x = x_pos)) +
  geom_rect(
    data = hd,
    aes(xmin = mid - w / 2, xmax = mid + w / 2, ymin = floor_y, ymax = bar_top),
    fill = "grey80",
    inherit.aes = FALSE
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(aes(y = estimate), colour = "#0072B2", linewidth = 0.8) +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 1.5) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr()
```

# Trust game {#sec-trust}

## Average treatment effect {#sec-trust-ate}

```{r}
#| label: ate-trust
ate_trust <- grf::average_treatment_effect(cf_trust, target.sample = "all")
cat(sprintf(
  "Trust ATE: %.4f  (SE %.4f);  95%% CI [%.4f, %.4f]\n",
  ate_trust["estimate"],
  ate_trust["std.err"],
  ate_trust["estimate"] - 1.96 * ate_trust["std.err"],
  ate_trust["estimate"] + 1.96 * ate_trust["std.err"]
))
```

## Targeting Operator Characteristic (RATE) {#sec-trust-toc}

```{r}
#| label: fig-grf-trust-toc
#| fig-cap: "GRF Targeting Operator Characteristic curve (Trust game): ATE among the top-q fraction by predicted CATE minus the overall ATE, with 95% CI. AUTOC summarises the area under the curve."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
prio_trust <- predict(cf_trust)$predictions
rate_trust <- grf::rank_average_treatment_effect(cf_trust, prio_trust)
print(rate_trust)

toc_trust <- rate_trust$TOC |>
  mutate(lower = estimate - 1.96 * std.err, upper = estimate + 1.96 * std.err)

ggplot(toc_trust, aes(x = q, y = estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(colour = "#0072B2", linewidth = 0.8) +
  labs(
    title = sprintf(
      "TOC (Trust): AUTOC = %.3f (SE %.3f)",
      rate_trust$estimate,
      rate_trust$std.err
    ),
    x = "Treated fraction q (highest predicted CATE first)",
    y = "ATE(top q) - ATE(all)"
  ) +
  ggpubr::theme_pubr()
```

## Best linear projection {#sec-trust-blp}

```{r}
#| label: fig-grf-trust-blp
#| fig-cap: "GRF best linear projection of the CATE onto the moderator set (Trust game), with 95% CIs. Appendix-style linear summary of effect modification."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 9
blp_trust <- grf::best_linear_projection(cf_trust, X_trust)
blp_trust_df <- blp_trust |>
  unclass() |>
  as.data.frame() |>
  tibble::rownames_to_column("term") |>
  as_tibble() |>
  rename(estimate = Estimate, std_error = `Std. Error`) |>
  mutate(
    lower = estimate - 1.96 * std_error,
    upper = estimate + 1.96 * std_error
  ) |>
  filter(term != "(Intercept)")

ggplot(blp_trust_df, aes(x = estimate, y = fct_reorder(term, estimate))) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper), colour = "#0072B2") +
  labs(
    title = "Best linear projection of the CATE (Trust)",
    x = "Projection coefficient",
    y = NULL
  ) +
  ggpubr::theme_pubr()
```

## Variable importance {#sec-trust-vi}

```{r}
#| label: fig-grf-trust-vi
#| fig-cap: "GRF variable importance (Trust game), aggregated to the original moderators. Profile-level and respondent-level moderators distinguished by colour. Country fixed-effect columns excluded."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 7
vi_trust <- grf::variable_importance(cf_trust)
vi_trust_df <- tibble(
  column = colnames(cf_trust$X.orig),
  importance = as.numeric(vi_trust)
) |>
  mutate(
    moderator = map_chr(column, function(cn) {
      hit <- all_mods[startsWith(cn, all_mods)]
      if (length(hit) == 0) NA_character_ else hit[which.max(nchar(hit))]
    })
  ) |>
  filter(!is.na(moderator)) |>
  summarise(importance = sum(importance), .by = moderator) |>
  mutate(
    family = if_else(
      moderator %in% prof_mods,
      "Profile-level",
      "Respondent-level"
    ),
    moderator = fct_reorder(moderator, importance)
  )

ggplot(vi_trust_df, aes(x = importance, y = moderator, fill = family)) +
  geom_col() +
  scale_fill_manual(
    values = c("Profile-level" = "#D55E00", "Respondent-level" = "#0072B2")
  ) +
  labs(
    title = "Variable importance (Trust)",
    x = "Importance (depth-weighted split frequency)",
    y = NULL,
    fill = NULL
  ) +
  ggpubr::theme_pubr()
```

## CATE by moderator — conjoint round-level {#sec-trust-prof}

### cj_nat {#sec-trust-cj-nat}

```{r}
#| label: fig-grf-trust-cj-nat
#| fig-cap: "GRF CATE of the Muslim profile by cj_nat (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_nat"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_eupos {#sec-trust-cj-eupos}

```{r}
#| label: fig-grf-trust-cj-eupos
#| fig-cap: "GRF CATE of the Muslim profile by cj_eupos (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_eupos"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_age {#sec-trust-cj-age}

```{r}
#| label: fig-grf-trust-cj-age
#| fig-cap: "GRF CATE of the Muslim profile by cj_age (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_age"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_sex {#sec-trust-cj-sex}

```{r}
#| label: fig-grf-trust-cj-sex
#| fig-cap: "GRF CATE of the Muslim profile by cj_sex (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_sex"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### cj_class {#sec-trust-cj-class}

```{r}
#| label: fig-grf-trust-cj-class
#| fig-cap: "GRF CATE of the Muslim profile by cj_class (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "cj_class"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

## CATE by moderator — respondent-level {#sec-trust-resp}

### q_gender {#sec-trust-q-gender}

```{r}
#| label: fig-grf-trust-q-gender
#| fig-cap: "GRF CATE of the Muslim profile by q_gender (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_gender"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_age {#sec-trust-q-age}

```{r}
#| label: fig-grf-trust-q-age
#| fig-cap: "GRF CATE of the Muslim profile across deciles of q_age (Trust): per-bin subset ATE with honest cluster-robust 95% CI (ribbon); grey histogram shows the covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_age"
col <- m_trust[[mod]]
bin <- ntile(col, 10)
rows <- list()
for (k in sort(unique(bin))) {
  sel <- bin == k
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(k)]] <- tibble(
    bin = k,
    x_pos = mean(col[sel]),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(lower = estimate - 1.96 * se, upper = estimate + 1.96 * se)
# distribution band
yr <- range(c(cate$lower, cate$upper))
pad <- 0.12 * diff(yr)
floor_y <- yr[1] - pad
span <- 0.20 * diff(yr)
h <- hist(col[!is.na(col)], breaks = 30, plot = FALSE)
hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
  mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
ggplot(cate, aes(x = x_pos)) +
  geom_rect(
    data = hd,
    aes(xmin = mid - w / 2, xmax = mid + w / 2, ymin = floor_y, ymax = bar_top),
    fill = "grey80",
    inherit.aes = FALSE
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(aes(y = estimate), colour = "#0072B2", linewidth = 0.8) +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 1.5) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr()
```

### q_identity_country {#sec-trust-q-identity-country}

```{r}
#| label: fig-grf-trust-q-identity-country
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_country (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_country"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_identity_eu {#sec-trust-q-identity-eu}

```{r}
#| label: fig-grf-trust-q-identity-eu
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_eu (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_eu"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_identity_europe {#sec-trust-q-identity-europe}

```{r}
#| label: fig-grf-trust-q-identity-europe
#| fig-cap: "GRF CATE of the Muslim profile by q_identity_europe (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_identity_europe"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_religion {#sec-trust-q-religion}

```{r}
#| label: fig-grf-trust-q-religion
#| fig-cap: "GRF CATE of the Muslim profile by q_religion (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts. Rare categories give wide CIs."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_religion"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_class {#sec-trust-q-class}

```{r}
#| label: fig-grf-trust-q-class
#| fig-cap: "GRF CATE of the Muslim profile by q_class (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_class"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_efficacy_understand {#sec-trust-q-eu-efficacy-understand}

```{r}
#| label: fig-grf-trust-q-eu-efficacy-understand
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_efficacy_understand (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_efficacy_understand"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_reps {#sec-trust-q-pop-reps}

```{r}
#| label: fig-grf-trust-q-pop-reps
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_reps (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_reps"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_goodevil {#sec-trust-q-pop-goodevil}

```{r}
#| label: fig-grf-trust-q-pop-goodevil
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_goodevil (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_goodevil"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_pop_compromise {#sec-trust-q-pop-compromise}

```{r}
#| label: fig-grf-trust-q-pop-compromise
#| fig-cap: "GRF CATE of the Muslim profile by q_pop_compromise (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_pop_compromise"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_dem_compromise {#sec-trust-q-dem-compromise}

```{r}
#| label: fig-grf-trust-q-dem-compromise
#| fig-cap: "GRF CATE of the Muslim profile by q_dem_compromise (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_dem_compromise"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_dem_listen {#sec-trust-q-dem-listen}

```{r}
#| label: fig-grf-trust-q-dem-listen
#| fig-cap: "GRF CATE of the Muslim profile by q_dem_listen (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_dem_listen"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_tech_experts {#sec-trust-q-tech-experts}

```{r}
#| label: fig-grf-trust-q-tech-experts
#| fig-cap: "GRF CATE of the Muslim profile by q_tech_experts (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_tech_experts"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_tech_leaders {#sec-trust-q-tech-leaders}

```{r}
#| label: fig-grf-trust-q-tech-leaders
#| fig-cap: "GRF CATE of the Muslim profile by q_tech_leaders (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_tech_leaders"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_party_harm {#sec-trust-q-party-harm}

```{r}
#| label: fig-grf-trust-q-party-harm
#| fig-cap: "GRF CATE of the Muslim profile by q_party_harm (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_party_harm"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_people_incompetent {#sec-trust-q-people-incompetent}

```{r}
#| label: fig-grf-trust-q-people-incompetent
#| fig-cap: "GRF CATE of the Muslim profile by q_people_incompetent (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_people_incompetent"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_longterm {#sec-trust-q-eu-longterm}

```{r}
#| label: fig-grf-trust-q-eu-longterm
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_longterm (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_longterm"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_responsive {#sec-trust-q-eu-responsive}

```{r}
#| label: fig-grf-trust-q-eu-responsive
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_responsive (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_responsive"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_econ {#sec-trust-q-eu-imp-nat-econ}

```{r}
#| label: fig-grf-trust-q-eu-imp-nat-econ
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_econ (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_econ"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_cul {#sec-trust-q-eu-imp-nat-cul}

```{r}
#| label: fig-grf-trust-q-eu-imp-nat-cul
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_cul (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_cul"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_imp_nat_pol {#sec-trust-q-eu-imp-nat-pol}

```{r}
#| label: fig-grf-trust-q-eu-imp-nat-pol
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_imp_nat_pol (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_imp_nat_pol"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_abolish {#sec-trust-q-eu-abolish}

```{r}
#| label: fig-grf-trust-q-eu-abolish
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_abolish (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_abolish"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_eu_satisfaction {#sec-trust-q-eu-satisfaction}

```{r}
#| label: fig-grf-trust-q-eu-satisfaction
#| fig-cap: "GRF CATE of the Muslim profile by q_eu_satisfaction (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_eu_satisfaction"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_rural_urban {#sec-trust-q-rural-urban}

```{r}
#| label: fig-grf-trust-q-rural-urban
#| fig-cap: "GRF CATE of the Muslim profile by q_rural_urban (Trust): per-level subset ATE with honest cluster-robust 95% CI (blue); grey bars show per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_rural_urban"
levs <- sort(unique(m_trust[[mod]]))
rows <- list()
for (lev in levs) {
  sel <- m_trust[[mod]] == lev
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(lev)]] <- tibble(
    level = as.character(lev),
    n = sum(sel),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(
    level = factor(level, levels = as.character(levs)),
    lower = estimate - 1.96 * se,
    upper = estimate + 1.96 * se
  )
yr <- range(c(cate$lower, cate$upper))
pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
floor_y <- yr[1] - pad
span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
cate <- cate |> mutate(bar_top = floor_y + (n / max(n)) * span)
ggplot(cate, aes(x = level)) +
  geom_segment(
    aes(xend = level, y = floor_y, yend = bar_top),
    colour = "grey80",
    linewidth = 4
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_linerange(aes(ymin = lower, ymax = upper), colour = "#0072B2") +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 2) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

### q_edu_age_stop {#sec-trust-q-edu-age-stop}

```{r}
#| label: fig-grf-trust-q-edu-age-stop
#| fig-cap: "GRF CATE of the Muslim profile across deciles of q_edu_age_stop (Trust): per-bin subset ATE with honest cluster-robust 95% CI (ribbon); grey histogram shows the covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
mod <- "q_edu_age_stop"
col <- m_trust[[mod]]
bin <- ntile(col, 10)
rows <- list()
for (k in sort(unique(bin))) {
  sel <- bin == k
  a <- grf::average_treatment_effect(cf_trust, subset = sel)
  rows[[as.character(k)]] <- tibble(
    bin = k,
    x_pos = mean(col[sel]),
    estimate = a["estimate"],
    se = a["std.err"]
  )
}
cate <- bind_rows(rows) |>
  mutate(lower = estimate - 1.96 * se, upper = estimate + 1.96 * se)
# distribution band
yr <- range(c(cate$lower, cate$upper))
pad <- 0.12 * diff(yr)
floor_y <- yr[1] - pad
span <- 0.20 * diff(yr)
h <- hist(col[!is.na(col)], breaks = 30, plot = FALSE)
hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
  mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
ggplot(cate, aes(x = x_pos)) +
  geom_rect(
    data = hd,
    aes(xmin = mid - w / 2, xmax = mid + w / 2, ymin = floor_y, ymax = bar_top),
    fill = "grey80",
    inherit.aes = FALSE
  ) +
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = "#0072B2") +
  geom_line(aes(y = estimate), colour = "#0072B2", linewidth = 0.8) +
  geom_point(aes(y = estimate), colour = "#0072B2", size = 1.5) +
  labs(title = paste0("CATE by ", mod), x = mod, y = yl) +
  ggpubr::theme_pubr()
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
