---
subtitle: |
  BCF Post-Processing — CATE by Moderator (Dictator + Trust)
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Purpose {#sec-purpose}

This notebook post-processes the **robustness** estimator — the saved hierarchical BCF fits
(`data/03_final/bcf_{dictator,trust}.rds`) — into Green (2012)–style figures: estimated CATE on
the y-axis, a moderator on the x-axis.
It is the BCF counterpart to `07_postprocess_grf.qmd` and is structurally parallel to it; only the
τ̂ extraction and the per-level uncertainty differ.

This is the first, *exploratory* pass.
For each moderator we build a **standalone `ggplot` object** (kept in a named list), not the final
composed/faceted figure; paneling is decided later.

Two moderator families, matching the research plan:

- **Conjoint round-level** moderators (`prof_mods`) — other attributes in the same profile.
- **Individual-level** moderators (`resp_mods`) — respondent pre-treatment items and indices.

Per-level uncertainty is the **95% posterior credible interval** of the bin/level CATE, mirroring
`fig-cate-by-cov-bcf` in `03_multibart_nested_ri_test.qmd`.
The credible interval here reflects posterior uncertainty only; the respondent cluster bootstrap
(within-person dependence across the three rounds) is a separate downstream step, not done here.
The covariate distribution is shown in every panel (rug for binned numerics, per-level count bars
for discrete moderators).

# Setup {#sec-setup}

The setup chunk loads the project packages plus `multibart`'s own dependencies before the local
package is attached (needed for `get_forest_fit()`).

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr, purrr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # later composition
  "sessioninfo", # session docs

  # multibart dependencies -----------------------------------------------------
  "Rcpp", # multibart Depends + LinkingTo
  "RcppArmadillo", # multibart Depends + LinkingTo
  "Rcereal", # multibart Depends + LinkingTo
  "fastDummies" # multibart helper dependency
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: setup-multibart
#| include: false
# install local source on first use
if (!requireNamespace("multibart", quietly = TRUE)) {
  install.packages(
    here::here("code", "multibart"),
    repos = NULL,
    type = "source"
  )
}
# attach installed package
library(multibart)
```

# Load data and fits {#sec-load}

```{r}
#| label: load-data
dat <- readRDS(here::here("data", "02_processed", "eu25_long.rds"))
fit_dict <- readRDS(here::here("data", "03_final", "bcf_dictator.rds"))
fit_trust <- readRDS(here::here("data", "03_final", "bcf_trust.rds"))
```

# Variable definitions {#sec-vars}

The frozen moderator list and `prep_game()` are reused verbatim from `05_bcf_fit.qmd` so the
reconstructed moderate design matches fit-time row order and columns exactly.

```{r}
#| label: moderators
prof_mods <- c("cj_nat", "cj_eupos", "cj_age", "cj_sex", "cj_class")
resp_mods <- c(
  "q_gender", "q_age", "q_identity_country", "q_identity_eu",
  "q_identity_europe", "q_religion", "q_class", "q_eu_efficacy_understand",
  "q_pop_reps", "q_pop_goodevil", "q_pop_compromise", "q_dem_compromise",
  "q_dem_listen", "q_tech_experts", "q_tech_leaders", "q_party_harm",
  "q_people_incompetent", "q_eu_longterm", "q_eu_responsive",
  "q_eu_imp_nat_econ", "q_eu_imp_nat_cul", "q_eu_imp_nat_pol",
  "q_eu_abolish", "q_eu_satisfaction", "q_rural_urban", "q_edu_age_stop"
)
```

```{r}
#| label: prep-game
prep_game <- function(dat, game) {
  sub <- dat |>
    filter(cj_game_type == game) # full per-game sample (no subsampling)

  y <- sub$cj_pl2
  z <- as.integer(sub$cj_rel == "muslim") # Muslim vs all-else pooled
  country_id <- factor(sub$meta_country)
  respondent_id <- factor(sub$meta_pid)

  mod_df <- sub |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
  sub_X <- model.matrix(~ . - 1, data = mod_df) # factors -> dummies

  stopifnot(
    !anyNA(sub_X),
    all(z %in% c(0L, 1L)),
    !anyNA(y),
    nrow(sub_X) == length(y)
  )

  list(
    y = y, z = z, sub_X = sub_X,
    country_id = country_id, respondent_id = respondent_id
  )
}
```

`game_mods()` returns the original (pre-dummy) moderator values for one game, in the same row
order as `prep_game()`, so each observation's τ̂ aligns with its moderator value.

```{r}
#| label: game-mods
game_mods <- function(dat, game) {
  dat |>
    filter(cj_game_type == game) |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
}
```

# CATE-by-moderator machinery {#sec-machinery}

A moderator is **discrete** (factor, or numeric with ≤ 10 distinct values: Likert items) or
**binned** (higher-cardinality numeric → 10 quantile bins).

```{r}
#| label: classify
classify_mod <- function(col) {
  if (is.factor(col) || is.character(col)) {
    return("discrete")
  }
  if (dplyr::n_distinct(col) <= 10) {
    return("discrete")
  }
  "binned"
}
```

For each moderator level / bin, the posterior of the bin CATE is the within-draw mean of τ(x) over
the bin's observations; we summarize with the median and a 95% credible interval.
`tau_draws` is the `nsim × n` posterior matrix from `get_forest_fit()`; columns index observations.

```{r}
#| label: bcf-summary
bcf_summary <- function(tau_draws, col, name) {
  kind <- classify_mod(col)
  # posterior of the bin CATE over a logical keep-vector (length n)
  post <- function(keep) {
    bd <- rowMeans(tau_draws[, keep, drop = FALSE]) # posterior of bin mean
    tibble(
      estimate = median(bd),
      lower = unname(quantile(bd, 0.025)),
      upper = unname(quantile(bd, 0.975))
    )
  }
  if (kind == "discrete") {
    levs <- if (is.factor(col)) levels(col) else sort(unique(col))
    out <- map(levs, function(v) {
      keep <- !is.na(col) & col == v
      post(keep) |>
        mutate(x_lab = as.character(v), x_pos = NA_real_, n = sum(keep))
    })
  } else {
    b <- ntile(col, 10)
    out <- map(sort(unique(b[!is.na(b)])), function(bb) {
      keep <- !is.na(b) & b == bb
      post(keep) |>
        mutate(x_lab = NA_character_, x_pos = mean(col[keep]), n = sum(keep))
    })
  }
  list_rbind(out) |> mutate(moderator = name, kind = kind)
}
```

The plot helpers draw blue estimates + credible interval and the covariate distribution.

```{r}
#| label: plot-helpers
.cate_col <- "#0072B2"

# discrete: pointrange per level + grey count bars (categorical distribution)
plot_discrete <- function(summ, name, ylab) {
  summ <- summ |>
    filter(!is.na(estimate)) |>
    mutate(x = factor(x_lab, levels = x_lab))
  yr <- range(c(summ$lower, summ$upper), na.rm = TRUE)
  pad <- if (diff(yr) > 0) 0.12 * diff(yr) else 0.5
  floor_y <- yr[1] - pad
  span <- if (diff(yr) > 0) 0.20 * diff(yr) else 0.5
  summ <- summ |> mutate(bar_top = floor_y + (n / max(n)) * span)

  ggplot(summ, aes(x = x)) +
    geom_segment(
      aes(xend = x, y = floor_y, yend = bar_top),
      colour = "grey80", linewidth = 4
    ) +
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
    geom_linerange(aes(ymin = lower, ymax = upper), colour = .cate_col) +
    geom_point(aes(y = estimate), colour = .cate_col, size = 2) +
    labs(title = paste0("CATE by ", name), x = name, y = ylab) +
    ggpubr::theme_pubr() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1))
}

# binned: ribbon + line + rug of raw values (continuous distribution)
plot_binned <- function(summ, raw, name, ylab) {
  rug <- tibble(value = raw)
  ggplot(summ, aes(x = x_pos)) +
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60") +
    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2, fill = .cate_col) +
    geom_line(aes(y = estimate), colour = .cate_col, linewidth = 0.8) +
    geom_point(aes(y = estimate), colour = .cate_col, size = 1.5) +
    geom_rug(
      data = rug, aes(x = value), sides = "b",
      alpha = 0.15, colour = .cate_col, inherit.aes = FALSE
    ) +
    labs(title = paste0("CATE by ", name), x = name, y = ylab) +
    ggpubr::theme_pubr()
}

plot_mod <- function(summ, raw, name, ylab) {
  if (summ$kind[1] == "discrete") {
    plot_discrete(summ, name, ylab)
  } else {
    plot_binned(summ, raw, name, ylab)
  }
}

# build one named list of plots over a set of moderators
build_bcf_plots <- function(tau_draws, mvals, mods, ylab) {
  setNames(
    lapply(mods, function(m) {
      col <- mvals[[m]]
      plot_mod(bcf_summary(tau_draws, col, m), col, m, ylab)
    }),
    mods
  )
}
```

# Build plots {#sec-build}

`tau_draws` is large (`nsim × n`); we extract it one game at a time and free it once the plots
(which retain only their summary tibbles) are built.

```{r}
#| label: build-dictator
yl <- "CATE (effect of Muslim profile)"

d_dict <- prep_game(dat, "cj_dict")
m_dict <- game_mods(dat, "cj_dict")
tau_dict <- get_forest_fit(fit_dict$moderate_fit, d_dict$sub_X) # nsim x n

stopifnot(
  nrow(m_dict) == length(d_dict$y),
  ncol(tau_dict) == length(d_dict$y)
)

# ATE sanity check (token scale)
mean(colMeans(tau_dict))

p_dict_prof <- build_bcf_plots(tau_dict, m_dict, prof_mods, yl)
p_dict_resp <- build_bcf_plots(tau_dict, m_dict, resp_mods, yl)

rm(tau_dict, fit_dict)
invisible(gc())
```

```{r}
#| label: build-trust
d_trust <- prep_game(dat, "cj_trust")
m_trust <- game_mods(dat, "cj_trust")
tau_trust <- get_forest_fit(fit_trust$moderate_fit, d_trust$sub_X) # nsim x n

stopifnot(
  nrow(m_trust) == length(d_trust$y),
  ncol(tau_trust) == length(d_trust$y)
)

mean(colMeans(tau_trust))

p_trust_prof <- build_bcf_plots(tau_trust, m_trust, prof_mods, yl)
p_trust_resp <- build_bcf_plots(tau_trust, m_trust, resp_mods, yl)

rm(tau_trust, fit_trust)
invisible(gc())

stopifnot(
  length(p_dict_prof) == length(prof_mods),
  length(p_dict_resp) == length(resp_mods),
  length(p_trust_prof) == length(prof_mods),
  length(p_trust_resp) == length(resp_mods)
)
```

# Dictator game {#sec-dictator}

## Conjoint round-level moderators {#sec-dict-prof}

```{r}
#| label: fig-bcf-dict-prof
#| fig-cap: "BCF: CATE of the Muslim profile attribute by conjoint round-level moderator (Dictator game). Blue: posterior median + 95% credible interval; grey bars: per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
walk(p_dict_prof, print)
```

## Individual-level moderators {#sec-dict-resp}

```{r}
#| label: fig-bcf-dict-resp
#| fig-cap: "BCF: CATE of the Muslim profile attribute by respondent-level moderator (Dictator game). Blue: posterior median + 95% credible interval; grey bars / rug: covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
walk(p_dict_resp, print)
```

# Trust game {#sec-trust}

## Conjoint round-level moderators {#sec-trust-prof}

```{r}
#| label: fig-bcf-trust-prof
#| fig-cap: "BCF: CATE of the Muslim profile attribute by conjoint round-level moderator (Trust game). Blue: posterior median + 95% credible interval; grey bars: per-level counts."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
walk(p_trust_prof, print)
```

## Individual-level moderators {#sec-trust-resp}

```{r}
#| label: fig-bcf-trust-resp
#| fig-cap: "BCF: CATE of the Muslim profile attribute by respondent-level moderator (Trust game). Blue: posterior median + 95% credible interval; grey bars / rug: covariate distribution."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
walk(p_trust_resp, print)
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true

end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
