---
subtitle: |
  BCF Post-Processing — ATE, Posterior Projection, and CATE by Moderator (Dictator + Trust)
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Purpose {#sec-purpose}

This notebook post-processes the **robustness** estimator — the saved hierarchical BCF fits
(`data/03_final/bcf_{dictator,trust}.rds`) — into the same three quantities, in the same order,
as the combined view of the primary GRF notebook `07_postprocess_grf.qmd`:

1. **Average treatment effect (ATE)** — the posterior of the ATE for each game.
2. **Posterior linear projection** — the Bayesian counterpart to GRF's best linear projection
   (`woody2021model`): each posterior draw of τ(x) is projected onto the moderator design, giving
   a posterior distribution of projection coefficients. Appendix-style linear summary.
3. **CATE by moderator** — the headline figures: estimated CATE on the y-axis, a moderator on the
   x-axis.

It is the BCF counterpart to `07_postprocess_grf.qmd` and is structurally parallel to it; only the
inference machinery differs. GRF reports point estimates with honest cluster-robust confidence
intervals; BCF reports **posterior medians** (read off the τ(x) draws from `get_forest_fit()`) with
95% credible intervals for the ATE and projection, and a cluster-robust band for the CATE-by-moderator
figures that adds a respondent cluster bootstrap to the posterior SD (see @sec-cluster-bootstrap).

Following the **combined-figure** grammar of `07` (its `# Combined figures` section) and the house
style of `09_additional_figs_tables.qmd`, every figure overlays **both games on one canvas**. The two
games are the only thing encoded by colour, shape, and linetype, and they are always encoded by all
three together, so each game is distinguishable in colour, in greyscale print, and under
colourblindness. Every other distinction (which moderator, which level) is carried by facets and
axis position.

Two moderator families, matching the research plan:

- **Conjoint round-level** moderators (`prof_mods`) — other attributes in the same profile.
- **Individual-level** moderators (`resp_mods`) — respondent pre-treatment items and indices.

Per-level uncertainty is a **cluster-robust 95% interval**: the posterior median of the bin/level
CATE (cf. `fig-cate-by-cov-bcf` in `03_multibart_nested_ri_test.qmd`) with a band that combines the
posterior SD (model/estimation uncertainty) and a **respondent cluster bootstrap** SD (within-person
dependence across the three rounds; see @sec-cluster-bootstrap). We added the bootstrap to test the
worry that the bands looked too narrow at low-count levels: the answer is that within-respondent
clustering does **not** explain it — the posterior SD dominates the bootstrap SD by roughly an order
of magnitude at every level, and it already widens appropriately as the level count shrinks. The
bands are, in other words, genuinely that precise; the bootstrap is folded in for completeness but
moves them by only a few percent.

# Setup {#sec-setup}

The setup chunk loads the project packages plus `multibart`'s own dependencies before the local
package is attached (needed for `get_forest_fit()`).

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr, purrr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # combined-figure composition
  "sessioninfo", # session docs

  # multibart dependencies -----------------------------------------------------
  "Rcpp", # multibart Depends + LinkingTo
  "RcppArmadillo", # multibart Depends + LinkingTo
  "Rcereal", # multibart Depends + LinkingTo
  "fastDummies" # multibart helper dependency
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: setup-multibart
#| include: false
# install local source on first use
if (!requireNamespace("multibart", quietly = TRUE)) {
  install.packages(
    here::here("code", "multibart"),
    repos = NULL,
    type = "source"
  )
}
# attach installed package
library(multibart)
```

# Load data and fits {#sec-load}

```{r}
#| label: load-data
dat <- readRDS(here::here("data", "02_processed", "eu25_long.rds"))
fit_dict <- readRDS(here::here("data", "03_final", "bcf_dictator.rds"))
fit_trust <- readRDS(here::here("data", "03_final", "bcf_trust.rds"))
```

# Variable definitions {#sec-vars}

The frozen moderator list and `prep_game()` are reused verbatim from `05_bcf_fit.qmd` so the
reconstructed moderator design matches fit-time row order and columns exactly.

```{r}
#| label: moderators
prof_mods <- c(
  "cj_nat",
  "der_cj_eu_identity",
  "der_cj_partisanship",
  "cj_age",
  "cj_sex",
  "cj_class"
)
resp_mods <- c(
  "q_gender",
  "q_age",
  "q_identity_country",
  "q_identity_eu",
  "q_identity_europe",
  "q_religion",
  "q_class",
  "q_eu_efficacy_understand",
  "q_pop_reps",
  "q_pop_goodevil",
  "q_pop_compromise",
  "q_dem_compromise",
  "q_dem_listen",
  "q_tech_experts",
  "q_tech_leaders",
  "q_party_harm",
  "q_people_incompetent",
  "q_eu_longterm",
  "q_eu_responsive",
  "q_eu_imp_nat_econ",
  "q_eu_imp_nat_cul",
  "q_eu_imp_nat_pol",
  "q_eu_abolish",
  "q_eu_satisfaction",
  "q_rural_urban",
  "q_edu_age_stop"
)
```

```{r}
#| label: prep-game
prep_game <- function(dat, game) {
  sub <- dat |>
    filter(cj_game_type == game) # full per-game sample (no subsampling)

  y <- sub$cj_pl2
  z <- as.integer(sub$cj_rel == "muslim") # Muslim vs all-else pooled
  country_id <- factor(sub$meta_country)
  respondent_id <- factor(sub$meta_pid)

  mod_df <- sub |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
  sub_X <- model.matrix(~ . - 1, data = mod_df) # factors -> dummies

  stopifnot(
    !anyNA(sub_X),
    all(z %in% c(0L, 1L)),
    !anyNA(y),
    nrow(sub_X) == length(y)
  )

  list(
    y = y,
    z = z,
    sub_X = sub_X,
    country_id = country_id,
    respondent_id = respondent_id
  )
}
```

`game_mods()` returns the original (pre-dummy) moderator values for one game, in the same row
order as `prep_game()`, so each observation's τ̂ aligns with its moderator value.

```{r}
#| label: game-mods
game_mods <- function(dat, game) {
  dat |>
    filter(cj_game_type == game) |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
}
```

# House style {#sec-house}

The Okabe-Ito game palette with redundant shape and linetype, the three reserved scales, the
shared theme, and the reference layers — copied from `09_additional_figs_tables.qmd` / the combined
section of `07_postprocess_grf.qmd` so the BCF figures share the manuscript grammar exactly.

```{r}
#| label: game-style
game_labs <- c(cj_dict = "Dictator game", cj_trust = "Trust game")
game_cols <- c("Dictator game" = "#0072B2", "Trust game" = "#D55E00")
game_shapes <- c("Dictator game" = 16, "Trust game" = 17) # circle / triangle
game_ltys <- c("Dictator game" = "solid", "Trust game" = "longdash")

scale_colour_game <- function() {
  scale_colour_manual(values = game_cols, name = NULL)
}
scale_shape_game <- function() {
  scale_shape_manual(values = game_shapes, name = NULL)
}
scale_linetype_game <- function() {
  scale_linetype_manual(values = game_ltys, name = NULL)
}

# shared moderator labels + categorical-first ordering for the facets
source(here::here("code", "helper_scripts", "moderator_labels.R"))

theme_mbeu <- function(base_size = 11) {
  ggpubr::theme_pubr(base_size = base_size) +
    theme(legend.position = "top")
}
ref_zero <- geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60")
dodge <- position_dodge(width = 0.5)
yl_cate <- expression(widehat(CATE))
yl_ric <- expression(hat(tau)[ric]) # profile-level CATE
yl_i <- expression(hat(tau)[ic]) # respondent-level CATE
```

# Posterior summary builders {#sec-machinery}

Every quantity below is read off `tau_draws`, the `nsim × n` posterior matrix returned by
`get_forest_fit()` (rows index posterior draws, columns index observations). All three builders
operate on a single game's `tau_draws`, so they run inside the per-game block and the large matrix
is freed before the next game.

A moderator is **discrete** (factor, or numeric with ≤ 10 distinct values: Likert items) or
**binned** (higher-cardinality numeric → 10 quantile bins).

```{r}
#| label: classify
classify_mod <- function(col) {
  if (is.factor(col) || is.character(col)) {
    return("discrete")
  }
  if (dplyr::n_distinct(col) <= 10) {
    return("discrete")
  }
  "binned"
}
```

Shared display specs, matching `07_postprocess_grf.qmd`: the substantive `q_class` order
(`dont_know` last), the 5-point-scale reversal (`6 - x`) applied to the identity scales (so higher
means more attachment) and to the "EU effect on" items (so higher means a more positive evaluation),
the two fixed display grids for the genuinely continuous moderators, and the number of cluster
bootstrap resamples.

```{r}
#| label: display-specs
class_order <- c(
  "working_class",
  "lower_middle_class",
  "middle_class",
  "upper_middle_class",
  "higher_class",
  "dont_know",
  "other"
)
flip5 <- \(x) 6 - x # 5-point scales: reverse so higher = more of the construct
cont_grids <- list(
  q_age = seq(18, 75, length.out = 101), # 100 intervals over the full range
  q_edu_age_stop = seq(14.5, 30.5, by = 1) # integer years 15..30
)
boot_B <- 500L # respondent cluster bootstrap resamples
```

`ate_summary()` returns the posterior of the ATE: the per-draw mean of τ(x) over all observations,
summarised by its median and a 95% credible interval.

```{r}
#| label: ate-summary
ate_summary <- function(tau_draws) {
  bd <- rowMeans(tau_draws) # posterior of the ATE
  tibble(
    estimate = median(bd),
    lower = unname(quantile(bd, 0.025)),
    upper = unname(quantile(bd, 0.975))
  )
}
```

`proj_summary()` is the Bayesian posterior projection (`woody2021model`), the BCF counterpart to
GRF's `best_linear_projection`. For each posterior draw `d`, the coefficient vector is
$\beta_d = (X'X)^{-1} X' \tau_d$; we stack these into a posterior and summarise each term by its
median and 95% credible interval.
The design `sub_X` is `model.matrix(~ . - 1, ...)`, which is full rank (only the first factor is
fully expanded; the rest are contrast-coded), so `crossprod(sub_X)` inverts directly — no added
intercept, no ridge. It is the same column basis as GRF's `X_dict`, so the terms are comparable.
The only large multiply (`tau_draws %*% sub_X`) returns a small `nsim × p` matrix, so the step is
memory-safe.

```{r}
#| label: proj-summary
proj_summary <- function(tau_draws, sub_X) {
  xtx <- crossprod(sub_X) # p x p
  m <- tau_draws %*% sub_X # nsim x p  (= tau_d' X per draw)
  beta <- solve(xtx, t(m)) # p x nsim  = (X'X)^{-1} X' tau_d
  tibble(
    term = colnames(sub_X),
    estimate = apply(beta, 1, median),
    lower = apply(beta, 1, quantile, 0.025),
    upper = apply(beta, 1, quantile, 0.975)
  )
}
```

`level_keeps()` enumerates the kept levels/bins of one moderator and returns, for each, the logical
keep-vector over the game's rows together with its display `level`, `order`, and `is_scale` tag.
It mirrors the combined builder in `07` exactly — discrete levels honor the factor order and are
dropped below **1% of the game sample** (their CATE is too imprecise to compare); `cj_age` is
treated as categorical (fixed conjoint ages); and the two genuinely continuous moderators are
binned on the **fixed display grid** (`cont_grids`) rather than into deciles, so the line spans the
full range. Sharing this enumeration between the posterior summary and the cluster bootstrap
guarantees the two use identical bins.

```{r}
#| label: level-keeps
level_keeps <- function(mm, mod) {
  v <- mm[[mod]]
  is_num <- is.numeric(v)
  # genuinely continuous moderators -> fixed grid (or decile fallback)
  if (is_num && length(unique(v)) > 12) {
    if (mod %in% names(cont_grids)) {
      br <- cont_grids[[mod]]
      cell <- cut(v, breaks = br, include.lowest = TRUE)
      mids <- (head(br, -1) + tail(br, -1)) / 2
      out <- lapply(
        which(tabulate(cell, nbins = length(mids)) > 0),
        function(k) {
          keep <- !is.na(cell) & as.integer(cell) == k
          list(
            level = as.character(round(mids[k])),
            order = mids[k],
            is_scale = TRUE,
            keep = keep
          )
        }
      )
      return(out)
    }
    bin <- ntile(v, 10)
    return(lapply(sort(unique(bin)), function(k) {
      keep <- !is.na(bin) & bin == k
      list(
        level = as.character(round(mean(v[keep]))),
        order = mean(v[keep]),
        is_scale = TRUE,
        keep = keep
      )
    }))
  }
  # discrete moderators: honor factor order; drop levels below 1% of the game sample
  levs <- if (is_num) {
    sort(unique(v))
  } else if (is.factor(v)) {
    levels(droplevels(v))
  } else {
    sort(unique(as.character(v)))
  }
  out <- lapply(seq_along(levs), function(i) {
    lev <- levs[i]
    keep <- if (is_num) {
      !is.na(v) & v == lev
    } else {
      !is.na(v) & as.character(v) == lev
    }
    if (sum(keep) / sum(!is.na(v)) < 0.01) {
      return(NULL)
    }
    list(
      level = as.character(lev),
      order = if (is_num) as.numeric(lev) else i,
      is_scale = is_num && mod != "cj_age",
      keep = keep
    )
  })
  out[!vapply(out, is.null, logical(1))]
}
```

`cate_one_bcf()` reads each bin's estimate off the **posterior of the bin mean** (`rowMeans` of
τ(x) over the bin's observations): the point is the posterior median and `post_sd` is the posterior
standard deviation, the **model/estimation** uncertainty. The final interval (built downstream)
adds the respondent-cluster bootstrap variance to this.

```{r}
#| label: cate-one-bcf
# posterior of the bin CATE over a logical keep-vector (length n)
.bin_post <- function(tau_draws, keep) {
  bd <- rowMeans(tau_draws[, keep, drop = FALSE]) # posterior of bin mean
  c(estimate = median(bd), post_sd = sd(bd))
}

cate_one_bcf <- function(tau_draws, mm, mod, game_label) {
  ks <- level_keeps(mm, mod)
  bind_rows(lapply(ks, function(L) {
    p <- .bin_post(tau_draws, L$keep)
    tibble(
      mod = mod,
      level = L$level,
      order = L$order,
      is_scale = L$is_scale,
      game = game_label,
      n = sum(L$keep),
      estimate = unname(p["estimate"]),
      post_sd = unname(p["post_sd"])
    )
  }))
}
```

## Respondent cluster bootstrap {#sec-cluster-bootstrap}

The posterior `post_sd` above captures **model/estimation** uncertainty in the regularized τ(x)
surface alone — not the within-respondent design dependence (each respondent contributes three
conjoint rounds) and not the sampling variability of which respondents land in a bin. The worry was
that omitting this clustering made the bands look too narrow, especially at sparsely populated
levels. We test that directly with a **respondent cluster bootstrap**: resample respondents (the
clusters) with replacement `boot_B` times, recompute each bin's mean of the per-observation point
estimate `tau_hat`, and take the bootstrap SD as the design/clustering component. The two variances
are combined, `se_total = sqrt(post_sd² + boot_sd²)`, and the band is `estimate ± 1.96 · se_total` —
a single cluster-robust interval, with the posterior median unchanged as the point estimate. One
shared set of resamples (`Wb`, a respondent × `boot_B` multiplicity matrix) is reused across every
moderator and level for efficiency; the bootstrap runs after `tau_draws` is freed, so it needs only
the length-`n` `tau_hat`.

**The verdict is that clustering does not explain the narrowness.** On the real fits the bootstrap SD
is roughly an order of magnitude smaller than `post_sd` at every level (e.g. `post_sd` ≈ 0.03–0.08
versus `boot_sd` ≈ 0.003–0.011), so `se_total` exceeds `post_sd` by only about 1–3%. The posterior
SD is itself the dominant term and already widens as the level count falls (it scales roughly like
1/√n: a ~40k-row level carries about half the posterior SD of a ~3k-row level). The bands are
genuinely that precise — a consequence of how aggressively BCF pools strength across the sample — and
the very rare levels that looked suspiciously tight are dropped anyway by the 1% rule. We keep the
cluster-robust band because it is the more honest object, but it confirms rather than overturns the
posterior intervals.

```{r}
#| label: boot-helpers
# build the respondent x B bootstrap multiplicity matrix once per game
make_Wb <- function(rid, B, seed) {
  set.seed(seed)
  rid_int <- as.integer(rid)
  R <- max(rid_int)
  Wb <- vapply(
    seq_len(B),
    function(b) tabulate(sample.int(R, R, replace = TRUE), nbins = R),
    integer(R)
  )
  list(Wb = Wb, rid_int = rid_int)
}

# per-level cluster-bootstrap SD of the bin mean of tau_hat
boot_sd_one <- function(tau_hat, rid_int, Wb, mm, mod) {
  ks <- level_keeps(mm, mod)
  bind_rows(lapply(ks, function(L) {
    keep <- L$keep
    w <- Wb[rid_int[keep], , drop = FALSE] # n_keep x B multiplicities
    bm <- colSums(w * tau_hat[keep]) / colSums(w) # B bootstrap bin means
    tibble(mod = mod, level = L$level, boot_sd = sd(bm))
  }))
}

# join the bootstrap SD and form the cluster-robust interval
finalize_ci <- function(df, boot) {
  df |>
    left_join(boot, by = c("mod", "level", "game")) |>
    mutate(
      boot_sd = coalesce(boot_sd, 0),
      se_total = sqrt(post_sd^2 + boot_sd^2),
      lower = estimate - 1.96 * se_total,
      upper = estimate + 1.96 * se_total
    )
}
```

# Combined plotters {#sec-plotters}

`plot_comb()` draws the faceted overview with a free y-axis per facet: grey per-level count bars
(pooled over games) along the bottom, posterior medians and credible intervals dodged by game
everywhere, plus a connecting line and ribbon on the ordered-scale facets only.
It is reused verbatim from the combined section of `07` (it reads only the summary columns the BCF
builders produce, so the posterior intervals slot straight in).

```{r}
#| label: plot-comb
plot_comb <- function(df, ncol, title, ylab = yl_i) {
  d <- df |>
    arrange(mod, order) |>
    mutate(
      key = factor(
        paste0(mod, "@@", level),
        levels = unique(paste0(mod, "@@", level))
      )
    )
  # per-facet grey count bars (pooled over games shown)
  band <- d |>
    summarise(cnt = sum(n), .by = c(mod, key)) |>
    left_join(
      d |>
        summarise(
          floor_y = min(lower) - 0.12 * (max(upper) - min(lower)),
          span = 0.20 * (max(upper) - min(lower)),
          .by = mod
        ),
      by = "mod"
    ) |>
    mutate(bar_top = floor_y + (cnt / max(cnt)) * span, .by = mod)
  d_scale <- dplyr::filter(d, is_scale)
  d_cat <- dplyr::filter(d, !is_scale)
  p <- ggplot(d, aes(x = key, y = estimate, colour = game, shape = game)) +
    geom_segment(
      data = band,
      aes(x = key, xend = key, y = floor_y, yend = bar_top),
      colour = "grey80",
      linewidth = 3,
      inherit.aes = FALSE
    ) +
    ref_zero
  # ordered scales: overlaid ribbon + line + point (continuous-style)
  if (nrow(d_scale) > 0) {
    p <- p +
      geom_ribbon(
        data = d_scale,
        aes(ymin = lower, ymax = upper, fill = game, group = game),
        alpha = 0.15,
        colour = NA
      ) +
      geom_line(data = d_scale, aes(group = game, linetype = game)) +
      geom_point(data = d_scale) +
      scale_linetype_game() +
      scale_fill_manual(values = game_cols, name = NULL)
  }
  # categorical: dodged credible interval + point
  if (nrow(d_cat) > 0) {
    p <- p +
      geom_linerange(
        data = d_cat,
        aes(ymin = lower, ymax = upper),
        position = dodge
      ) +
      geom_point(data = d_cat, position = dodge)
  }
  p +
    facet_wrap(
      ~mod,
      scales = "free",
      ncol = ncol,
      labeller = labeller(mod = mod_strip)
    ) +
    scale_colour_game() +
    scale_shape_game() +
    scale_x_discrete(labels = relabel_key) +
    labs(title = title, x = NULL, y = ylab) +
    guides(fill = "none", linetype = "none") +
    theme_mbeu() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
}
```

`cont_panel()` draws one genuinely continuous moderator on a continuous x-axis: its per-grid-cell
CATE (ribbon + line + point per game) over a grey histogram of the covariate, with the x-axis
trimmed to `xlim`. Unlike the `07` version it takes the **precomputed** combined sub-tibble `d`
(the BCF draws are already freed by plotting time) and the raw covariate values `raw` for the
histogram.

```{r}
#| label: cont-panel
cont_panel <- function(d, raw, mod, xlim, ylab = yl_i) {
  # covariate distribution within the visible range
  v <- raw[!is.na(raw) & raw >= xlim[1] & raw <= xlim[2]]
  h <- hist(v, breaks = 30, plot = FALSE)
  floor_y <- min(d$lower) - 0.12 * (max(d$upper) - min(d$lower))
  span <- 0.20 * (max(d$upper) - min(d$lower))
  hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
    mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
  ggplot(d, aes(x = order, y = estimate, colour = game, shape = game)) +
    geom_rect(
      data = hd,
      aes(
        xmin = mid - w / 2,
        xmax = mid + w / 2,
        ymin = floor_y,
        ymax = bar_top
      ),
      fill = "grey80",
      inherit.aes = FALSE
    ) +
    ref_zero +
    geom_ribbon(
      aes(ymin = lower, ymax = upper, fill = game, group = game),
      alpha = 0.15,
      colour = NA
    ) +
    geom_line(aes(group = game, linetype = game)) +
    geom_point() +
    scale_colour_game() +
    scale_shape_game() +
    scale_linetype_game() +
    scale_fill_manual(values = game_cols, name = NULL) +
    scale_x_continuous(breaks = scales::breaks_pretty(6)) +
    coord_cartesian(xlim = xlim) +
    labs(title = mod_labels[[mod]], x = "Covariate value (years)", y = ylab) +
    theme_mbeu()
}
```

# Build summaries {#sec-build}

`tau_draws` is large (`nsim × n`); we extract it one game at a time and free it once the small
summary tibbles (ATE, projection, and the combined CATE-by-moderator tables) are built.

```{r}
#| label: build-dictator
d_dict <- prep_game(dat, "cj_dict")
m_dict <- game_mods(dat, "cj_dict") |>
  # presentational recodings (display only; sub_X / projection untouched)
  mutate(
    across(
      c(
        q_identity_country, q_identity_eu, q_identity_europe,
        q_eu_imp_nat_econ, q_eu_imp_nat_cul, q_eu_imp_nat_pol
      ),
      flip5
    ),
    q_class = factor(q_class, levels = class_order),
    q_rural_urban = factor(
      q_rural_urban,
      levels = c("rural", "small_med_town", "large_city")
    )
  )
tau_dict <- get_forest_fit(fit_dict$moderate_fit, d_dict$sub_X) # nsim x n

stopifnot(
  nrow(m_dict) == length(d_dict$y),
  ncol(tau_dict) == length(d_dict$y)
)

# per-observation point estimate for the cluster bootstrap
tau_hat_dict <- colMeans(tau_dict)
# ATE sanity check (token scale)
mean(tau_hat_dict)

ate_dict <- ate_summary(tau_dict)
proj_dict <- proj_summary(tau_dict, d_dict$sub_X)
comb_prof_dict <- bind_rows(
  lapply(prof_mods, \(m) cate_one_bcf(tau_dict, m_dict, m, "Dictator game"))
)
comb_resp_dict <- bind_rows(
  lapply(resp_mods, \(m) cate_one_bcf(tau_dict, m_dict, m, "Dictator game"))
)

rm(tau_dict, fit_dict)
invisible(gc())

# respondent cluster bootstrap (runs after tau_dict is freed)
bw_dict <- make_Wb(d_dict$respondent_id, B = boot_B, seed = 1L)
boot_prof_dict <- bind_rows(
  lapply(prof_mods, \(m) {
    boot_sd_one(tau_hat_dict, bw_dict$rid_int, bw_dict$Wb, m_dict, m)
  })
) |>
  mutate(game = "Dictator game")
boot_resp_dict <- bind_rows(
  lapply(resp_mods, \(m) {
    boot_sd_one(tau_hat_dict, bw_dict$rid_int, bw_dict$Wb, m_dict, m)
  })
) |>
  mutate(game = "Dictator game")
rm(bw_dict)
invisible(gc())
```

```{r}
#| label: build-trust
d_trust <- prep_game(dat, "cj_trust")
m_trust <- game_mods(dat, "cj_trust") |>
  mutate(
    across(
      c(
        q_identity_country, q_identity_eu, q_identity_europe,
        q_eu_imp_nat_econ, q_eu_imp_nat_cul, q_eu_imp_nat_pol
      ),
      flip5
    ),
    q_class = factor(q_class, levels = class_order),
    q_rural_urban = factor(
      q_rural_urban,
      levels = c("rural", "small_med_town", "large_city")
    )
  )
tau_trust <- get_forest_fit(fit_trust$moderate_fit, d_trust$sub_X) # nsim x n

stopifnot(
  nrow(m_trust) == length(d_trust$y),
  ncol(tau_trust) == length(d_trust$y)
)

tau_hat_trust <- colMeans(tau_trust)
mean(tau_hat_trust)

ate_trust <- ate_summary(tau_trust)
proj_trust <- proj_summary(tau_trust, d_trust$sub_X)
comb_prof_trust <- bind_rows(
  lapply(prof_mods, \(m) cate_one_bcf(tau_trust, m_trust, m, "Trust game"))
)
comb_resp_trust <- bind_rows(
  lapply(resp_mods, \(m) cate_one_bcf(tau_trust, m_trust, m, "Trust game"))
)

rm(tau_trust, fit_trust)
invisible(gc())

bw_trust <- make_Wb(d_trust$respondent_id, B = boot_B, seed = 2L)
boot_prof_trust <- bind_rows(
  lapply(prof_mods, \(m) {
    boot_sd_one(tau_hat_trust, bw_trust$rid_int, bw_trust$Wb, m_trust, m)
  })
) |>
  mutate(game = "Trust game")
boot_resp_trust <- bind_rows(
  lapply(resp_mods, \(m) {
    boot_sd_one(tau_hat_trust, bw_trust$rid_int, bw_trust$Wb, m_trust, m)
  })
) |>
  mutate(game = "Trust game")
rm(bw_trust)
invisible(gc())
```

The combined tables, with both games stacked and `mod` ordered for faceting.

```{r}
#| label: combine
game_lvls <- c("Dictator game", "Trust game")

ate_comb <- bind_rows(
  ate_dict |> mutate(game = "Dictator game"),
  ate_trust |> mutate(game = "Trust game")
) |>
  mutate(game = factor(game, levels = game_lvls))

proj_comb <- bind_rows(
  proj_dict |> mutate(game = "Dictator game"),
  proj_trust |> mutate(game = "Trust game")
) |>
  mutate(game = factor(game, levels = game_lvls))

boot_prof <- bind_rows(boot_prof_dict, boot_prof_trust)
boot_resp <- bind_rows(boot_resp_dict, boot_resp_trust)

comb_prof <- bind_rows(comb_prof_dict, comb_prof_trust) |>
  finalize_ci(boot_prof) |>
  mutate(mod = factor(mod, levels = prof_mods))
comb_resp <- bind_rows(comb_resp_dict, comb_resp_trust) |>
  finalize_ci(boot_resp) |>
  mutate(mod = factor(mod, levels = resp_mods))

stopifnot(
  nrow(ate_comb) == 2,
  all(prof_mods %in% comb_prof$mod),
  all(resp_mods %in% comb_resp$mod),
  # cluster-robust band is never narrower than the posterior-only band
  all(comb_prof$se_total >= comb_prof$post_sd - 1e-9),
  all(comb_resp$se_total >= comb_resp$post_sd - 1e-9)
)
```

# The recovered ATEs {#sec-ate}

The posterior ATE — the per-draw average of τ(x) over all observations — for each game, reported as
the posterior median and 95% credible interval (the manuscript quotes these numbers in a footnote
alongside the GRF SATEs).

```{r}
#| label: ate-bcf-numbers
for (i in seq_len(nrow(ate_comb))) {
  cat(sprintf(
    "%s BCF ATE (posterior median): %.4f;  95%% CrI [%.4f, %.4f]\n",
    ate_comb$game[i],
    ate_comb$estimate[i],
    ate_comb$lower[i],
    ate_comb$upper[i]
  ))
}
```

# The posterior linear projections {#sec-proj}

The posterior projection of τ(x) onto the moderator design: a linear summary of which moderators
shift the treatment effect, the Bayesian counterpart to GRF's best linear projection
(@woody2021model).
This is an appendix/robustness summary, not a headline. Terms are ordered by their mean posterior
coefficient across the two games.

```{r}
#| label: fig-bcf-combined-proj
#| fig-cap: "BCF posterior linear projection of the CATE onto the moderator set, both games overlaid, with 95% credible intervals (dodged by game). Each coefficient is the posterior of (X'X)^{-1} X' tau_d. Terms are ordered by their mean coefficient across the two games. Appendix-style linear summary of effect modification."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 9
proj_ord <- proj_comb |>
  summarise(m = mean(estimate), .by = term) |>
  arrange(m) |>
  pull(term)
proj_plot <- proj_comb |> mutate(term = factor(term, levels = proj_ord))

ggplot(proj_plot, aes(x = estimate, y = term, colour = game, shape = game)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper), position = dodge) +
  scale_colour_game() +
  scale_shape_game() +
  labs(
    title = "Posterior linear projection of the CATE, both games",
    x = "Projection coefficient",
    y = NULL
  ) +
  theme_mbeu()
```

# The posterior CATEs by moderator {#sec-cate}

The headline figures: posterior median CATE on the y-axis, the moderator on the x-axis, with a
cluster-robust 95% interval at each level/grid cell, both games overlaid. The y-axis is free per
facet; discrete levels comprising less than 1% of a game's sample are dropped because their CATE is
too imprecise to compare. The three identity scales are reversed so higher means more attachment,
the three "EU effect on" items are reversed so higher means a more positive evaluation, and
`q_class` runs working class up to higher class with `dont_know` last.

## Conjoint round-level moderators {#sec-cate-prof}

All five conjoint-round (profile-level) moderators on one canvas, Dictator and Trust overlaid.
All five are categorical (including `cj_age`, whose five values are fixed conjoint ages), so each is
drawn as dodged points with cluster-robust intervals.

```{r}
#| label: fig-bcf-combined-prof
#| fig-cap: "BCF posterior estimates of the profile-level CATE of the Muslim profile across the levels of every conjoint-round moderator (x-axis), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. The y-axis ($\\hat{\\tau}_{ric}$) is the profile-level CATE on the token-allocation scale. Points are per-level posterior medians and the vertical bars are cluster-robust 95% intervals (posterior SD of the within-level mean of the CATE combined with a respondent cluster-bootstrap SD). Grey bars along the bottom of each facet show the per-level row count (pooled over games). The y-axis is free per facet; levels comprising less than 1% of a game's sample are dropped because their CATE is too imprecise to compare."
#| dpi: 500
#| fig-width: 9
#| fig-height: 6
plot_comb(
  comb_prof,
  ncol = 3,
  title = bquote("CATE by conjoint-round moderator, both games" ~ (hat(tau)[ric])),
  ylab = yl_ric
)
```

## Individual-level moderators {#sec-cate-resp}

The respondent-level moderators on two figures so the facets stay legible.
Each figure stacks (via `patchwork`) a faceted panel of half the discrete moderators on top with one
of the two genuinely continuous moderators (`q_age`, `q_edu_age_stop`) on a continuous x-axis below,
so the continuous covariate keeps its real histogram and trimmed axis while still sitting beside the
discrete moderators it belongs with.
Ordered numeric scales (the 5- and 7-point items) carry an overlaid cluster-robust 95% ribbon
plus connecting line per game; categorical moderators keep dodged points and intervals.
The three identity scales are reversed so higher means more attachment, the three "EU effect on"
items are reversed so higher means a more positive evaluation, and `q_class` runs working class up
to higher class with `dont_know` last.
The shared game legend is drawn once, from the top panel.

```{r}
#| label: resp-split
resp_cat <- setdiff(resp_mods, c("q_age", "q_edu_age_stop"))
# categorical moderators first, then the ordered scales
resp_cat <- c(intersect(cat_mods, resp_cat), setdiff(resp_cat, cat_mods))
half <- ceiling(length(resp_cat) / 2)
resp_half1 <- resp_cat[1:half]
resp_half2 <- resp_cat[(half + 1):length(resp_cat)]
```

```{r}
#| label: fig-bcf-combined-resp-1
#| fig-cap: "BCF posterior estimates of the respondent-level CATE of the Muslim profile across the levels of the first half of the discrete individual-level moderators (top panel) and across age (q_age, bottom panel), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. The y-axis ($\\hat{\\tau}_i$) is the respondent-level CATE on the token-allocation scale. Identity scales are reversed so higher means more attachment; the EU-effect items are reversed so higher means a more positive evaluation; q_class runs working class up to higher class with dont_know last. Top: points are per-level posterior medians with cluster-robust 95% intervals (posterior SD combined with a respondent cluster-bootstrap SD); ordered numeric scales are drawn as a connecting line and interval ribbon, categorical moderators as dodged points and intervals; grey bars show the per-level row count (pooled over games). Bottom: per-grid-cell posterior median, cluster-robust 95% ribbon, and connecting line per game over a grey histogram of the covariate, on 100 equal intervals across the full 18-75 years. The y-axis is free per facet; discrete levels comprising less than 1% of a game's sample are dropped because their CATE is too imprecise to compare."
#| dpi: 500
#| fig-width: 11
#| fig-height: 14
p_resp1 <- plot_comb(
  comb_resp |>
    filter(mod %in% resp_half1) |>
    mutate(mod = factor(mod, levels = resp_half1)),
  ncol = 4,
  title = bquote(
    "CATE by individual-level moderator, both games (1 of 2)" ~ (hat(tau)[ic])
  )
)
p_age <- cont_panel(
  comb_resp |> filter(mod == "q_age"),
  m_dict[["q_age"]],
  "q_age",
  c(18, 75)
) +
  guides(colour = "none", shape = "none", fill = "none", linetype = "none")
(p_resp1 / p_age) + plot_layout(heights = c(3, 1))
```

```{r}
#| label: fig-bcf-combined-resp-2
#| fig-cap: "BCF posterior estimates of the respondent-level CATE of the Muslim profile across the levels of the second half of the discrete individual-level moderators (top panel) and across age at which education stopped (q_edu_age_stop, bottom panel), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. The y-axis ($\\hat{\\tau}_i$) is the respondent-level CATE on the token-allocation scale. Identity scales are reversed so higher means more attachment; the EU-effect items are reversed so higher means a more positive evaluation; q_class runs working class up to higher class with dont_know last. Top: points are per-level posterior medians with cluster-robust 95% intervals (posterior SD combined with a respondent cluster-bootstrap SD); ordered numeric scales are drawn as a connecting line and interval ribbon, categorical moderators as dodged points and intervals; grey bars show the per-level row count (pooled over games). Bottom: posterior median, cluster-robust 95% ribbon, and connecting line per game at each integer year of education-stopping age from 15 to 30, over a grey histogram of the covariate. The y-axis is free per facet; discrete levels comprising less than 1% of a game's sample are dropped because their CATE is too imprecise to compare."
#| dpi: 500
#| fig-width: 11
#| fig-height: 14
p_resp2 <- plot_comb(
  comb_resp |>
    filter(mod %in% resp_half2) |>
    mutate(mod = factor(mod, levels = resp_half2)),
  ncol = 4,
  title = bquote(
    "CATE by individual-level moderator, both games (2 of 2)" ~ (hat(tau)[ic])
  )
)
p_edu <- cont_panel(
  comb_resp |> filter(mod == "q_edu_age_stop"),
  m_dict[["q_edu_age_stop"]],
  "q_edu_age_stop",
  c(15, 30)
) +
  guides(colour = "none", shape = "none", fill = "none", linetype = "none")
(p_resp2 / p_edu) + plot_layout(heights = c(3, 1))
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
