---
subtitle: |
  BCF Post-Processing — ATE, Posterior Projection, and CATE by Moderator (Dictator + Trust)
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Purpose {#sec-purpose}

This notebook post-processes the **robustness** estimator — the saved hierarchical BCF fits
(`data/03_final/bcf_{dictator,trust}.rds`) — into the same three quantities, in the same order,
as the combined view of the primary GRF notebook `07_postprocess_grf.qmd`:

1. **Average treatment effect (ATE)** — the posterior of the ATE for each game.
2. **Posterior linear projection** — the Bayesian counterpart to GRF's best linear projection
   (`woody2021model`): each posterior draw of τ(x) is projected onto the moderator design, giving
   a posterior distribution of projection coefficients. Appendix-style linear summary.
3. **CATE by moderator** — the headline figures: estimated CATE on the y-axis, a moderator on the
   x-axis.

It is the BCF counterpart to `07_postprocess_grf.qmd` and is structurally parallel to it; only the
inference machinery differs. GRF reports point estimates with honest cluster-robust confidence
intervals; BCF reports **posterior medians with 95% credible intervals**, read off the posterior
draws of τ(x) extracted with `get_forest_fit()`.

Following the **combined-figure** grammar of `07` (its `# Combined figures` section) and the house
style of `09_main_figs_tables.qmd`, every figure overlays **both games on one canvas**. The two
games are the only thing encoded by colour, shape, and linetype, and they are always encoded by all
three together, so each game is distinguishable in colour, in greyscale print, and under
colourblindness. Every other distinction (which moderator, which level) is carried by facets and
axis position.

Two moderator families, matching the research plan:

- **Conjoint round-level** moderators (`prof_mods`) — other attributes in the same profile.
- **Individual-level** moderators (`resp_mods`) — respondent pre-treatment items and indices.

Per-level uncertainty is the **95% posterior credible interval** of the bin/level CATE, mirroring
`fig-cate-by-cov-bcf` in `03_multibart_nested_ri_test.qmd`.
The credible interval here reflects posterior uncertainty only; the respondent cluster bootstrap
(within-person dependence across the three rounds) is a separate downstream step, not done here.

# Setup {#sec-setup}

The setup chunk loads the project packages plus `multibart`'s own dependencies before the local
package is attached (needed for `get_forest_fit()`).

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr, purrr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # combined-figure composition
  "sessioninfo", # session docs

  # multibart dependencies -----------------------------------------------------
  "Rcpp", # multibart Depends + LinkingTo
  "RcppArmadillo", # multibart Depends + LinkingTo
  "Rcereal", # multibart Depends + LinkingTo
  "fastDummies" # multibart helper dependency
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: setup-multibart
#| include: false
# install local source on first use
if (!requireNamespace("multibart", quietly = TRUE)) {
  install.packages(
    here::here("code", "multibart"),
    repos = NULL,
    type = "source"
  )
}
# attach installed package
library(multibart)
```

# Load data and fits {#sec-load}

```{r}
#| label: load-data
dat <- readRDS(here::here("data", "02_processed", "eu25_long.rds"))
fit_dict <- readRDS(here::here("data", "03_final", "bcf_dictator.rds"))
fit_trust <- readRDS(here::here("data", "03_final", "bcf_trust.rds"))
```

# Variable definitions {#sec-vars}

The frozen moderator list and `prep_game()` are reused verbatim from `05_bcf_fit.qmd` so the
reconstructed moderator design matches fit-time row order and columns exactly.

```{r}
#| label: moderators
prof_mods <- c("cj_nat", "cj_eupos", "cj_age", "cj_sex", "cj_class")
resp_mods <- c(
  "q_gender", "q_age", "q_identity_country", "q_identity_eu",
  "q_identity_europe", "q_religion", "q_class", "q_eu_efficacy_understand",
  "q_pop_reps", "q_pop_goodevil", "q_pop_compromise", "q_dem_compromise",
  "q_dem_listen", "q_tech_experts", "q_tech_leaders", "q_party_harm",
  "q_people_incompetent", "q_eu_longterm", "q_eu_responsive",
  "q_eu_imp_nat_econ", "q_eu_imp_nat_cul", "q_eu_imp_nat_pol",
  "q_eu_abolish", "q_eu_satisfaction", "q_rural_urban", "q_edu_age_stop"
)
```

```{r}
#| label: prep-game
prep_game <- function(dat, game) {
  sub <- dat |>
    filter(cj_game_type == game) # full per-game sample (no subsampling)

  y <- sub$cj_pl2
  z <- as.integer(sub$cj_rel == "muslim") # Muslim vs all-else pooled
  country_id <- factor(sub$meta_country)
  respondent_id <- factor(sub$meta_pid)

  mod_df <- sub |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
  sub_X <- model.matrix(~ . - 1, data = mod_df) # factors -> dummies

  stopifnot(
    !anyNA(sub_X),
    all(z %in% c(0L, 1L)),
    !anyNA(y),
    nrow(sub_X) == length(y)
  )

  list(
    y = y, z = z, sub_X = sub_X,
    country_id = country_id, respondent_id = respondent_id
  )
}
```

`game_mods()` returns the original (pre-dummy) moderator values for one game, in the same row
order as `prep_game()`, so each observation's τ̂ aligns with its moderator value.

```{r}
#| label: game-mods
game_mods <- function(dat, game) {
  dat |>
    filter(cj_game_type == game) |>
    select(all_of(c(prof_mods, resp_mods))) |>
    mutate(across(where(is.character), factor))
}
```

# House style {#sec-house}

The Okabe-Ito game palette with redundant shape and linetype, the three reserved scales, the
shared theme, and the reference layers — copied from `09_main_figs_tables.qmd` / the combined
section of `07_postprocess_grf.qmd` so the BCF figures share the manuscript grammar exactly.

```{r}
#| label: game-style
game_labs <- c(cj_dict = "Dictator game", cj_trust = "Trust game")
game_cols <- c("Dictator game" = "#0072B2", "Trust game" = "#D55E00")
game_shapes <- c("Dictator game" = 16, "Trust game" = 17) # circle / triangle
game_ltys <- c("Dictator game" = "solid", "Trust game" = "longdash")

scale_colour_game <- function() scale_colour_manual(values = game_cols, name = NULL)
scale_shape_game <- function() scale_shape_manual(values = game_shapes, name = NULL)
scale_linetype_game <- function() scale_linetype_manual(values = game_ltys, name = NULL)

theme_mbeu <- function(base_size = 11) {
  ggpubr::theme_pubr(base_size = base_size) +
    theme(legend.position = "top")
}
ref_zero <- geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60")
dodge <- position_dodge(width = 0.5)
yl_cate <- "CATE (effect of Muslim profile)"
```

# Posterior summary builders {#sec-machinery}

Every quantity below is read off `tau_draws`, the `nsim × n` posterior matrix returned by
`get_forest_fit()` (rows index posterior draws, columns index observations). All three builders
operate on a single game's `tau_draws`, so they run inside the per-game block and the large matrix
is freed before the next game.

A moderator is **discrete** (factor, or numeric with ≤ 10 distinct values: Likert items) or
**binned** (higher-cardinality numeric → 10 quantile bins).

```{r}
#| label: classify
classify_mod <- function(col) {
  if (is.factor(col) || is.character(col)) {
    return("discrete")
  }
  if (dplyr::n_distinct(col) <= 10) {
    return("discrete")
  }
  "binned"
}
```

`ate_summary()` returns the posterior of the ATE: the per-draw mean of τ(x) over all observations,
summarised by its median and a 95% credible interval.

```{r}
#| label: ate-summary
ate_summary <- function(tau_draws) {
  bd <- rowMeans(tau_draws) # posterior of the ATE
  tibble(
    estimate = median(bd),
    lower = unname(quantile(bd, 0.025)),
    upper = unname(quantile(bd, 0.975))
  )
}
```

`proj_summary()` is the Bayesian posterior projection (`woody2021model`), the BCF counterpart to
GRF's `best_linear_projection`. For each posterior draw `d`, the coefficient vector is
$\beta_d = (X'X)^{-1} X' \tau_d$; we stack these into a posterior and summarise each term by its
median and 95% credible interval.
The design `sub_X` is `model.matrix(~ . - 1, ...)`, which is full rank (only the first factor is
fully expanded; the rest are contrast-coded), so `crossprod(sub_X)` inverts directly — no added
intercept, no ridge. It is the same column basis as GRF's `X_dict`, so the terms are comparable.
The only large multiply (`tau_draws %*% sub_X`) returns a small `nsim × p` matrix, so the step is
memory-safe.

```{r}
#| label: proj-summary
proj_summary <- function(tau_draws, sub_X) {
  xtx <- crossprod(sub_X) # p x p
  m <- tau_draws %*% sub_X # nsim x p  (= tau_d' X per draw)
  beta <- solve(xtx, t(m)) # p x nsim  = (X'X)^{-1} X' tau_d
  tibble(
    term = colnames(sub_X),
    estimate = apply(beta, 1, median),
    lower = apply(beta, 1, quantile, 0.025),
    upper = apply(beta, 1, quantile, 0.975)
  )
}
```

`cate_one_bcf()` is the BCF version of the combined CATE builder in `07`: same level/decile logic,
same `< 500`-row sparse-level drop, same `is_scale` tagging (`cj_age` is treated as categorical
because its five values are fixed conjoint ages, not a continuous scale), and the same
`order`/`level`/`n` columns — but each bin's estimate and interval come from the **posterior of the
bin mean** (`rowMeans` of τ(x) over the bin's observations; median + 2.5/97.5%) rather than a
subset ATE.

```{r}
#| label: cate-one-bcf
# posterior of the bin CATE over a logical keep-vector (length n)
.bin_post <- function(tau_draws, keep) {
  bd <- rowMeans(tau_draws[, keep, drop = FALSE]) # posterior of bin mean
  c(
    estimate = median(bd),
    lower = unname(quantile(bd, 0.025)),
    upper = unname(quantile(bd, 0.975))
  )
}

cate_one_bcf <- function(tau_draws, mm, mod, game_label) {
  v <- mm[[mod]]
  is_num <- is.numeric(v)
  # continuous moderators: decile bins, integer labels
  if (is_num && length(unique(v)) > 12) {
    bin <- ntile(v, 10)
    rows <- lapply(sort(unique(bin)), function(k) {
      sel <- !is.na(bin) & bin == k
      p <- .bin_post(tau_draws, sel)
      tibble(
        mod = mod, level = as.character(round(mean(v[sel]))),
        order = mean(v[sel]), is_scale = TRUE, game = game_label,
        n = sum(sel),
        estimate = p["estimate"], lower = p["lower"], upper = p["upper"]
      )
    })
    return(bind_rows(rows))
  }
  levs <- if (is_num) sort(unique(v)) else sort(unique(as.character(v)))
  rows <- lapply(seq_along(levs), function(i) {
    lev <- levs[i]
    sel <- if (is_num) !is.na(v) & v == lev else !is.na(v) & as.character(v) == lev
    # drop sparse levels (within game)
    if (sum(sel) < 500) {
      return(NULL)
    }
    p <- .bin_post(tau_draws, sel)
    tibble(
      mod = mod, level = as.character(lev),
      order = if (is_num) as.numeric(lev) else i,
      is_scale = is_num && mod != "cj_age", game = game_label,
      n = sum(sel),
      estimate = p["estimate"], lower = p["lower"], upper = p["upper"]
    )
  })
  bind_rows(rows)
}
```

# Combined plotters {#sec-plotters}

`plot_comb()` draws the faceted overview with a free y-axis per facet: grey per-level count bars
(pooled over games) along the bottom, posterior medians and credible intervals dodged by game
everywhere, plus a connecting line and ribbon on the ordered-scale facets only.
It is reused verbatim from the combined section of `07` (it reads only the summary columns the BCF
builders produce, so the posterior intervals slot straight in).

```{r}
#| label: plot-comb
plot_comb <- function(df, ncol, title) {
  d <- df |>
    arrange(mod, order) |>
    mutate(key = factor(
      paste0(mod, "@@", level),
      levels = unique(paste0(mod, "@@", level))
    ))
  # per-facet grey count bars (pooled over games shown)
  band <- d |>
    summarise(cnt = sum(n), .by = c(mod, key)) |>
    left_join(
      d |>
        summarise(
          floor_y = min(lower) - 0.12 * (max(upper) - min(lower)),
          span = 0.20 * (max(upper) - min(lower)),
          .by = mod
        ),
      by = "mod"
    ) |>
    mutate(bar_top = floor_y + (cnt / max(cnt)) * span, .by = mod)
  d_scale <- dplyr::filter(d, is_scale)
  d_cat <- dplyr::filter(d, !is_scale)
  p <- ggplot(d, aes(x = key, y = estimate, colour = game, shape = game)) +
    geom_segment(
      data = band,
      aes(x = key, xend = key, y = floor_y, yend = bar_top),
      colour = "grey80",
      linewidth = 3,
      inherit.aes = FALSE
    ) +
    ref_zero
  # ordered scales: overlaid ribbon + line + point (continuous-style)
  if (nrow(d_scale) > 0) {
    p <- p +
      geom_ribbon(
        data = d_scale,
        aes(ymin = lower, ymax = upper, fill = game, group = game),
        alpha = 0.15,
        colour = NA
      ) +
      geom_line(data = d_scale, aes(group = game, linetype = game)) +
      geom_point(data = d_scale) +
      scale_linetype_game() +
      scale_fill_manual(values = game_cols, name = NULL)
  }
  # categorical: dodged credible interval + point
  if (nrow(d_cat) > 0) {
    p <- p +
      geom_linerange(
        data = d_cat,
        aes(ymin = lower, ymax = upper),
        position = dodge
      ) +
      geom_point(data = d_cat, position = dodge)
  }
  p +
    facet_wrap(~mod, scales = "free", ncol = ncol) +
    scale_colour_game() +
    scale_shape_game() +
    scale_x_discrete(labels = \(k) sub(".*@@", "", k)) +
    labs(title = title, x = NULL, y = yl_cate) +
    guides(fill = "none", linetype = "none") +
    theme_mbeu() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
}
```

`cont_panel()` draws one genuinely continuous moderator on a continuous x-axis: its per-decile
posterior CATE (ribbon + line + point per game) over a grey histogram of the covariate, with the
x-axis trimmed to `xlim`. Unlike the `07` version it takes the **precomputed** combined sub-tibble
`d` (the BCF draws are already freed by plotting time) and the raw covariate values `raw` for the
histogram.

```{r}
#| label: cont-panel
cont_panel <- function(d, raw, mod, xlim) {
  # covariate distribution within the visible range
  v <- raw[!is.na(raw) & raw >= xlim[1] & raw <= xlim[2]]
  h <- hist(v, breaks = 30, plot = FALSE)
  floor_y <- min(d$lower) - 0.12 * (max(d$upper) - min(d$lower))
  span <- 0.20 * (max(d$upper) - min(d$lower))
  hd <- tibble(mid = h$mids, w = diff(h$breaks)[1], cnt = h$counts) |>
    mutate(bar_top = floor_y + (cnt / max(cnt)) * span)
  ggplot(d, aes(x = order, y = estimate, colour = game, shape = game)) +
    geom_rect(
      data = hd,
      aes(xmin = mid - w / 2, xmax = mid + w / 2, ymin = floor_y, ymax = bar_top),
      fill = "grey80",
      inherit.aes = FALSE
    ) +
    ref_zero +
    geom_ribbon(
      aes(ymin = lower, ymax = upper, fill = game, group = game),
      alpha = 0.15,
      colour = NA
    ) +
    geom_line(aes(group = game, linetype = game)) +
    geom_point() +
    scale_colour_game() +
    scale_shape_game() +
    scale_linetype_game() +
    scale_fill_manual(values = game_cols, name = NULL) +
    scale_x_continuous(breaks = scales::breaks_pretty(6)) +
    coord_cartesian(xlim = xlim) +
    labs(title = mod, x = "Covariate value (years)", y = yl_cate) +
    theme_mbeu()
}
```

# Build summaries {#sec-build}

`tau_draws` is large (`nsim × n`); we extract it one game at a time and free it once the small
summary tibbles (ATE, projection, and the combined CATE-by-moderator tables) are built.

```{r}
#| label: build-dictator
d_dict <- prep_game(dat, "cj_dict")
m_dict <- game_mods(dat, "cj_dict")
tau_dict <- get_forest_fit(fit_dict$moderate_fit, d_dict$sub_X) # nsim x n

stopifnot(
  nrow(m_dict) == length(d_dict$y),
  ncol(tau_dict) == length(d_dict$y)
)

# ATE sanity check (token scale)
mean(colMeans(tau_dict))

ate_dict <- ate_summary(tau_dict)
proj_dict <- proj_summary(tau_dict, d_dict$sub_X)
comb_prof_dict <- bind_rows(
  lapply(prof_mods, \(m) cate_one_bcf(tau_dict, m_dict, m, "Dictator game"))
)
comb_resp_dict <- bind_rows(
  lapply(resp_mods, \(m) cate_one_bcf(tau_dict, m_dict, m, "Dictator game"))
)

rm(tau_dict, fit_dict)
invisible(gc())
```

```{r}
#| label: build-trust
d_trust <- prep_game(dat, "cj_trust")
m_trust <- game_mods(dat, "cj_trust")
tau_trust <- get_forest_fit(fit_trust$moderate_fit, d_trust$sub_X) # nsim x n

stopifnot(
  nrow(m_trust) == length(d_trust$y),
  ncol(tau_trust) == length(d_trust$y)
)

mean(colMeans(tau_trust))

ate_trust <- ate_summary(tau_trust)
proj_trust <- proj_summary(tau_trust, d_trust$sub_X)
comb_prof_trust <- bind_rows(
  lapply(prof_mods, \(m) cate_one_bcf(tau_trust, m_trust, m, "Trust game"))
)
comb_resp_trust <- bind_rows(
  lapply(resp_mods, \(m) cate_one_bcf(tau_trust, m_trust, m, "Trust game"))
)

rm(tau_trust, fit_trust)
invisible(gc())
```

The combined tables, with both games stacked and `mod` ordered for faceting.

```{r}
#| label: combine
game_lvls <- c("Dictator game", "Trust game")

ate_comb <- bind_rows(
  ate_dict |> mutate(game = "Dictator game"),
  ate_trust |> mutate(game = "Trust game")
) |>
  mutate(game = factor(game, levels = game_lvls))

proj_comb <- bind_rows(
  proj_dict |> mutate(game = "Dictator game"),
  proj_trust |> mutate(game = "Trust game")
) |>
  mutate(game = factor(game, levels = game_lvls))

comb_prof <- bind_rows(comb_prof_dict, comb_prof_trust) |>
  mutate(mod = factor(mod, levels = prof_mods))
comb_resp <- bind_rows(comb_resp_dict, comb_resp_trust) |>
  mutate(mod = factor(mod, levels = resp_mods))

stopifnot(
  nrow(ate_comb) == 2,
  all(prof_mods %in% comb_prof$mod),
  all(resp_mods %in% comb_resp$mod)
)
```

# The recovered ATEs {#sec-ate}

The posterior ATE — the per-draw average of τ(x) over all observations — for each game, with its
95% credible interval.

```{r}
#| label: fig-bcf-combined-ate
#| fig-cap: "BCF posterior ATE of the Muslim profile, both games. Points are posterior medians and bars are 95% credible intervals (per-draw average of tau(x) over all observations). Games distinguished jointly by colour and shape."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 4
ate_comb |>
  ggplot(aes(x = game, y = estimate, colour = game, shape = game)) +
  ref_zero +
  geom_pointrange(aes(ymin = lower, ymax = upper), linewidth = 0.8, size = 0.9) +
  scale_colour_game() +
  scale_shape_game() +
  labs(
    title = "Posterior ATE of the Muslim profile, both games",
    x = NULL,
    y = yl_cate
  ) +
  theme_mbeu()
```

# The posterior linear projections {#sec-proj}

The posterior projection of τ(x) onto the moderator design: a linear summary of which moderators
shift the treatment effect, the Bayesian counterpart to GRF's best linear projection
(`woody2021model`).
This is an appendix/robustness summary, not a headline. Terms are ordered by their mean posterior
coefficient across the two games.

```{r}
#| label: fig-bcf-combined-proj
#| fig-cap: "BCF posterior linear projection of the CATE onto the moderator set, both games overlaid, with 95% credible intervals (dodged by game). Each coefficient is the posterior of (X'X)^{-1} X' tau_d. Terms are ordered by their mean coefficient across the two games. Appendix-style linear summary of effect modification."
#| dpi: 500
#| fig-width: 6.5
#| fig-height: 9
proj_ord <- proj_comb |>
  summarise(m = mean(estimate), .by = term) |>
  arrange(m) |>
  pull(term)
proj_plot <- proj_comb |> mutate(term = factor(term, levels = proj_ord))

ggplot(proj_plot, aes(x = estimate, y = term, colour = game, shape = game)) +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "grey60") +
  geom_pointrange(aes(xmin = lower, xmax = upper), position = dodge) +
  scale_colour_game() +
  scale_shape_game() +
  labs(
    title = "Posterior linear projection of the CATE, both games",
    x = "Projection coefficient",
    y = NULL
  ) +
  theme_mbeu()
```

# The posterior CATEs by moderator {#sec-cate}

The headline figures: posterior median CATE on the y-axis, the moderator on the x-axis, with a 95%
credible interval at each level/decile, both games overlaid. The y-axis is free per facet; levels
with fewer than 500 rows in a game are dropped for legibility.

## Conjoint round-level moderators {#sec-cate-prof}

All five conjoint-round (profile-level) moderators on one canvas, Dictator and Trust overlaid.
All five are categorical (including `cj_age`, whose five values are fixed conjoint ages), so each is
drawn as dodged points with credible intervals.

```{r}
#| label: fig-bcf-combined-prof
#| fig-cap: "BCF posterior CATE of the Muslim profile (y-axis) across the levels of every conjoint-round moderator (x-axis), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. Points are per-level posterior medians and the vertical bars are 95% credible intervals (posterior of the within-level mean of tau(x)). Grey bars along the bottom of each facet show the per-level row count (pooled over games). The y-axis is free per facet; levels with fewer than 500 rows in a game are dropped for legibility."
#| dpi: 500
#| fig-width: 9
#| fig-height: 6
plot_comb(comb_prof, ncol = 3, title = "CATE by conjoint-round moderator, both games")
```

## Individual-level moderators {#sec-cate-resp}

The respondent-level moderators on two figures so the facets stay legible.
Each figure stacks (via `patchwork`) a faceted panel of half the discrete moderators on top with one
of the two genuinely continuous moderators (`q_age`, `q_edu_age_stop`) on a continuous x-axis below,
so the continuous covariate keeps its real histogram and trimmed axis while still sitting beside the
discrete moderators it belongs with.
Ordered numeric scales (the 5- and 7-point items) carry an overlaid 95% credible-interval ribbon
plus connecting line per game; categorical moderators keep dodged points and intervals.
The shared game legend is drawn once, from the top panel.

```{r}
#| label: resp-split
resp_cat <- setdiff(resp_mods, c("q_age", "q_edu_age_stop"))
half <- ceiling(length(resp_cat) / 2)
resp_half1 <- resp_cat[1:half]
resp_half2 <- resp_cat[(half + 1):length(resp_cat)]
```

```{r}
#| label: fig-bcf-combined-resp-1
#| fig-cap: "BCF posterior CATE of the Muslim profile (y-axis) across the levels of the first half of the discrete individual-level moderators (top panel) and across age (q_age, bottom panel), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. Top: points are per-level posterior medians with 95% credible intervals; ordered numeric scales are drawn as a connecting line and credible-interval ribbon, categorical moderators as dodged points and intervals; grey bars show the per-level row count (pooled over games). Bottom: per-decile posterior median, 95% credible-interval ribbon, and connecting line per game over a grey histogram of the covariate; the x-axis is truncated to 18-75 years. The y-axis is free per facet; levels with fewer than 500 rows in a game are dropped for legibility."
#| dpi: 500
#| fig-width: 11
#| fig-height: 14
p_resp1 <- plot_comb(
  comb_resp |> filter(mod %in% resp_half1) |> mutate(mod = factor(mod, levels = resp_half1)),
  ncol = 4,
  title = "CATE by individual-level moderator, both games (1 of 2)"
)
p_age <- cont_panel(
  comb_resp |> filter(mod == "q_age"),
  m_dict[["q_age"]], "q_age", c(18, 75)
) +
  guides(colour = "none", shape = "none", fill = "none", linetype = "none")
(p_resp1 / p_age) + plot_layout(heights = c(3, 1))
```

```{r}
#| label: fig-bcf-combined-resp-2
#| fig-cap: "BCF posterior CATE of the Muslim profile (y-axis) across the levels of the second half of the discrete individual-level moderators (top panel) and across age at which education stopped (q_edu_age_stop, bottom panel), Dictator and Trust games overlaid and distinguished jointly by colour, shape, and linetype. Top: points are per-level posterior medians with 95% credible intervals; ordered numeric scales are drawn as a connecting line and credible-interval ribbon, categorical moderators as dodged points and intervals; grey bars show the per-level row count (pooled over games). Bottom: per-decile posterior median, 95% credible-interval ribbon, and connecting line per game over a grey histogram of the covariate; the x-axis is truncated to 15-30 years. The y-axis is free per facet; levels with fewer than 500 rows in a game are dropped for legibility."
#| dpi: 500
#| fig-width: 11
#| fig-height: 14
p_resp2 <- plot_comb(
  comb_resp |> filter(mod %in% resp_half2) |> mutate(mod = factor(mod, levels = resp_half2)),
  ncol = 4,
  title = "CATE by individual-level moderator, both games (2 of 2)"
)
p_edu <- cont_panel(
  comb_resp |> filter(mod == "q_edu_age_stop"),
  m_dict[["q_edu_age_stop"]], "q_edu_age_stop", c(15, 30)
) +
  guides(colour = "none", shape = "none", fill = "none", linetype = "none")
(p_resp2 / p_edu) + plot_layout(heights = c(3, 1))
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true

end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
