---
subtitle: |
  Main Figures and Tables
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    code-fold: true
    code-tools: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
#| include: false
# execution time
start_time <- Sys.time()
# console width
options(width = 80)
# packages
p_required <- c(
  "tidyverse", # dplyr, ggplot2, tidyr
  "here", # relative paths
  "ggpubr", # theme_pubr
  "patchwork", # multi-panel composition
  "sessioninfo" # session docs
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load long format data {#sec-code-1}

```{r}
#| label: load-dat
eu25_long <- read_rds(
  here(
    "data",
    "02_processed",
    "eu25_long.rds"
  )
)
```

# House style {#sec-house}

The shared visual grammar for every figure in this notebook.
The two games are the only thing encoded by colour, shape, and linetype, and they are always
encoded by all three at once, so each game is distinguishable in colour, in greyscale print,
and under colourblindness.
Any other categorical distinction (moderator family, estimator, treatment level) is carried by
facets, panels, or axis position — never by reusing a game channel.

```{r}
#| label: game-style
# game identity: Okabe-Ito blue / orange, redundant shape + linetype
game_labs <- c(cj_dict = "Dictator game", cj_trust = "Trust game")
game_cols <- c("Dictator game" = "#0072B2", "Trust game" = "#D55E00")
game_shapes <- c("Dictator game" = 16, "Trust game" = 17) # circle / triangle
game_ltys <- c("Dictator game" = "solid", "Trust game" = "longdash")

# raw cj_game_type -> ordered, human-readable factor
lab_game <- function(x) {
  factor(unname(game_labs[as.character(x)]), levels = unname(game_labs))
}
```

The three reserved scales are always added together so the legend collapses to one key.

```{r}
#| label: game-scales
scale_colour_game <- function() {
  scale_colour_manual(values = game_cols, name = NULL)
}
scale_shape_game <- function() {
  scale_shape_manual(values = game_shapes, name = NULL)
}
scale_linetype_game <- function() {
  scale_linetype_manual(values = game_ltys, name = NULL)
}
```

Shared theme, reference layers, dodge width, and the common CATE y-axis label.

```{r}
#| label: house-theme
theme_mbeu <- function(base_size = 11) {
  ggpubr::theme_pubr(base_size = base_size) +
    theme(legend.position = "top")
}
# dashed null line for effect figures
ref_zero <- geom_hline(yintercept = 0, linetype = "dashed", colour = "grey60")
# side-by-side offset for two-game overlays
dodge <- position_dodge(width = 0.5)
# shared axis label for CATE-by-moderator figures
yl_cate <- "CATE (effect of Muslim profile)"
```

The golden ratio is the default figure aspect (width : height ≈ 1.618 : 1).
Set chunk `fig-width`/`fig-height` from `golden` so single-panel figures share one proportion;
do not apply it to faceted small multiples or auto-sized contexts.

```{r}
#| label: golden-ratio
golden <- (1 + sqrt(5)) / 2 # ~1.618
# figure height (in) for a given width at golden proportion
golden_h <- function(width) width / golden
```

# Token allocation to Muslim profiles {#sec-diff-means}

The motivating descriptive: how many tokens does a profile receive when it is
labelled Muslim versus everything else, in each game.
We summarise this two ways — a per-game Welch two-sample t-test on the raw
difference in means (the sample average treatment effect, SATE), and a
slope/dumbbell figure of the two group means with 95% confidence intervals.
The test is intentionally simple and descriptive: respondent clustering is left
to the heterogeneity models that follow.

```{r}
#| label: diff-in-means-test
# analysis frame: muslim vs all-else, readable game
dim_dat <- eu25_long |>
  mutate(
    treat = factor(
      if_else(cj_rel == "muslim", "Muslim", "Non-Muslim"),
      levels = c("Non-Muslim", "Muslim")
    ),
    game = lab_game(cj_game_type)
  )

# welch t-test per game, muslim - non-muslim
dim_test_one <- function(df) {
  tt <- t.test(cj_pl2 ~ treat, data = df) # non-muslim - muslim
  tibble(
    mean_nonmuslim = unname(tt$estimate[1]),
    mean_muslim = unname(tt$estimate[2]),
    diff = mean_muslim - mean_nonmuslim,
    conf_low = -tt$conf.int[2],
    conf_high = -tt$conf.int[1],
    t = -unname(tt$statistic),
    df = unname(tt$parameter),
    p = tt$p.value
  )
}

dim_tests <- dim_dat |>
  group_by(game) |>
  group_modify(~ dim_test_one(.x)) |>
  ungroup()

dim_tests
```

Read the SATE numbers off `dim_tests` above and fill the placeholders in the
figure caption.

```{r}
#| label: fig-diff-in-means
#| fig-cap: "Mean tokens allocated to a profile by the Muslim label, by game. The outcome (y-axis) is the number of tokens the respondent allocates to the displayed profile. X-axis contrasts profiles labelled Muslim against all other religions pooled. Points are group means and error bars are 95% confidence intervals. The slope of each line is the sample average treatment effect (SATE) of the Muslim label, estimated by a per-game Welch two-sample difference-in-means t-test: $\\widehat{\\text{SATE}}_\\text{Dictator} = -0.57\\ [-0.61, -0.53]$, $\\widehat{\\text{SATE}}_\\text{Trust} = -0.64\\ [-0.68, -0.61]$."
#| fig-dpi: 500
#| fig-width: 5.5
#| fig-height: 3.4
# group means + 95% ci
dim_means <- dim_dat |>
  group_by(game, treat) |>
  summarise(
    mean_tok = mean(cj_pl2),
    se = sd(cj_pl2) / sqrt(n()),
    ci = qt(0.975, n() - 1) * se,
    .groups = "drop"
  )

dim_means |>
  ggplot(aes(
    x = treat,
    y = mean_tok,
    colour = game,
    shape = game,
    linetype = game,
    group = game
  )) +
  geom_line(position = dodge, linewidth = 0.7) +
  geom_errorbar(
    aes(ymin = mean_tok - ci, ymax = mean_tok + ci),
    position = dodge,
    width = 0.08,
    linewidth = 0.4,
    linetype = "solid"
  ) +
  geom_point(position = dodge, size = 3) +
  scale_colour_game() +
  scale_shape_game() +
  scale_linetype_game() +
  labs(
    title = "Muslim profiles receive fewer tokens in both games",
    x = NULL,
    y = "Mean tokens allocated"
  ) +
  theme_mbeu()
```


# Outcome Distribution

The distribution of the raw outcome — tokens allocated to the displayed profile,
an integer from 0 to 10 — in each game.
Both games are drawn together with the reserved colour/shape/linetype grammar applied at
once, and shown as within-game proportions so the two games are comparable despite differing
numbers of decisions.

```{r}
#| label: fig-outcome-distr
#| fig-cap: "Distribution of outcomes (tokens allocated to the displayed profile) by game. Height of bars are the within-game share of decisions at each integer token value, connected within game."
#| fig-dpi: 500
#| fig-width: 5.5
#| fig-height: 3.4
# within-game share at each integer token value
outcome_distr <- eu25_long |>
  mutate(game = lab_game(cj_game_type)) |>
  count(game, cj_pl2) |>
  group_by(game) |>
  mutate(prop = n / sum(n)) |>
  ungroup()

outcome_distr |>
  ggplot(aes(
    x = cj_pl2,
    y = prop,
    colour = game,
    shape = game,
    linetype = game,
    group = game
  )) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 2.5) +
  scale_colour_game() +
  scale_shape_game() +
  scale_linetype_game() +
  scale_x_continuous(breaks = 0:10) +
  scale_y_continuous(labels = scales::label_percent()) +
  labs(
    title = "Token allocations cluster at the endpoints in both games",
    x = "Tokens allocated to profile",
    y = "Share of decisions"
  ) +
  theme_mbeu()
```

# Session Info {#sec-session-info .appendix .unnumbered}

```{r}
#| label: session-info
#| eval: true
#| echo: true
session_info()
```

# Execution Time {#sec-exec-time .appendix .unnumbered}

```{r}
#| label: exec-time
#| eval: true
#| echo: true
#| include: true
end_time <- Sys.time()
exec_time <- end_time - start_time
cat(paste(
  "R code execution time:",
  round(as.numeric(exec_time, units = "secs"), 2),
  "seconds."
))
```
